### 2017-12-18 article/ms.tex
add first author

\documentclass[a4paper,fleqn,usenatbib]{mnras}

\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Matthew T. Miles et al.]{
Matthew T. Miles,$^{1}$\thanks{E-mail: mn@ras.org.uk (KTS)}
A. N. Other,$^{2}$
Third Author$^{2,3}$
and Fourth Author$^{3}$
\\
% List of institutions
$^{1}$School of Physics and Astronomy, Monash University, Clayton Campus, Victoria 3800\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

\date{Accepted XXX. Received YYY; in original form ZZZ}

\pubyear{2015}

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

\section{Introduction}

This is a simple template for authors to write new MNRAS papers.
See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
for a full user guide.

All papers should start with an Introduction section, which sets the work
in context, cites relevant earlier studies in the field by \citet{Others2013},
and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.

\section{Methods, Observations, Simulations etc.}

Normally the next section describes the techniques the authors used.
It is frequently split into subsections, such as Section~\ref{sec:maths} below.

\subsection{Maths}
\label{sec:maths}

Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
as a numbered equation:

\begin{equation}
    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
	\label{eq:quadratic}
\end{equation}

Refer back to them as e.g. equation~(\ref{eq:quadratic}).

\subsection{Figures and tables}

Figures and tables should be placed at logical positions in the text. Don't
worry about the exact layout, which will be handled by the publishers.

Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
e.g. Table~\ref{tab:example_table}.

\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{example}
    \caption{This is an example figure. Captions appear below each figure.
	Give enough detail for the reader to understand what they're looking at,
	but leave detailed discussion to the main body of the text.}
    \label{fig:example_figure}
\end{figure}

\begin{table}
	\centering
	\caption{This is an example table. Captions appear above each table.
	Remember to define the quantities, symbols and units used.}
	\label{tab:example_table}
	\begin{tabular}{lccr} % four columns, alignment for each
		\hline
		A & B & C & D\\
		\hline
		1 & 2 & 3 & 4\\
		2 & 4 & 6 & 8\\
		3 & 5 & 7 & 9\\
		\hline
	\end{tabular}
\end{table}

\section{Conclusions}

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

% The best way to enter references is to use BibTeX:

%\bibliographystyle{mnras}
%\bibliography{example} % if your bibtex file is called example.bib

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
Others S., 2012, Journal of Interesting Stuff, 17, 198
\end{thebibliography}

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

### 2018-01-15 article/ms.tex
update
intro first-pass

@@
 % Keep the title short and informative.
-\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}
+\title[Research is fun, max. 45 characters]{You can't spell Euphoric without Eu.}
 
@@
 \author[Matthew T. Miles et al.]{
-Matthew T. Miles,$^{1}$\thanks{E-mail: mn@ras.org.uk (KTS)}
+Matthew T. Miles,$^{1}$\thanks{E-mail: mtmil3@student.monash.edu}
 A. N. Other,$^{2}$
@@
 
-This is a simple template for authors to write new MNRAS papers.
-See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
-for a full user guide.
+Heavy elements (those with an atomic number greater than 30) must be synthesized using the slow (s) and rapid (r) neutron capture processes (\cite{Sneden2008}).
+The creation and abundance of these elements has been a key area in astrophysics research, and has been discussed and debated ever since the idea was first introduced in 1957 (\cite{Burbidge1957}).
+In the particular case of Europium (atomic number 63), almost all is produced through the r-process.
+The r-process occurs under very specific circumstances, where the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the element undergoes a $\beta$ decay.
+The sites at which this phenomena can occur are very specific, with the most favoured being early core-collapse supernovae which would have enriched gas clouds that later led to enriched star formation.
+Or more recently, neutron star mergers, as is theorised to have occurred in the case of the highly r-processed enhanced ultra-faint dwarf (UFD) galaxy Reticulum II (\cite{Ji2016}).
 
-All papers should start with an Introduction section, which sets the work
-in context, cites relevant earlier studies in the field by \citet{Others2013},
-and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.
+The recent discovery of the UFD Reticulum II has sparked discussion about the origin of r-process elements.
+Historically UFD's have had some of the lowest abundance of r-process elements of any celestial body, however analysis of several of Reticulum II's stars show they are greatly enriched, to the factor of 2-3 orders of magnitude higher than stars found in any other UFD (\cite{Ji2016}).
+This measure of enrichment lends evidence to the theory that a single rare event (such as a neutron star merger) must have occurred in the galaxies formative years to enrich it, as (for Europium especially) the heavy element yields are found to be 1000 times higher than would be achieved from core-collapse supernovae ejecta.
+
+While core-collapse supernovae and neutron star mergers are likely to be the progenitors of most r-process material, that is not to say that all r-process material stems from these sources.
+Rather it might serve as an indication of the rarity of stars found to be enhanced in these elements.
+\\\\
+The second data release from the LAMOST telescope catalogued close to 2 million spectra (low resolution) of giant stars.
+Of these 2 million, 454,180 were fit against a normalised spectra from a sample of 9952 giants by Anna Ho (\cite{AnnaHo2017}), and from this it became possible to analyse which giants showed an abundance or depletion of particular heavy elements.
+
+In this letter we report the probable discovery of 22 of these LAMOST giants that show enhanced r-process peaks for Europium at both 4129 and 4205 Angstroms.
+The giants belong to a broad range of both metallicity and temperature, and don't cluster or trend towards any particular place in the observed sky.
+These characteristics and seeming lack-of a trend could argue that the mechanism that created these r-process enhanced stars may be general for all similar giant stars.
 
 \section{Methods, Observations, Simulations etc.}
-
 Normally the next section describes the techniques the authors used.
 It is frequently split into subsections, such as Section~\ref{sec:maths} below.
+
+\subsection{Observations}
+The
 
@@
 
-%\bibliographystyle{mnras}
-%\bibliography{example} % if your bibtex file is called example.bib
-
+\bibliographystyle{mnras}
+\bibliography{paper} % if your bibtex file is called example.bib
 \begin{thebibliography}{99}
-\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-Others S., 2012, Journal of Interesting Stuff, 17, 198
+	\bibitem[\protect\citeauthoryear{Sneden, Christopher; Cowan, John J; Gallino, Roberto}{2008}]{Sneden2008}
+	Sneden C., Cowan J.J., \& Gallino R. 2013, Annual review of Astronomy \& Astrophysics, 46, 1
+	\bibitem[\protect\citeauthoryear{Ji, Alexander P.; Frebel, Anna; Chiti, Anirudh; Simon, Joshua D.}{2016}]{Ji2016}
+	Ji A. P., Frebel A., Chiti A., \& Simon J. D. 2016, Nature, 531
+	\bibitem[\protect\citeauthoryear{Ho, Anna Y.Q; Ness, Melissa K; Hogg, David W; Rix, Hans-Walter; Liu, Chao,; Yang, Fan; Zhang, Yong; Hou Yonhui; Wang Yuefei}{2017}]{AnnaHo2017}
+	Ho A. Y. Q., Ness M. K., Hogg David W., Rix H-W., Liu C., Yang F., Zhang Y., Hou Y.,\& Wang Y. 2017, ApJ, 836, 1
+	\bibitem[\protect\citeauthoryear{Burbidge, E. Margaret; Burbidge, G.R.; Fowler, William A.; Hoyle, F}{1957}]{Burbidge1957}
+	Burbidge E. M., Burbidge G. R., Fowler W. A., \& Hoyle F. 1957, Review of Modern Physics, 29, 4
 \end{thebibliography}
@@
 % Don't change these lines
-\bsp	% typesetting comment
+%\bsp	% typesetting comment
 \label{lastpage}

### 2018-01-16 Na_newcode.py
Sodium Code

@@ -1,0 +1,104 @@
+import numpy as np
+import os
+import matplotlib.pyplot as plt
+
+import lamost
+import utils
+
+
+catalog = lamost.load_catalog()
+wavelengths = lamost.common_wavelengths
+N, P = (len(catalog), wavelengths.size)
+
+# Open the data arrays
+all_observed_flux = np.memmap(
+os.path.join(lamost.LAMOST_PATH, "observed_flux.memmap"),
+    mode="r", dtype='float32', shape=(N, P))
+
+all_observed_ivar = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "observed_ivar.memmap"),
+    mode="r", dtype='float32', shape=(N, P))
+
+all_model_flux = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "model_flux.memmap"),
+    mode="r", dtype="float32", shape=(N, P))
+
+star_index = 10
+
+observed_flux = all_observed_flux[star_index]
+observed_ivar = all_observed_ivar[star_index]
+model_flux = all_model_flux[star_index]
+
+x, y, y_err, indices = lamost.get_data_to_fit(wavelengths, observed_flux,
+    observed_ivar, model_flux, 4120, 4140)
+
+p0 = np.array([-0.1,  4129, 2])
+
+p_opt, p_cov = lamost.fit_gaussian(x, y, y_err, p0)
+
+
+
+
+L = len(p_opt)
+Na_p_opts_5890 = np.zeros((N,L))
+Na_p_covs_5890 = np.zeros((N,L,L))
+Na_p_opts_5896 = np.zeros((N,L))
+Na_p_covs_5896 = np.zeros((N,L,L))
+
+for index, star in enumerate(catalog):
+
+    
+    observed_flux = all_observed_flux[index]
+    observed_ivar = all_observed_ivar[index]
+    model_flux = all_model_flux[index]
+
+    #Sodium doublet (Enhanced)
+    x, y, y_err, indices = lamost.get_data_to_fit(wavelengths, observed_flux,
+        observed_ivar, model_flux, 5879, 5899)
+    try:
+        p0 = np.array([-0.1, 5889.95, 2]) 
+        p_optNa_5890, p_covNa_5890 = lamost.fit_gaussian(x, y, y_err, p0)
+        p_opt_errorNa_5890 = np.sqrt(np.diag(p_covNa_5890))
+    except ValueError:
[…]

### 2018-01-16 Na_process.py

@@ -1,0 +1,108 @@
+import numpy as np
+import os
+import matplotlib.pyplot as plt
+from astropy.table import Table
+
+import lamost
+import utils
+import pandas as pd
+
+plt.ioff()
+catalog = lamost.load_catalog()
+wavelengths = lamost.common_wavelengths
+N, P = (len(catalog), wavelengths.size)
+
+# Open the data arrays
+all_observed_flux = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "observed_flux.memmap"),
+    mode="r", dtype='float32', shape=(N, P))
+
+all_observed_ivar = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "observed_ivar.memmap"),
+    mode="r", dtype='float32', shape=(N, P))
+
+all_model_flux = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "model_flux.memmap"),
+    mode="r", dtype="float32", shape=(N, P))
+
+t = Table.read("Na_new_catalog.csv")
+
+snrg = t["snrg"]
+chi = t["cannon_red_chisq"]
+starID=t["id"]
+
+teff= t["cannon_teff"]
+surfg= t["cannon_logg"]
+met= t["cannon_m_h"]
+
+Na5889_wavelength = t["Na_5890_wavelength"] 
+Na5889_amp = t["Na_5890_amplitude"]
+Na5889_amperr = t["Na_5890_amplitude_err"]
+Na5896_wavelength = t["Na_5896_wavelength"] 
+Na5896_amp = t["Na_5896_amplitude"]
+Na5896_amperr = t["Na_5896_amplitude_err"]
+
+N_Na5889 = (np.abs(Na5889_amp/(Na5889_amperr.astype(float) + 1e-10)) > 3) \
+       * (chi < 3) \
+       * (Na5889_amp < -0.05) \
+       * (np.abs(Na5889_wavelength - 5889) < 2) \
+       * (Na5889_amperr.astype(float) > 0)\
+       * (snrg > 30)
+
+N_Na5896 = (np.abs(Na5896_amp/(Na5896_amperr.astype(float) + 1e-10)) > 3) \
+       * (chi < 3) \
+       * (Na5896_amp < -0.05) \
+       * (np.abs(Na5896_wavelength - 5896) < 2) \
+       * (Na5896_amperr.astype(float) > 0)\
+       * (snrg > 30)
+
+
+N_Sodiumstars = N_Na5889*N_Na5889
+
[…]

### 2018-01-18 article/ms.tex
intro abstract and method

@@
 \usepackage{ae,aecompl}
+
+\usepackage{booktabs}
+\usepackage{float}
 
@@
 
-\pubyear{2015}
+\pubyear{2018}
 
@@
 \begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
+The creation of heavy elements occurs through the slow and rapid neutron capture process.
+The site of the slow neutron capture process is known and occurs commonly throughout the Milky Way, particularly in AGB stars.
+However the site of the rapid neutron capture process is still heavily debated.
+There are many sites that could potentially create the conditions needed to synthesise r-process elements, however there have arisen issues with frequency, abundance, and probability fed from observations of our celestial neighbours in the Milky Way, that prevent us from choosing any single site for this phenomena.
+Here we show the discovery of 22 r-process (Europium) enhanced stars, double the currently known amount in our galaxy.
+The discovery of these stars, and the lack of common features they possess, implies the action of multiple different r-process sites.
+This is opposed to all r-process material being produced in small amounts in common events such as core-collapse supernovae, or the material only being produced in very large amounts in very rare events, such as neutron star mergers.
 \end{abstract}
@@
 The creation and abundance of these elements has been a key area in astrophysics research, and has been discussed and debated ever since the idea was first introduced in 1957 (\cite{Burbidge1957}).
-In the particular case of Europium (atomic number 63), almost all is produced through the r-process.
-The r-process occurs under very specific circumstances, where the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the element undergoes a $\beta$ decay.
-The sites at which this phenomena can occur are very specific, with the most favoured being early core-collapse supernovae which would have enriched gas clouds that later led to enriched star formation.
-Or more recently, neutron star mergers, as is theorised to have occurred in the case of the highly r-processed enhanced ultra-faint dwarf (UFD) galaxy Reticulum II (\cite{Ji2016}).
 
+Since it was first hypothesised 61 years ago, theorists have argued about the potential sites of the r-process.
+The r-process occurs under very specific circumstances, where the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the element undergoes a $\beta$-decay.
+The sites at which this phenomena can occur are very specific, with the most favoured being core-collapse supernovae which could enrich gas clouds that later could lead to enriched star formation.
+Or alternatively, where r-process elements are in a much higher abundance, Neutron Star Mergers or magnetorotationally driven supernovae, as is theorised to have happened in the case of the highly r-process enhanced ultra-faint dwarf (UFD) galaxy Reticulum II (\cite{Ji2016}).
+Neutron star mergers may have a stronger argument to be the parent sight of such a large amount of material being injected to a particular area, as is observed from Reticulum II.
+However, magnetorotationally driven supernovae are another possible solution.
+While they may not produce as much r-process material (although still more than core-collapse supernovae), they occur more frequently.
+
+In the particular case of Europium (atomic number 63), almost all is produced through the r-process [citation needed].
 The recent discovery of the UFD Reticulum II has sparked discussion about the origin of r-process elements.
 Historically UFD's have had some of the lowest abundance of r-process elements of any celestial body, however analysis of several of Reticulum II's stars show they are greatly enriched, to the factor of 2-3 orders of magnitude higher than stars found in any other UFD (\cite{Ji2016}).
-This measure of enrichment lends evidence to the theory that a single rare event (such as a neutron star merger) must have occurred in the galaxies formative years to enrich it, as (for Europium especially) the heavy element yields are found to be 1000 times higher than would be achieved from core-collapse supernovae ejecta.
+This measure of enrichment lends evidence to the theory that a single rare event must have occurred in the galaxies formative years to enrich it, as (for Europium especially) the heavy element yields are found to be 1000 times higher than would be achieved from core-collapse supernovae ejecta.
+As the idea that 1000 supernovae could have contributed to Reticulum II is extremely improbable, then the fact that Reticulum II is so heavily enriched is evidence that at least some r-process material must be produced by a rare astrophysical event such as a neutron star-neutron star merger, or a magnetorotationally driven supernovae.
 
-While core-collapse supernovae and neutron star mergers are likely to be the progenitors of most r-process material, that is not to say that all r-process material stems from these sources.
-Rather it might serve as an indication of the rarity of stars found to be enhanced in these elements.
+While neutron star mergers or magnetorotationally driven supernovae are likely to be the progenitors of much r-process material, that is not to say that all r-process material stems from these sources.
+Rather ithe rarity of these events might serve as an indication of the rarity of stars found to be heavily enhanced in these elements.
+What we then have to ask is can these rare events be responsible for all r-process stars found in the Milky Way, regardless of the relative strength of their abundance?
+And if not, can we then conclude that there must be multiple sites of r-process element creation throughout the Milky Way, that create these elements to different extents?
+
+To answer this question it is necessary to find and catalogue more r-process stars to find some relative fraction of enhanced stars that are either very enhanced, and so must come from a rare event.
+Or only slightly enhanced, and so they may come from a more common event that produces less material.
+However, r-process stars are unfortunately very rare, which makes finding this fraction difficult.
+For this reason we look to massive data sets, such as the LAMOST sky survey.
 \\\\
-The second data release from the LAMOST telescope catalogued close to 2 million spectra (low resolution) of giant stars.
-Of these 2 million, 454,180 were fit against a normalised spectra from a sample of 9952 giants by Anna Ho (\cite{AnnaHo2017}), and from this it became possible to analyse which giants showed an abundance or depletion of particular heavy elements.
+The second data release from the LAMOST telescope catalogued $\approx$ 2.2 million spectra (low resolution) of stars in the Northern sky.
+Of these 2.2 million, 454,180 giants were fit against a normalised spectra from a sample of 9952 giants by Anna Ho (\cite{AnnaHo2017}), and from this it became possible to analyse which giants showed an abundance or depletion of particular heavy elements.
 
@@
 The giants belong to a broad range of both metallicity and temperature, and don't cluster or trend towards any particular place in the observed sky.
-These characteristics and seeming lack-of a trend could argue that the mechanism that created these r-process enhanced stars may be general for all similar giant stars.
+These characteristics and seeming lack-of a trend could argue that there must be multiple sights of the r-process.
+While rare events such as neutron star mergers may create r-process elements in a very high abundance in localised areas, it is improbable to assume that these rare events occur commonly enough across the observed sky to explain what we see here.
+We suggest instead that there exists another r-process site that is acting alongside neutron star mergers that is far more common, but produces far less r-process material, such as core-collapse supernovae.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{423451}
+	\caption{The spectral region around two Europium absorption lines at 4129 and 4205 Angstroms.
+This particular stars spectra (black) shows clear absorption at these wavelengths, as compared to the normalised spectra of a similar star (red).}
+	\label{fig:starindex_423451}
+\end{figure}
 
@@
 
-\subsection{Observations}
-The
+\subsection{Observations and Target Selection}
+The LAMOST survey is a low resolution ($R\approx1800$) optical survey that took spectra of stars between (3650-9000 \AA).
+The LAMOST Data-Release 2 (DR2) collected spectra in this band for $\approx$ 2.2 million stars.
+Anna Ho describes in her 2017 paper (\cite{AnnaHo2017}) how she used a machine learning method named \textit{The Cannon}.
+\textit{The Cannon} fit a predictive model using 9952 LAMOST stars that were also found in the higher resolution ($R\approx22500$) APOGEE survey.
+From this Ho was able to fit normalised spectra to 454180 giants from the LAMOST survey and was restricted to between 3905 and 9000 \AA.
+
+We located potential candidate stars with an abundance of Europium by searching for deviations from the normalized spectra supplied by \textit{The Cannon}.
+A negative deviation implied an enhancement in a particular element while a positive deviation implied a depletion (compared to what the model expected).
+
+At the two main absorption lines for Europium (4129 and 4205 \AA) we fitted Gaussian profiles to each star in the 454180 giants from LAMOST DR2, and we recorded the amplitude and the wavelength of each, as well as their corresponding errors.
+The relevant stars were then found by meeting a specific set of criteria:
+
+\begin{itemize}
+	\item The amplitude of their deviation from the model needed to be less than -0.05 (remembering that a negative deviation corresponds to an enhancement in the element);
+	\item The Signal to Noise (S/N) must have been greater than 30;
+	\item The deviation from the required wavelength in question must have been less than 2 \AA;
+	\item The $\chi^{2}$ value (where the $\chi^{2}$ value represents how well the rest of the model fit the spectrum, aside from the enhancement points) must have been less 3, and;
+	\item All of these conditions must have been met for both 4129 and 4205 \AA for us to consider them sufficiently Eu enhanced.
+\end{itemize}
+
+This left us with an initial sample of 48 candidates out of the 454180 LAMOST giant sample.
+They were then visually scrutinised to find any that were clear outliers and did not belong in the sample.
+After this process we were left with 22 potentially r-process enhanced candidates.
 
@@
 e.g. Table~\ref{tab:example_table}.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{RA_v_dec_radial_velocity}
+	\caption{The right ascension and declination for the enhanced stars, coloured by radial velocity. No clear trend or significant grouping is present.}
+	\label{fig:radec_Eucands}
+\end{figure}
 
@@
 	Ji A. P., Frebel A., Chiti A., \& Simon J. D. 2016, Nature, 531
-	\bibitem[\protect\citeauthoryear{Ho, Anna Y.Q; Ness, Melissa K; Hogg, David W; Rix, Hans-Walter; Liu, Chao,; Yang, Fan; Zhang, Yong; Hou Yonhui; Wang Yuefei}{2017}]{AnnaHo2017}
+	\bibitem[\protect\citeauthoryear{Ho et al.}{2017}]{AnnaHo2017}
 	Ho A. Y. Q., Ness M. K., Hogg David W., Rix H-W., Liu C., Yang F., Zhang Y., Hou Y.,\& Wang Y. 2017, ApJ, 836, 1
@@
 \appendix
-
+\newpage
 \section{Some extra material}
@@
 
+\begin{table}
+	\centering
+	\resizebox{\textwidth}{!}{%
+		\begin{tabular}{@{}llllllllllllll@{}}
+			\toprule
+			\textbf{2MASS ID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{\begin{tabular}[c]{@{}l@{}}Vr\\ (km/s)\end{tabular}} & \textbf{Teff} & \textbf{Logg} & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\chi^{2}$} & \textbf{\begin{tabular}[c]{@{}l@{}}{[}Eu/Fe{]}\\ at 4129\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}{[}Eu/Fe{]}\\ at 4129 error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}{[}Eu/Fe{]}\\ at 4205\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}{[}Eu/Fe{]}\\ at 4205 error\end{tabular}} \\ \midrule
+			J063400.95+420904.3 & 34:01.0 & +42:09:04.4 & 34.09 & 9.89 & 4315.56 & 1.62 & -0.50 & 0.10 & 0.43 & 1.02 & 3.09 & 1.35 & 0.22 \\ \midrule
+			J220118.66+033558.6 & 01:18.7 & +03:35:58.6 & 35.11 & -108.23 & 4790.06 & 2.51 & -1.36 & 0.33 & 0.37 & 1.51 & 0.03 & 1.38 & 0.16 \\ \midrule
+			J060021.29+384840.6 & 00:21.3 & +38:48:40.6 & 30.03 & 32.68 & 4305.08 & 2.10 & 0.15 & -0.01 & 0.54 & 1.48 & 0.29 & 1.51 & 0.04 \\ \midrule
+			J025225.88+324308.1 & 52:25.9 & +32:43:08.2 & 34.79 & 24.88 & 4797.58 & 2.52 & -0.23 & 0.05 & 0.24 & 1.32 & 0.16 & 1.31 & 0.14 \\ \midrule
+			J163116.81+002349.5 & 31:16.8 & +00:23:49.5 & 32.63 & -35.98 & 4628.92 & 2.53 & 0.01 & 0.18 & 0.29 & 1.37 & 0.25 & 1.51 & 0.03 \\ \midrule
+			J153333.12+510621.8 & 33:33.1 & +51:06:21.9 & 49.45 & -17.99 & 4861.78 & 2.51 & -0.49 & 0.22 & 0.46 & 1.33 & 0.16 & 1.29 & 0.12 \\ \midrule
+			J075116.55+220137.8 & 51:16.6 & +22:01:37.9 & 32.87 & 90.24 & 4810.60 & 2.70 & -0.33 & 0.02 & 0.30 & 1.38 & 0.18 & 1.32 & 0.15 \\ \midrule
+			J003929.43+430039.5 & 39:29.4 & +43:00:39.6 & 33.14 & -104.33 & 4190.26 & 1.87 & -0.01 & 0.07 & 0.41 & 1.37 & 0.19 & 1.33 & 0.19 \\ \midrule
+			J071206.83+213038.0 & 12:06.8 & +21:30:38.1 & 32.66 & 29.08 & 4432.03 & 1.75 & -0.38 & 0.11 & 0.40 & 1.51 & 0.03 & 1.43 & 0.19 \\ \midrule
+			J222820.22+340750.3 & 28:20.2 & +34:07:50.3 & 34.52 & -45.27 & 4419.96 & 2.06 & -0.07 & 0.11 & 0.49 & 1.36 & 0.17 & 1.38 & 0.17 \\ \midrule
+			J222310.49+344357.4 & 23:10.5 & +34:43:57.5 & 54.06 & -20.09 & 4232.66 & 1.87 & -0.01 & 0.03 & 0.86 & 1.27 & 0.09 & 1.18 & 0.21 \\ \midrule
+			J222101.61+365923.6 & 21:01.6 & +36:59:23.7 & 30.81 & -27.88 & 4360.28 & 2.23 & 0.20 & 0.04 & 0.45 & 1.51 & 0.03 & 1.42 & 0.21 \\ \midrule
+			J074102.63+130520.3 & 41:02.6 & +13:05:20.4 & 40.83 & 49.17 & 5000.84 & 3.00 & -0.38 & -0.02 & 0.30 & 1.27 & 0.15 & 1.42 & 0.12 \\ \midrule
+			J061559.10+470344.9 & 15:59.1 & +47:03:44.9 & 36.84 & -18.29 & 4811.98 & 2.82 & -0.59 & 0.07 & 0.44 & 0.63 & 1.30 & 1.37 & 0.13 \\ \midrule
+			J054704.12+600827.1 & 47:04.1 & +60:08:27.1 & 33.19 & -23.33 & 4770.80 & 2.64 & -0.10 & 0.06 & 0.40 & 1.51 & 0.03 & 1.40 & 0.16 \\ \midrule
+			J042723.73+271546.8 & 27:23.7 & +27:15:46.9 & 45.73 & -40.17 & 4211.91 & 1.72 & -0.04 & 0.05 & 0.79 & 1.36 & 0.20 & 1.30 & 0.18 \\ \midrule
+			J035702.05+281335.2 & 57:02.1 & +28:13:35.3 & 31.82 & -44.67 & 4712.89 & 2.44 & 0.01 & 0.16 & 0.46 & 1.35 & 0.14 & 1.22 & 0.29 \\ \midrule
+			J091256.32+353008.3 & 12:56.3 & +35:30:08.3 & 73.39 & 20.39 & 4441.95 & 2.33 & 0.41 & 0.02 & 0.76 & 0.61 & 0.30 & 1.24 & 0.14 \\ \midrule
+			J071534.00+211353.8 & 15:34.0 & +21:13:53.9 & 31.68 & 42.27 & 4892.00 & 2.57 & -0.72 & 0.11 & 0.34 & -0.20 & 0.00 & 1.38 & 0.21 \\ \midrule
+			J101317.14+122928.8 & 13:17.1 & +12:29:28.8 & 45.54 & 300.69 & 5055.95 & 2.24 & -1.34 & 0.33 & 0.38 & 1.51 & 0.03 & 1.41 & 0.14 \\ \midrule
+			J161326.00+073218.1 & 13:26.0 & +07:32:18.2 & 48.45 & -50.07 & 5086.79 & 3.40 & -0.68 & 0.29 & 0.93 & 1.44 & 0.11 & 1.32 & 0.08 \\ \midrule
+			J173711.85+101126.6 & 37:11.9 & +10:11:26.7 & 30.01 & -33.58 & 4991.07 & 3.49 & -0.05 & 0.17 & 0.41 & 1.40 & 0.15 & 1.50 & 0.13 \\ \bottomrule
+		\end{tabular}%
+	}
+	\caption{My caption}
+	\label{my-label}
+\end{table}
+
 % Don't change these lines

### 2018-01-22 article/ms.tex
minor

@@
 % Keep the title short and informative.
-\title[Research is fun, max. 45 characters]{You can't spell Euphoric without Eu.}
+\title[Discovery of r-process stars in LAMOST]{Discovery of $r$-process stars in LAMOST}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[Matthew T. Miles et al.]{
-Matthew T. Miles,$^{1}$\thanks{E-mail: mtmil3@student.monash.edu}
-A. N. Other,$^{2}$
-Third Author$^{2,3}$
-and Fourth Author$^{3}$
+\author[Matthew T. Miles et al.]{Matthew T. Miles,$^{1}$\thanks{E-mail: mtmil3@student.monash.edu}
+Andrew R. Casey,$^{1,2}$
+Brodie Norfolk?,$^{1}$
+Alex Kemp?,$^{1}$\newauthor
+John Lattanzio?,$^{1}$
+Kevin Schlaufman?,$^{3}$
+Alexander P. Ji?,$^{4}$
+\emph{et al?}
 \\
 % List of institutions
-$^{1}$School of Physics and Astronomy, Monash University, Clayton Campus, Victoria 3800\\
-$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
-$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
+$^{1}$School of Physics and Astronomy, Monash University, Clayton Campus, Victoria 3800, Australia\\
+$^{2}$Faculty of Information Technology, Monash University, Clayton Campus, Victoria 3800, Australia\\
+$^{3}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA\\
+$^{4}$Carnegie Observatories
 }

### 2018-01-22 article/ms.tex
minor

@@
 \usepackage{graphicx}	% Including figure files
+\usepackage{color}
 \usepackage{amsmath}	% Advanced maths commands
 \usepackage{amssymb}	% Extra maths symbols
+
+\newcommand{\todo}[1]{\textcolor{red}{#1}}
 
@@
 
-Heavy elements (those with an atomic number greater than 30) must be synthesized using the slow (s) and rapid (r) neutron capture processes (\cite{Sneden2008}).
+Heavy elements ($Z > 30$) are synthesised through the slow (s) and rapid (r) neutron capture processes (\cite{Sneden2008}).
 The creation and abundance of these elements has been a key area in astrophysics research, and has been discussed and debated ever since the idea was first introduced in 1957 (\cite{Burbidge1957}).
@@
 Or alternatively, where r-process elements are in a much higher abundance, Neutron Star Mergers or magnetorotationally driven supernovae, as is theorised to have happened in the case of the highly r-process enhanced ultra-faint dwarf (UFD) galaxy Reticulum II (\cite{Ji2016}).
-Neutron star mergers may have a stronger argument to be the parent sight of such a large amount of material being injected to a particular area, as is observed from Reticulum II.
+Neutron star mergers may have a stronger argument to be the parent site of such a large amount of material being injected to a particular area, as is observed from Reticulum II.
 However, magnetorotationally driven supernovae are another possible solution.
+% While which may not produce much material? Be specific!
+% Also: it is almost impossible for us to distinguish an abundance signature as coming from a NS merger compared to a MRDSN, so normally they are thrown into the same bucket when discussing them.
+Keep that of mind.
 While they may not produce as much r-process material (although still more than core-collapse supernovae), they occur more frequently.
 
-In the particular case of Europium (atomic number 63), almost all is produced through the r-process [citation needed].
+In the particular case of Europium (atomic number 63), is almost entirely produced through the r-process [citation needed].
 The recent discovery of the UFD Reticulum II has sparked discussion about the origin of r-process elements.
+% The above statement is not entirely true: there has been constant discussion about the r-process origin, but the discovery of Reticulum II marked a very interesting case where: (i) lots of r-process material was found and (ii) the environment meant that CCSN could be entirely excluded.
  Historically UFD's have had some of the lowest abundance of r-process elements of any celestial body, however analysis of several of Reticulum II's stars show they are greatly enriched, to the factor of 2-3 orders of magnitude higher than stars found in any other UFD (\cite{Ji2016}).
@@
 \\\\
-The second data release from the LAMOST telescope catalogued $\approx$ 2.2 million spectra (low resolution) of stars in the Northern sky.
+The second data release from the LAMOST telescope catalogued $\approx$ 2.2 million spectra (low resolution) of stars in the northern sky.
 Of these 2.2 million, 454,180 giants were fit against a normalised spectra from a sample of 9952 giants by Anna Ho (\cite{AnnaHo2017}), and from this it became possible to analyse which giants showed an abundance or depletion of particular heavy elements.
 
+% 22 or 48? We report on 48, where 22 are more likely.
 In this letter we report the probable discovery of 22 of these LAMOST giants that show enhanced r-process peaks for Europium at both 4129 and 4205 Angstroms.
-The giants belong to a broad range of both metallicity and temperature, and don't cluster or trend towards any particular place in the observed sky.
+\todo{In Section X we do blah,...}
+
+% Move this to discussion!
+% The giants belong to a broad range of both metallicity and temperature, and don't cluster or trend towards any particular place in the observed sky.
 These characteristics and seeming lack-of a trend could argue that there must be multiple sights of the r-process.
@@
 
-\section{Methods, Observations, Simulations etc.}
-Normally the next section describes the techniques the authors used.
-It is frequently split into subsections, such as Section~\ref{sec:maths} below.
+\section{Methods}
 
-\subsection{Observations and Target Selection}
+\subsection{Observations and Candidate Selection}
 The LAMOST survey is a low resolution ($R\approx1800$) optical survey that took spectra of stars between (3650-9000 \AA).
@@
 \textit{The Cannon} fit a predictive model using 9952 LAMOST stars that were also found in the higher resolution ($R\approx22500$) APOGEE survey.
-From this Ho was able to fit normalised spectra to 454180 giants from the LAMOST survey and was restricted to between 3905 and 9000 \AA.
+From this Ho was able to fit normalised spectra to 454,180 giants from the LAMOST survey and was restricted to between 3905\,\AA\ and 9000\,\AA.
+% What labels did Anna Ho predict? What's the typical precision of those labels?
 
+% Located? Selected?
 We located potential candidate stars with an abundance of Europium by searching for deviations from the normalized spectra supplied by \textit{The Cannon}.
@@
 
-At the two main absorption lines for Europium (4129 and 4205 \AA) we fitted Gaussian profiles to each star in the 454180 giants from LAMOST DR2, and we recorded the amplitude and the wavelength of each, as well as their corresponding errors.
-The relevant stars were then found by meeting a specific set of criteria:
+At the two main absorption lines for Europium (4129\,\AA\ and 4205\,\AA) we fitted Gaussian profiles to each star in the 454,180 giants from LAMOST DR2, and we recorded the amplitude and the wavelength of each, as well as their corresponding errors.
+Candidate Eu-enhanced stars were identified by stars that met the following criteria:
 
@@
 After this process we were left with 22 potentially r-process enhanced candidates.
-
-\subsection{Maths}
-\label{sec:maths}
-
-Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
-or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
-as a numbered equation:
-
-\begin{equation}
-    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
-	\label{eq:quadratic}
-\end{equation}
-
-Refer back to them as e.g. equation~(\ref{eq:quadratic}).
-
-\subsection{Figures and tables}
-
-Figures and tables should be placed at logical positions in the text. Don't
-worry about the exact layout, which will be handled by the publishers.
-
-Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
-e.g. Table~\ref{tab:example_table}.
+% The above statement isn't true is it? Didn't you have >>48 candidates that you culled to 48, and then 22 stars looked really good by comparison?
 
@@
 
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{example}
-    \caption{This is an example figure. Captions appear below each figure.
-	Give enough detail for the reader to understand what they're looking at,
-	but leave detailed discussion to the main body of the text.}
-    \label{fig:example_figure}
-\end{figure}
+\section{Discussion}
 
-\begin{table}
-	\centering
-	\caption{This is an example table. Captions appear above each table.
-	Remember to define the quantities, symbols and units used.}
-	\label{tab:example_table}
-	\begin{tabular}{lccr} % four columns, alignment for each
-		\hline
-		A & B & C & D\\
-		\hline
-		1 & 2 & 3 & 4\\
-		2 & 4 & 6 & 8\\
-		3 & 5 & 7 & 9\\
-		\hline
-	\end{tabular}
-\end{table}
+\begin{itemize}
+\item Your discussion points! 
+\end{itemize}
 
@@
 
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
+\begin{itemize}
+\item Largest sample of r-process stars discovered to date
+\item Found at all metallicities (not just metal-poor stars), found at all temperatures/logg values so not something that is particularly biased in one part of the H-R diagram  (indicating we are probably not strongly biased to/against a particular kind of star)
+\item Found in the disk/halo all across the sky
+\item Orbits necessary for distinguishing origin. Encourage high-resolution follow-up and orbit analysis after Gaia DR2+
+\end{itemize}
 

### 2018-01-22 article/ms.tex
update before merge

--- 2018-01-18 article/ms.tex
@@
 
-\subsection{Maths}
-\label{sec:maths}
-
-Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
-or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
-as a numbered equation:
-
-\begin{equation}
-    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
-	\label{eq:quadratic}
-\end{equation}
-
-Refer back to them as e.g. equation~(\ref{eq:quadratic}).
-
-\subsection{Figures and tables}
-
-Figures and tables should be placed at logical positions in the text. Don't
-worry about the exact layout, which will be handled by the publishers.
-
-Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
-e.g. Table~\ref{tab:example_table}.
-
 \begin{figure}
@@
 
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{example}
-    \caption{This is an example figure. Captions appear below each figure.
-	Give enough detail for the reader to understand what they're looking at,
-	but leave detailed discussion to the main body of the text.}
-    \label{fig:example_figure}
-\end{figure}
-
-\begin{table}
-	\centering
-	\caption{This is an example table. Captions appear above each table.
-	Remember to define the quantities, symbols and units used.}
-	\label{tab:example_table}
-	\begin{tabular}{lccr} % four columns, alignment for each
-		\hline
-		A & B & C & D\\
-		\hline
-		1 & 2 & 3 & 4\\
-		2 & 4 & 6 & 8\\
-		3 & 5 & 7 & 9\\
-		\hline
-	\end{tabular}
-\end{table}
+\section{Discussion points}
+\begin{itemize}
+	\item \textbf{consider CCSN}
+	\item \textbf{consider NS-NS}
+	\item \textbf{consider the things about our stars that mean it can't be just one of these. i.e differing Rad vels, much different positions, speed travelling vs age of galaxy vs frequency of NS-NS} 
+	\item \textbf{consider abundances, lower abundances don't fit NS-NS model, high abundances don't fit CCSN model.}
+	\item \textbf{consider then, that the solution is both.}
+	\item \textbf{there has to be some kind of statistical argument we can make on this one I reckon, find it.}
+\end{itemize}
 
@@
 \newpage
+
 \section{Some extra material}

### 2018-01-24 article/ms.tex

--- 2018-01-22 article/ms.tex
@@
 	\begin{abstract}
-The creation of heavy elements occurs through the slow and rapid neutron capture process.
-The site of the slow neutron capture process is known and occurs commonly throughout the Milky Way, particularly in AGB stars.
-However the site of the rapid neutron capture process is still heavily debated.
-There are many sites that could potentially create the conditions needed to synthesise r-process elements, however there have arisen issues with frequency, abundance, and probability fed from observations of our celestial neighbours in the Milky Way, that prevent us from choosing any single site for this phenomena.
-Here we show the discovery of 22 r-process (Europium) enhanced stars, double the currently known amount in our galaxy.
+		The creation of heavy elements occurs through the slow and rapid neutron capture process, however the site of the rapid neutron capture process is still heavily debated.
+There are many sites that could potentially create the conditions needed to synthesise r-process elements, but there have arisen issues with frequency, abundance, and probability fed from observations of our celestial neighbours in the Milky Way.
+These prevent us from choosing any single site for this phenomena.
+Here we show the discovery of 47 r-process (Europium) enhanced stars, over double the currently known amount in our galaxy.
+Additionally we provide the first quantitative analysis of whether neutron star mergers are able to produce all r-process material currently known.
 The discovery of these stars, and the lack of common features they possess, implies the action of multiple different r-process sites.
@@
 Neutron star mergers may have a stronger argument to be the parent site of such a large amount of material being injected to a particular area, as is observed from Reticulum II.
-However, magnetorotationally driven supernovae are another possible solution.
-% While which may not produce much material? Be specific!
-% Also: it is almost impossible for us to distinguish an abundance signature as coming from a NS merger compared to a MRDSN, so normally they are thrown into the same bucket when discussing them.
-Keep that of mind.
-While they may not produce as much r-process material (although still more than core-collapse supernovae), they occur more frequently.
+However, magnetorotationally driven supernovae (MRDSN) are another possible solution.
 
-In the particular case of Europium (atomic number 63), is almost entirely produced through the r-process [citation needed].
-The recent discovery of the UFD Reticulum II has sparked discussion about the origin of r-process elements.
-% The above statement is not entirely true: there has been constant discussion about the r-process origin, but the discovery of Reticulum II marked a very interesting case where: (i) lots of r-process material was found and (ii) the environment meant that CCSN could be entirely excluded.
+	While MRDSN may not produce as much r-process material (although still more than core-collapse supernovae), they occur more frequently than neutron star mergers, and enough material is produced that it is currently impossible to distinguish between them through abundance signatures.
+
+	In the particular case of Europium (atomic number 63), it is almost entirely produced through the r-process [\todo{citation needed}].
+The recent discovery of the UFD Reticulum II has marked a particularly interesting case where the level of r-process element enrichment could not have come from a core-collapse supernovae.
+
 	Historically UFD's have had some of the lowest abundance of r-process elements of any celestial body, however analysis of several of Reticulum II's stars show they are greatly enriched, to the factor of 2-3 orders of magnitude higher than stars found in any other UFD (\cite{Ji2016}).
 This measure of enrichment lends evidence to the theory that a single rare event must have occurred in the galaxies formative years to enrich it, as (for Europium especially) the heavy element yields are found to be 1000 times higher than would be achieved from core-collapse supernovae ejecta.
-As the idea that 1000 supernovae could have contributed to Reticulum II is extremely improbable, then the fact that Reticulum II is so heavily enriched is evidence that at least some r-process material must be produced by a rare astrophysical event such as a neutron star-neutron star merger, or a magnetorotationally driven supernovae.
+As the idea that 1000 supernovae could have contributed to Reticulum II is extremely improbable, then the fact that Reticulum II is so heavily enriched is evidence that at least some r-process material must be produced by a rare astrophysical event such as a neutron star-neutron star merger, or a MRDSN.
 
@@
 For this reason we look to massive data sets, such as the LAMOST sky survey.
-\\\\
+
 	The second data release from the LAMOST telescope catalogued $\approx$ 2.2 million spectra (low resolution) of stars in the northern sky.
@@
 
-% 22 or 48? We report on 48, where 22 are more likely.
-In this letter we report the probable discovery of 22 of these LAMOST giants that show enhanced r-process peaks for Europium at both 4129 and 4205 Angstroms.
-\todo{In Section X we do blah,...}
-
-% Move this to discussion!
-% The giants belong to a broad range of both metallicity and temperature, and don't cluster or trend towards any particular place in the observed sky.
-These characteristics and seeming lack-of a trend could argue that there must be multiple sights of the r-process.
-While rare events such as neutron star mergers may create r-process elements in a very high abundance in localised areas, it is improbable to assume that these rare events occur commonly enough across the observed sky to explain what we see here.
-We suggest instead that there exists another r-process site that is acting alongside neutron star mergers that is far more common, but produces far less r-process material, such as core-collapse supernovae.
+	In this letter we report the probable discovery of 47 of these LAMOST giants that show enhanced r-process peaks for Europium at both 4129 and 4205 Angstroms.
+	\todo{In Section X we do etc,...}
 
@@
 This particular stars spectra (black) shows clear absorption at these wavelengths, as compared to the normalised spectra of a similar star (red).}
+		\label{fig:starindex_423451}
+	\end{figure}
+
+	\begin{figure}
+		\includegraphics[width=\columnwidth]{NoTrend}
+		\caption{The apparent lack of trends for the 47 enhanced stars. In three distinguishing categories: Metallicity (left), Effective Temperature (centre), and $log(g)$ (right).}
 		\label{fig:starindex_423451}
@@
 \textit{The Cannon} fit a predictive model using 9952 LAMOST stars that were also found in the higher resolution ($R\approx22500$) APOGEE survey.
+\textit{The Cannon} was used to predict the labels $T_{eff}$, $log_{10}[g]$, $[Fe/H]$, and $[\alpha/Fe]$.
 From this Ho was able to fit normalised spectra to 454,180 giants from the LAMOST survey and was restricted to between 3905\,\AA\ and 9000\,\AA.
-% What labels did Anna Ho predict? What's the typical precision of those labels?
+For reference, typical uncertainties for these labels are $70K$ for $T_{eff}$, $0.1$ in $log_{10}[g]$, 0.1 in $[Fe/H]$, and 0.04 in $[\alpha/H]$.
 
-% Located? Selected?
-We located potential candidate stars with an abundance of Europium by searching for deviations from the normalized spectra supplied by \textit{The Cannon}.
+	We selected potential candidate stars with an abundance of Europium by searching for deviations from the normalized spectra supplied by \textit{The Cannon}.
 A negative deviation implied an enhancement in a particular element while a positive deviation implied a depletion (compared to what the model expected).
@@
 
-This left us with an initial sample of 48 candidates out of the 454180 LAMOST giant sample.
-They were then visually scrutinised to find any that were clear outliers and did not belong in the sample.
-After this process we were left with 22 potentially r-process enhanced candidates.
-% The above statement isn't true is it? Didn't you have >>48 candidates that you culled to 48, and then 22 stars looked really good by comparison?
+	This left us with an initial sample of approximately 100 candidates out of the 454180 LAMOST giant sample.
+These were then visually scrutinised to find any that were clear outliers and did not belong in the sample.
+After this process we were left with 47 potentially r-process enhanced candidates, 22 of which stand out as very good candidates by comparison.
 
 	\begin{figure}
-	\includegraphics[width=\columnwidth]{RA_v_dec_radial_velocity}
+		\includegraphics[width=\columnwidth]{RA_DEC_RadVel_48}
 		\caption{The right ascension and declination for the enhanced stars, coloured by radial velocity. No clear trend or significant grouping is present.}
@@
 
-\section{Discussion}
+	\section{The r-process}
+	For the r-process to occur there must be a very large neutron density, such that neutron capture must be able to occur before the nucleus undergoes a $\beta$-decay (assuming the nucleus is in an unstable state).
+The conditions that can create this are rare.
+Events such as supernovae or neutron star mergers list among the most favoured sites.
 
+	\subsection{Selection effects}
+	The LAMOST giants we analyse belong to a broad range of both metallicity and temperature, and don't cluster or trend towards any particular place in the observed sky.
+These characteristics and seeming lack-of a trend could argue that there must be multiple sites of the r-process.
+While rare events such as neutron star mergers may create r-process elements in a very high abundance in localised areas, it is improbable to assume that these rare events occur commonly enough across the observed sky to explain what we see here.
+We suggest instead that there exists another r-process site that is acting alongside neutron star mergers that is far more common, but produces far less r-process material, such as core-collapse supernovae.
+
+	The previous sample of r-process stars, before the release of this letter, almost totally consists of metal-poor stars.
+This fact is not to be confused with saying that most r-process stars found should be metal-poor stars, rather that at low metallicities we know that the s-process will not contribute.
+So neutron capture elements formed from these stars would be only from the r-process.
+Similarly, over half the current known r-process stars come from a very metal poor ultra faint dwarf galaxy, Reticulum II.
+However, Europium we know to be almost totally made from the r-process, therefore even at metallicities where the s-process would be active, Europium is a valuable indication of r-process synthesis.
+
+	\subsection{Core-collapse supernovae}
+	Core-collapse supernova was the site initially proposed to have a high enough neutron density in order to create elements synthesised by the r-process.
+The exact mechanism that leads to this high neutron density is so far unknown, but there have been promising theories and models in recent years that can explain r-process element synthesis in these conditions to an adequate degree.
+One of which is the action of high-entropy neutrino winds being released from a proto-neutron star during core-collapse.
+In this stage of the collapse, this neutrino loss is the driving factor behind mass loss and could be instrumental in the existence of the r-process in supernovae conditions.
+However how much enhanced material is released from the event is very dependant on the amount of material that falls back onto the remnant at the arrival of the reverse shock, and so often it may not release enough material to always be considered a site at which r-process material is expelled (\cite{Woosley1992}).
+Regardless of the exact mechanism, core-collapse supernovae seem to release $M_{Eu}\approx10^{-8}$ (\cite{Argast2004}) solar masses.
+While this may not be a particularly significant amount, core-collapse supernovae occur frequently in the Milky Way, and so it isn't unreasonable to suggest that much if not all r-process material could have been formed by these and recycled in the stars we present in this letter.
+
+	\subsection{Neutron star mergers}
+	\label{NSmerg}
+	Neutron star mergers are another favoured possible site of r-process element synthesis, possibly the most favoured at the moment.
+They are easily able to meet the conditions for a high neutron density as interacting tidal forces between the stars rip away neutron dense material allowing r-process element synthesis to occur easily.
+In this interaction they produce a considerable amount more enriched material than core-collapse supernovae ($M_{Eu}\approx10^{-4.5}$) (\cite{Goriely2011}), however the direct interaction and merger of a binary neutron star pair occurs very infrequently with only one ever having been directly observed, and with an upper frequency estimate of $12600\ Gpc^{-3}yr^{-1}$ (\cite{LIGO2016}).
+The massive amount of material that these mergers release could more than make up for the low frequency and so, similar to core-collapse supernovae, it is not unreasonable to suggest that they are responsible for most if not all known r-process material.
+
+	The recent discovery of the UFD Reticulum II (\cite{Ji2016}) is evidence against the case for a single r-process site.
+Of nine stars observed in Reticulum II, 7 of them were shown to be highly enriched in r-process elements ([Eu/Fe]~1.7) which suggests a single prolific event having occurred in close proximity to the galaxy early in it's formation, such as a neutron star merger.
+However, two of the stars observed were only weakly enhanced in r-process elements which suggests that there must have been a second, less efficient, form of r-process enhancement present.
+
+	\subsection{The rate of neutron star mergers, what we expect, what we find}
+	From the recent aLIGO data \cite{LIGO2016}, we are able to find an estimate for an upper-bound frequency at which neutron star mergers occur, as mentioned in section \ref{NSmerg}. 
+	Using this we were able to find:
 	\begin{itemize}
-\item Your discussion points! 
+		\item An estimate for the amount of r-process stars that should be present in the Milky Way that have been enhanced through neutron star mergers.
+Assuming instant recycling in that any star that dies is instantly formed into a new star, also assuming that no r-process matter pollutes other stars by any other means than this.
+		\item An estimate of how many r-process enhanced giants should be present from an estimate number of the Milky Way's total stars.
+		\item An estimate of how many r-process enhanced stars (giants or otherwise) that should be present from an estimate number of the Milky Way's total stars.
 	\end{itemize}
 
+	In preparing these calculations we assumed a constant star formation rate, 2 M$_\odot yr^{-1}$, in the disk of the Milky Way, r=15kpc, with a typical IMF and giant star birth rate of approximately $0.3\ $stars per year.
+We also assumed the lifetime between $\log{g} = 3.2$ and the end of the core-helium burning phase is about $250\,{\rm Myr}$.
+Therefore if we assume a steady-state system, the number of giant stars in the Milky Way comes to approximately $7.53\times10^7$.
+This allowed us to find the percentage of the Milky Ways stars that our sample represents.
+\todo{I tried to make this explanation a fair bit different, let me know if it needs further changes.}
+
+	In these calculations we also say that a star is said to be enhanced if [Eu/Fe] >= 0.7, and performed the low-bound estimate that all of our 47 stars exhibited this abundance.
+Additionally the amount of r-process material is the same as previously discussed, using Europium as our identifier, of $M_{Eu}\approx10^{-4.5}$.
+
+    We found from this that in the Milky Way alone there should be present 125589 r-process enhanced stars.
+Considering this should be considered a lower-bound estimate (by using the maximum rate for neutron star mergers, and assuming the lower bound Europium abundance) this is a startlingly large difference from the now updated known amount of r-process enhanced stars which comes to 60.
+
+    We also find that, of our sample of $\approx450000$ giants, the amount of r-process enhanced stars we should have find comes to less than one (0.226).
+Similarly if we are to extend our sample from the 450000 giants supplied by Anna Ho, and instead use the entire LAMOST data release 2 (a survey of $\approx2.2$ million stars), we predict that we should have found 1.11 stars enhanced in the r-process.
+While again this should be considered a lower bound, it is still a startling difference from the 47 that we found in our sample.
+
+    From these estimates we can also find an approximation for whether or not neutron star mergers by themselves are sufficient to enrich our entire r-process enhanced catalogue.
+We find that, by using the assumptions listed, neutron star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for all 60 known r-process enhanced stars within $1.1\times10^9$ years.
+
+	%From Andy's Lithium paper.
+%	I star formation rate of $2\,M_\odot\,{\rm yr}^{-1}$ and a typical initial mass function\cite{Kroupa_2001} and find a birth rate of giant stars in the Milky Way (the main-sequence turn-off rate) of about $0.3\,{\rm stars}\,{\rm yr}^{-1}$.
+%	We considered stellar masses between $0.1\,M_\odot$ and $100\,M_\odot$ when weighting the initial mass function.
+%	For an evolutionary track \cite{MIST_Dotter,MIST_Choi} of a $1.3\,M_\odot$ solar-metallicity star, the lifetime between $\log{g} = 3.2$ and the end of the core-helium burning phase is about $250\,{\rm Myr}$.
+Thus, assuming a steady-state system, the number of giant stars in the Milky Way with $\log{g} < 3.2$ is about $7.5\times10^7$.
+
+	\subsection{Multiple r-process sites?}
+	While we've shown that all r-process material that we currently know of can be made by neutron star mergers, we still have cases of stars in the galaxy which show particularly weak enrichment from r-process elements ([Eu/Fe] < 0.7).
+While these enhancements are small, they are still very important as it implies that another site of r-process element synthesis is likely to be active.
+The neutron star merger rates may show that all heavily enriched stars can be enhanced by these phenomena within an adequate timescale, but we are not able to assume that as a consequence of the merger some stars are greatly enhanced, while others are only very slightly enhanced.
+Therefore it is better to assume that at least two sites exist, with one (potentially mergers) producing a massive abundance of enhanced material, and the other only producing some small amount, such as supernovae.
+
 	\section{Conclusions}
+	We present the largest to date sample of r-process element enhanced stars.
+These stars are found at a wide range of metallicities, contrary to previous discovery of only metal-poor r-process enhanced stars.
+Similarly they seem to show no trend in either temperatures, $log(g)$, or radial velocity.
+They don't cluster to any one end of the H-R diagram, so it is likely there is no correlation between type of star.
+They are found both in the disk and halo, and are not clustered anywhere in the sky.
+In addition to this we also present the first ever quantitative analysis, from information provided by aLIGO, that neutron star mergers possess the ability to synthesise all currently known r-process material in a feasible timescale.
 
-\begin{itemize}
-\item Largest sample of r-process stars discovered to date
-\item Found at all metallicities (not just metal-poor stars), found at all temperatures/logg values so not something that is particularly biased in one part of the H-R diagram  (indicating we are probably not strongly biased to/against a particular kind of star)
-\item Found in the disk/halo all across the sky
-\item Orbits necessary for distinguishing origin. Encourage high-resolution follow-up and orbit analysis after Gaia DR2+
-\end{itemize}
+	We recommend follow-up high resolution spectra be obtained for each of the 60 stars to ascertain how enhanced they are.
+To find the origin of these stars and to show whether or not they may come from a similar progenitor site it is necessary to find orbits for them.
+We encourage orbit analysis after further Gaia data releases should these stars be present in them.
 
@@
 
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
+	We acknowledge Andrew Casey for reminding us of the volume of a sphere. Further acknowledgements are awarded to him for firing me less than the other two, so far.
 
@@
 	\begin{thebibliography}{99}
-	\bibitem[\protect\citeauthoryear{Sneden, Christopher; Cowan, John J; Gallino, Roberto}{2008}]{Sneden2008}
+		\bibitem[\protect\citeauthoryear{Sneden, C. et al.}{2008}]{Sneden2008}
 		Sneden C., Cowan J.J., \& Gallino R. 2013, Annual review of Astronomy \& Astrophysics, 46, 1
-	\bibitem[\protect\citeauthoryear{Ji, Alexander P.; Frebel, Anna; Chiti, Anirudh; Simon, Joshua D.}{2016}]{Ji2016}
+		\bibitem[\protect\citeauthoryear{Ji, A. P. et al.}{2016}]{Ji2016}
 		Ji A. P., Frebel A., Chiti A., \& Simon J. D. 2016, Nature, 531
@@
 		Ho A. Y. Q., Ness M. K., Hogg David W., Rix H-W., Liu C., Yang F., Zhang Y., Hou Y.,\& Wang Y. 2017, ApJ, 836, 1
-	\bibitem[\protect\citeauthoryear{Burbidge, E. Margaret; Burbidge, G.R.; Fowler, William A.; Hoyle, F}{1957}]{Burbidge1957}
+		\bibitem[\protect\citeauthoryear{Burbidge, E. et al.}{1957}]{Burbidge1957}
 		Burbidge E. M., Burbidge G. R., Fowler W. A., \& Hoyle F. 1957, Review of Modern Physics, 29, 4
+		\bibitem[\protect\citeauthoryear{Goriely, S. et al.}{2011}]{Goriely2011}
+		Goriely S., Bauswein A. \& Janka H-T. 2011, ApJ, 738, L32
+		\bibitem[\protect\citeauthoryear{Abbott, B.P. et al.}{2016}]{LIGO2016}
+		Abbot B.P. et al. 2011, ApJ, 832, L21
+		\bibitem[\protect\citeauthoryear{Argast, D. et al.}{2004}]{Argast2004}
+		Argast D., Samland M., Thielmann F-K. \& Qian Y-Z. 2004, Astronomy and Astrophysics, 416
+		\bibitem[\protect\citeauthoryear{Woosley, S.E. et al.}{1992}]{Woosley1992}
+		Woosley S.E, \& Hoffman R.D. 1992, ApJ, 395, 1
 	\end{thebibliography}
@@
 	\appendix
-\newpage
 	\section{Some extra material}
@@
 
-\begin{table}
+	\begin{table*}
 		\centering
@@
 		}
-	\caption{My caption}
-	\label{my-label}
-\end{table}
+		\caption{Abundances and additional information of the comparatively very good candidates. Abundances were found from the LAMOST data.}
+		\label{Eu for the great 22}
+	\end{table*}
 

### 2018-01-25 article/ms.tex
new drapht, fixed some stuff

@@
 	From the recent aLIGO data \cite{LIGO2016}, we are able to find an estimate for an upper-bound frequency at which neutron star mergers occur, as mentioned in section \ref{NSmerg}. 
-	Using this we were able to find:
+	Using this we are able to find:
 	\begin{itemize}
@@
 
-	In these calculations we also say that a star is said to be enhanced if [Eu/Fe] >= 0.7, and performed the low-bound estimate that all of our 47 stars exhibited this abundance.
-Additionally the amount of r-process material is the same as previously discussed, using Europium as our identifier, of $M_{Eu}\approx10^{-4.5}$.
+	In these calculations we also say that a star is said to be enhanced if [Eu/Fe] $\geq$ 0.7, and performed the low-bound estimate that all of our 47 stars exhibited this abundance.
+Additionally the amount of r-process material expelled is the same as previously discussed, using Europium as our identifier, of $M_{Eu}\approx10^{-4.5}$.
 
@@
 
-    We also find that, of our sample of $\approx450000$ giants, the amount of r-process enhanced stars we should have find comes to less than one (0.226).
-Similarly if we are to extend our sample from the 450000 giants supplied by Anna Ho, and instead use the entire LAMOST data release 2 (a survey of $\approx2.2$ million stars), we predict that we should have found 1.11 stars enhanced in the r-process.
+    We also find that, of our sample of $\approx450000$ giants, the amount of r-process enhanced stars we should find comes to less than one (0.224).
+Similarly if we are to extend our sample from the 450000 giants supplied by Anna Ho, and instead use the entire LAMOST data release 2 (a survey of $\approx2.2$ million stars), we predict that we should have found 1.09 stars enhanced in the r-process.
 While again this should be considered a lower bound, it is still a startling difference from the 47 that we found in our sample.
@@
 
-	We recommend follow-up high resolution spectra be obtained for each of the 60 stars to ascertain how enhanced they are.
+	We recommend follow-up high resolution spectra be obtained for each of the 47 stars to ascertain how enhanced they are.
 To find the origin of these stars and to show whether or not they may come from a similar progenitor site it is necessary to find orbits for them.

### 2018-01-31 Neutron_merger.py
code for mergers/supernovae

@@ -1,0 +1,87 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Jan 24 14:38:17 2018
+
+@author: Matt
+"""
+
+import numpy as np 
+import os
+import matplotlib.pyplot as plt
+import math
+
+from astropy import units as u
+from astropy import constants as const
+import astropy as asp 
+
+
+
+MilkyWayVol = 4/3*math.pi*(15000*u.pc)**3 #radius of MW=15000 pc; Vol in pc^3
+N_MWstars = 250*10^(9) # Average number of stars in MW (+/- 150 billion error)
+N_MWgiants = 75300000
+LAMOSTstars = 454180
+
+Ejecta = 1.989*10**(30)*10**(-4.5)*u.kg #Typical Eu Neutron Star Ejecta in kg from Ji's Paper
+
+#Upper limit Merger rate from LIGO paper {Upper limits on the rates of binary neutron star 
+#and neutron-star--black-hole mergers from Advanced LIGO's 
+#first observing run}
+
+#Lower limit merger rate from 1991 paper; author: Phinney E.S. {The rate of neutron star binary mergers in the universe
+# - Minimal predictions for gravity wave detectors}
+
+Rate = (10**(-6))*(u.Mpc**(-3))/(u.yr) #Lower limit
+#Rate = 12600*(u.Gpc**(-3))/(u.yr) #Upper limit NS merger rate per parsec cubed per year
+
+Densityintime = Ejecta*Rate #kg*parsec^(-3)*yr^(-1)
+
+LAMOST_MW_Frac = float(LAMOSTstars)/N_MWgiants #percentage of Milky Way stars observed by Anna Ho
+
+ObsMW = LAMOST_MW_Frac*MilkyWayVol #The observed volume of the Milky Way in parsec^3
+
+AveStarMass = 1.989*10**(30)*0.8*u.kg#Average star mass in kg
+
+Eu_Fe = 0.7
+
+Hatom_mass = 1.6737236*10**(-27)*u.kg #kg
+
+H_mass = AveStarMass*0.75 #Hydrogen mass in the star (kg)
+
+N_Hatoms = H_mass/Hatom_mass
+
+Fe_H = 0.0134 # Using Solar metallicity as average
+
+Eu_H = Eu_Fe + Fe_H
+
+N_Euatoms = 10**(Eu_H - 12)*N_Hatoms
+
+Euatom_mass = 2.5234214*10**(-25)*u.kg
[…]

### 2018-01-31 supernovae.py

@@ -1,0 +1,82 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jan 30 15:19:51 2018
+
+@author: Matt
+"
+
+# -*- coding: utf-8 -*-
+
+"""
+
+import numpy as np 
+import os
+import matplotlib.pyplot as plt
+import math
+
+from astropy import units as u
+from astropy import constants as const
+import astropy as asp 
+
+
+
+MilkyWayVol = 4/3*math.pi*(15000*u.pc)**3 #radius of MW=15000 pc; Vol in pc^3
+N_MWstars = 250*10**(9) # Average number of stars in MW (+/- 150 billion error)
+N_MWgiants = 75300000
+LAMOSTstars = 454180
+
+Ejecta = 1.989*10**(30)*10**(-7.5)*u.kg #Typical Eu Supernovae Ejecta in kg from Ji's Paper
+
+#Rate given by 'Nearby supernova rates from LOSS - III'
+#Weidong Li, Ryan Chornock, Jesse Leaman
+
+Rate = 0.447*(10**(-4))*(u.Mpc**(-3))/(u.yr) #Type II supernovae volumetric rate 
+
+Densityintime = Ejecta*Rate #kg*parsec^(-3)*yr^(-1)
+
+LAMOST_MW_Frac = float(LAMOSTstars)/N_MWgiants #percentage of Milky Way stars observed by Anna Ho
+
+ObsMW = LAMOST_MW_Frac*MilkyWayVol #The observed volume of the Milky Way in parsec^3
+
+AveStarMass = 1.989*10**(30)*0.8*u.kg#Average star mass in kg
+
+Eu_Fe = 0.7
+
+Hatom_mass = 1.6737236*10**(-27)*u.kg #kg
+
+H_mass = AveStarMass*0.75 #Hydrogen mass in the star (kg)
+
+N_Hatoms = H_mass/Hatom_mass
+
+Fe_H = 0.0134 # Using Solar metallicity as average
+
+Eu_H = Eu_Fe + Fe_H
+
+N_Euatoms = 10**(Eu_H - 12)*N_Hatoms
+
+Euatom_mass = 2.5234214*10**(-25)*u.kg
+Eu_mass = Euatom_mass*N_Euatoms #Total mass of Eu in each enhanced star (assuming average of [Eu/Fe]=0.7)
+
+Eu60 = Eu_mass*60 #Total (average) mass of Eu in the 60 stars
+
[…]

### 2018-02-02 article/ms.tex
newest draft for Andy

--- 2018-01-22 article/ms.tex
@@
 
+\usepackage{numprint}
 \usepackage{booktabs}
@@
 
+\usepackage{amsbsy}
 \usepackage{graphicx}	% Including figure files
+\usepackage{color}
 \usepackage{amsmath}	% Advanced maths commands
 \usepackage{amssymb}	% Extra maths symbols
+
+\newcommand{\todo}[1]{\textcolor{red}{#1}}
 
@@
 % Keep the title short and informative.
-\title[Research is fun, max. 45 characters]{You can't spell Euphoric without Eu.}
+\title[Discovery of 47 r-process stars from the LAMOST survey]{Discovery of 47 $r$-process stars from the LAMOST survey}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[Matthew T. Miles et al.]{
-Matthew T. Miles,$^{1}$\thanks{E-mail: mtmil3@student.monash.edu}
-A. N. Other,$^{2}$
-Third Author$^{2,3}$
-and Fourth Author$^{3}$
+\author[Matthew T. Miles et al.]{Matthew T. Miles,$^{1}$\thanks{E-mail: mtmil3@student.monash.edu}
+	Andrew R. Casey,$^{1,2}$
+	Brodie J. Norfolk,$^{1}$
+	Alex J. Kemp,$^{1}$\newauthor
+	John C. Lattanzio,$^{1}$
+	Kevin C. Schlaufman,$^{3}$
+	Alexander P. Ji,$^{4}$
+	Anna Y. Q. Ho,$^{5}$
 	\\
 	% List of institutions
-$^{1}$School of Physics and Astronomy, Monash University, Clayton Campus, Victoria 3800\\
-$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
-$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
+	$^{1}$School of Physics and Astronomy, Monash University, Clayton Campus, Victoria 3800, Australia\\
+	$^{2}$Faculty of Information Technology, Monash University, Clayton Campus, Victoria 3800, Australia\\
+	$^{3}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA\\
+	$^{4}$Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA\\
+	$^{5}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, CA, 91125, USA
 }
@@
 	\begin{abstract}
-The creation of heavy elements occurs through the slow and rapid neutron capture process.
-The site of the slow neutron capture process is known and occurs commonly throughout the Milky Way, particularly in AGB stars.
-However the site of the rapid neutron capture process is still heavily debated.
-There are many sites that could potentially create the conditions needed to synthesise r-process elements, however there have arisen issues with frequency, abundance, and probability fed from observations of our celestial neighbours in the Milky Way, that prevent us from choosing any single site for this phenomena.
-Here we show the discovery of 22 r-process (Europium) enhanced stars, double the currently known amount in our galaxy.
-The discovery of these stars, and the lack of common features they possess, implies the action of multiple different r-process sites.
-This is opposed to all r-process material being produced in small amounts in common events such as core-collapse supernovae, or the material only being produced in very large amounts in very rare events, such as neutron star mergers.
+		The production of heavy elements occurs through the slow and rapid neutron capture process.
+Numerous sites satisfy the conditions needed to synthesise r-process elements, but the frequency and abundance of these sites is unclear.
+The lack of a large number of stars with strong r-process signatures limits us.
+Here we report the discovery of 47 r-process enhanced stars from the LAMOST survey, more than doubling the known number in our Galaxy.
+Additionally, we provide the first estimate, to our knowledge, of whether neutron star mergers are able to account for the r-process element abundances in all known r-process enhanced stars in the Milky Way.
+The discovery of these stars implies multiple r-process sites, contrary to previous conclusions in the literature including all r-process material being produced in small amounts in common events such as core-collapse supernovae, or the material only being produced in very large amounts in very rare events, such as neutron star mergers.
 	\end{abstract}
@@
 	\begin{keywords}
-keyword1 -- keyword2 -- keyword3
+		nucleosynthesis -- r-process -- neutron star mergers -- core-collapse supernovae
 	\end{keywords}
@@
 
-Heavy elements (those with an atomic number greater than 30) must be synthesized using the slow (s) and rapid (r) neutron capture processes (\cite{Sneden2008}).
-The creation and abundance of these elements has been a key area in astrophysics research, and has been discussed and debated ever since the idea was first introduced in 1957 (\cite{Burbidge1957}).
+	Heavy elements ($Z > 30$) are synthesised through the slow (s) and rapid (r) neutron capture processes \citep{Sneden2008}.
+The nucleosynthesis of these elements has been a key area in astrophysics research since it was first theorised  \citep{Burbidge1957}.
 
-Since it was first hypothesised 61 years ago, theorists have argued about the potential sites of the r-process.
-The r-process occurs under very specific circumstances, where the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the element undergoes a $\beta$-decay.
-The sites at which this phenomena can occur are very specific, with the most favoured being core-collapse supernovae which could enrich gas clouds that later could lead to enriched star formation.
-Or alternatively, where r-process elements are in a much higher abundance, Neutron Star Mergers or magnetorotationally driven supernovae, as is theorised to have happened in the case of the highly r-process enhanced ultra-faint dwarf (UFD) galaxy Reticulum II (\cite{Ji2016}).
-Neutron star mergers may have a stronger argument to be the parent sight of such a large amount of material being injected to a particular area, as is observed from Reticulum II.
-However, magnetorotationally driven supernovae are another possible solution.
-While they may not produce as much r-process material (although still more than core-collapse supernovae), they occur more frequently.
+	For over 60 years theorists have argued about the potential sites of the r-process.
+The r-process occurs when the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the isotope undergoes a $\beta$-decay.
+The sites where this phenomena can occur are very specific, with the most favoured being core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae.
+Core-collapse supernovae are relatively common throughout the Galaxy, but they only produce small amounts of r-process material.
+Neutron star mergers or magnetorotationally driven supernovae, however, occur much more infrequently than core-collapse supernovae, but produce far more r-process material.
+Events such as these are theorised to account for the case of the highly r-process enhanced ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}.
+Neutron star mergers may have a stronger argument to be the parent site of this level of r-process enhancement in such a small volume.
+However, magnetorotationally driven supernovae are also a possible solution.
 
-In the particular case of Europium (atomic number 63), almost all is produced through the r-process [citation needed].
-The recent discovery of the UFD Reticulum II has sparked discussion about the origin of r-process elements.
-Historically UFD's have had some of the lowest abundance of r-process elements of any celestial body, however analysis of several of Reticulum II's stars show they are greatly enriched, to the factor of 2-3 orders of magnitude higher than stars found in any other UFD (\cite{Ji2016}).
-This measure of enrichment lends evidence to the theory that a single rare event must have occurred in the galaxies formative years to enrich it, as (for Europium especially) the heavy element yields are found to be 1000 times higher than would be achieved from core-collapse supernovae ejecta.
-As the idea that 1000 supernovae could have contributed to Reticulum II is extremely improbable, then the fact that Reticulum II is so heavily enriched is evidence that at least some r-process material must be produced by a rare astrophysical event such as a neutron star-neutron star merger, or a magnetorotationally driven supernovae.
+	While magnetorotationally driven supernovae may not produce as much r-process material as neutron star mergers (although still more than core-collapse supernovae), they occur more frequently, and enough material is produced that it is currently impossible to distinguish between them through abundance signatures.
 
-While neutron star mergers or magnetorotationally driven supernovae are likely to be the progenitors of much r-process material, that is not to say that all r-process material stems from these sources.
-Rather ithe rarity of these events might serve as an indication of the rarity of stars found to be heavily enhanced in these elements.
+	Europium (Z=63), is entirely produced through the r-process.
+This makes it a very useful signature when detecting stars that show evidence of pollution by r-process material.
+The recent discovery of the UFD Reticulum II used Europium as evidence of its r-process enhancement, and found the particularly interesting result that the UFD's level of r-process enrichment was too high to have occurred through a core-collapse supernovae event.
+
+	Historically UFD's have had some of the lowest abundance of r-process elements of any celestial body.
+However analysis of several of Reticulum II's stars show they are greatly enriched, 2-3 orders of magnitude higher than stars found in any other UFD galaxy \citep{Ji2016}.
+This degree of enrichment supports the theory that a single rare event must have occurred in the galaxies formative years to enrich it, as (for Europium especially) the heavy element yields are found to be 1000 times higher than are achieved from core-collapse supernovae ejecta.
+As the idea that 1000 supernovae could have contributed to Reticulum II is extremely improbable, then the fact that Reticulum II is so heavily enriched is evidence that at least some r-process material must be produced by a rare astrophysical event such as a neutron star-neutron star merger.
+
+	While neutron star mergers or magnetorotationally driven supernovae are likely to produce significant amounts of r-process material, that is not to say that all r-process material stems from these sources.
+Rather, the rarity of these events might serve as an indication of the rarity of stars found to be heavily enhanced in these elements.
 What we then have to ask is can these rare events be responsible for all r-process stars found in the Milky Way, regardless of the relative strength of their abundance?
-And if not, can we then conclude that there must be multiple sites of r-process element creation throughout the Milky Way, that create these elements to different extents?
+Or perhaps, assuming very little mixing, could core-collapse supernovae create enough material to pollute the stars we've found?
+And if neither of these prove to be the case, can we then conclude that there must be multiple sites of r-process element creation throughout the Milky Way, that create these elements to different extents?
 
 	To answer this question it is necessary to find and catalogue more r-process stars to find some relative fraction of enhanced stars that are either very enhanced, and so must come from a rare event.
-Or only slightly enhanced, and so they may come from a more common event that produces less material.
-However, r-process stars are unfortunately very rare, which makes finding this fraction difficult.
-For this reason we look to massive data sets, such as the LAMOST sky survey.
-\\\\
-The second data release from the LAMOST telescope catalogued $\approx$ 2.2 million spectra (low resolution) of stars in the Northern sky.
-Of these 2.2 million, 454,180 giants were fit against a normalised spectra from a sample of 9952 giants by Anna Ho (\cite{AnnaHo2017}), and from this it became possible to analyse which giants showed an abundance or depletion of particular heavy elements.
+Or only slightly enhanced, and so must come from a more common event that produces less material.
+However, r-process stars are very rare, which makes finding this fraction difficult.
+For this reason we must look to massive data sets, such as the LAMOST sky survey.
 
-In this letter we report the probable discovery of 22 of these LAMOST giants that show enhanced r-process peaks for Europium at both 4129 and 4205 Angstroms.
-The giants belong to a broad range of both metallicity and temperature, and don't cluster or trend towards any particular place in the observed sky.
-These characteristics and seeming lack-of a trend could argue that there must be multiple sights of the r-process.
-While rare events such as neutron star mergers may create r-process elements in a very high abundance in localised areas, it is improbable to assume that these rare events occur commonly enough across the observed sky to explain what we see here.
-We suggest instead that there exists another r-process site that is acting alongside neutron star mergers that is far more common, but produces far less r-process material, such as core-collapse supernovae.
+	In this letter we report the probable discovery of 47 of these LAMOST giants that show enhanced r-process peaks for Europium at both 4129 and 4205 Angstroms.
+	In Section 2 we outline the methods used to attain our results and the analysis done. In Section 3 we discuss what our results imply about the r-process. We conclude in section 4.
 
@@
 		\caption{The spectral region around two Europium absorption lines at 4129 and 4205 Angstroms.
-This particular stars spectra (black) shows clear absorption at these wavelengths, as compared to the normalised spectra of a similar star (red).}
+This particular star's spectra (black) shows clear absorption at these wavelengths, as compared to the data-driven model (red).}
 		\label{fig:starindex_423451}
@@
 
-\section{Methods, Observations, Simulations etc.}
-Normally the next section describes the techniques the authors used.
-It is frequently split into subsections, such as Section~\ref{sec:maths} below.
+	\begin{figure}
+		\includegraphics[width=\columnwidth]{metalhistpython}
+		\caption{The metallicities of the 47 candidate stars.}
+		\label{fig:starindex_423451}
+	\end{figure}
 
-\subsection{Observations and Target Selection}
-The LAMOST survey is a low resolution ($R\approx1800$) optical survey that took spectra of stars between (3650-9000 \AA).
-The LAMOST Data-Release 2 (DR2) collected spectra in this band for $\approx$ 2.2 million stars.
-Anna Ho describes in her 2017 paper (\cite{AnnaHo2017}) how she used a machine learning method named \textit{The Cannon}.
-\textit{The Cannon} fit a predictive model using 9952 LAMOST stars that were also found in the higher resolution ($R\approx22500$) APOGEE survey.
-From this Ho was able to fit normalised spectra to 454180 giants from the LAMOST survey and was restricted to between 3905 and 9000 \AA.
+	\section{Methods}
 
-We located potential candidate stars with an abundance of Europium by searching for deviations from the normalized spectra supplied by \textit{The Cannon}.
-A negative deviation implied an enhancement in a particular element while a positive deviation implied a depletion (compared to what the model expected).
+	\subsection{Observations and Candidate Selection}
 
-At the two main absorption lines for Europium (4129 and 4205 \AA) we fitted Gaussian profiles to each star in the 454180 giants from LAMOST DR2, and we recorded the amplitude and the wavelength of each, as well as their corresponding errors.
-The relevant stars were then found by meeting a specific set of criteria:
+	The LAMOST survey is a low resolution ($R\approx1800$) optical survey that took spectra of stars between 3650-9000 \AA.
+The second data release from the LAMOST telescope catalogued $\approx$ 2.2 million spectra (low resolution) of stars in the northern sky.
+Of these 2.2 million, 454,180 giants were fit against a normalised spectra from a sample of 9952 giants \citep{AnnaHo2017}, and from this it became possible to analyse which giants showed an abundance or depletion of particular heavy elements.
+A machine learning code \textit{The Cannon} was used to fit a predictive model using 9952 LAMOST giant stars that were also found in the higher resolution ($R\approx22500$) APOGEE survey.
+The labels \textit{The Cannon} predicted were $T_{\rm{eff}}$, $\rm{log_{10}[g]}$, $\rm{[Fe/H]}$, and $\rm{[\alpha/Fe]}$.
+Normalised spectra was then fit to 454,180 giants from the LAMOST survey and was restricted to between 3905\,\AA\ and 9000\,\AA.
+For reference, typical uncertainties for these labels are $70\rm{K}$ for $T_{\rm{eff}}$, $0.1$ in $\rm{log_{10}[g]}$, 0.1 in $\rm{[Fe/H]}$, and 0.04 in $\rm{[\alpha/H]}$.
+
+	We selected potential candidate stars with an over-abundance of Europium by searching for deviations from the normalized spectra supplied by \textit{The Cannon}.
+A negative deviation implies an enhancement in a particular element while a positive deviation implies a depletion (compared to what the data-driven model predicted).
+
+	At the two main absorption lines for Europium (4129\,\AA\ and 4205\,\AA) \todo{citation needed} we fitted Gaussian profiles to each star in the 454,180 giants from LAMOST DR2, and we recorded the amplitude and the wavelength of each, as well as their corresponding errors.
+Candidate Europium enhanced stars were selected by identifying stars that met the following criteria:
 
 	\begin{itemize}
-	\item The amplitude of their deviation from the model needed to be less than -0.05 (remembering that a negative deviation corresponds to an enhancement in the element);
-	\item The Signal to Noise (S/N) must have been greater than 30;
-	\item The deviation from the required wavelength in question must have been less than 2 \AA;
-	\item The $\chi^{2}$ value (where the $\chi^{2}$ value represents how well the rest of the model fit the spectrum, aside from the enhancement points) must have been less 3, and;
-	\item All of these conditions must have been met for both 4129 and 4205 \AA for us to consider them sufficiently Eu enhanced.
+		\item The amplitude of their deviation from the model needed to be less than $\rm{A}<-0.05$;
+		\item The signal to noise (S/N) must be greater than 30;
+		\item The deviation from the required wavelength in question must be less than 2 \AA;
+		\item The reduced $\chi_{\rm{r}}^{2}$ value (where the $\chi_{\rm{r}}^{2}$ value represents how well the model fit the spectrum) must be less than 3, $\chi_{\rm{r}}^{2}<3$.
+		\item All of these conditions must be met for both 4129 \AA\ and 4205 \AA\ for us to consider them sufficiently Eu enhanced.
 	\end{itemize}
 
-This left us with an initial sample of 48 candidates out of the 454180 LAMOST giant sample.
-They were then visually scrutinised to find any that were clear outliers and did not belong in the sample.
-After this process we were left with 22 potentially r-process enhanced candidates.
+	We gathered an initial sample of 62 candidates out of the 454180 LAMOST giant sample.
+These were then visually scrutinised to identify those that lacked visual evidence that they were enhanced.
+After this process we were left with 47 potentially r-process enhanced candidates, 22 of which stand out as very strong candidates.
 
-\begin{figure}
-	\includegraphics[width=\columnwidth]{RA_v_dec_radial_velocity}
-	\caption{The right ascension and declination for the enhanced stars, coloured by radial velocity. No clear trend or significant grouping is present.}
-	\label{fig:radec_Eucands}
-\end{figure}
+	\section{The r-process}
+	For the r-process to occur there must be a very high neutron density, such that neutron capture must be able to occur before the nucleus undergoes a $\beta$-decay (assuming the nucleus is in an unstable state).
+The conditions that can create this are rare.
+Events such as supernovae or neutron star mergers list among the most favoured sites.
 
-\section{Discussion points}
-\begin{itemize}
-	\item \textbf{consider CCSN}
-	\item \textbf{consider NS-NS}
-	\item \textbf{consider the things about our stars that mean it can't be just one of these. i.e differing Rad vels, much different positions, speed travelling vs age of galaxy vs frequency of NS-NS} 
-	\item \textbf{consider abundances, lower abundances don't fit NS-NS model, high abundances don't fit CCSN model.}
-	\item \textbf{consider then, that the solution is both.}
-	\item \textbf{there has to be some kind of statistical argument we can make on this one I reckon, find it.}
-\end{itemize}
+	\subsection{Selection effects}
+	The LAMOST giants we analyse belong to a broad range of metallicity ($\rm{[Fe/H]} -1.6\ \rm{to}\ 0.6$), and don't cluster towards any position in the observed sky.
+These characteristics argue that the abundance we see could not have originated from a common era or site.
+
+	The previous sample of r-process stars, before the release of this letter, almost exclusively consists of metal-poor stars.
+This fact is not to be confused with saying that most r-process stars found should be metal-poor stars, rather that at low metallicities we know that the s-process will not contribute, so neutron capture elements formed from these stars would be only from the r-process.
+Over half the current known r-process stars come from a very metal poor ultra faint dwarf galaxy, Reticulum II.
+However, Europium we know to be totally made from the r-process, therefore even at metallicities where the s-process contributes, Europium is a valuable indication of r-process synthesis.
+
+	\subsection{Multiple r-process sites?}
+	While it is possible that all currently known r-process enhancements can be made by neutron star mergers, we still have cases of stars in the galaxy which show particularly weak enrichment from r-process elements ([Eu/Fe] < 0.7).
+These enhancements imply that another site of r-process element synthesis is likely to be active.
+As we show in \ref{rates}  neutron star merger rates may show that all heavily enriched stars can be enhanced by these phenomena within an adequate time-scale, but we are not able to assume that as a consequence of the merger some stars are greatly enhanced, while others are only very slightly enhanced.
+It is more accurate to propose that at least two sites exist, with one (potentially mergers) producing a massive amount of enhanced material, and another only producing a small amount, such as supernovae.
+
+	\subsection{Core-collapse supernovae (CCSN)}
+	Core-collapse supernova is one of the sites initially proposed to have a high enough neutron density to create elements synthesised by the r-process \citep{Burbidge1957}.
+
+	As of yet our knowledge is incomplete on the exact mechanism that allows material with a high enough neutron density to escape the supernovae event.
+	One possible mechanism is the action of high-entropy neutrino winds being released from a proto-neutron star during core-collapse.
+In this stage of the collapse, this neutrino wind is driving mass loss and could be instrumental in the expulsion of the r-process material in supernovae conditions.
+However, how much enhanced material is released from the event is very dependant on the amount of material that is allowed to fall back onto the remnant at the arrival of the reverse shock, and so often the supernovae may not release a considerable amount of material \citep{Woosley1992, Burrows1995}.
+
+	Core-collapse supernovae seem to release $M_{\rm{Eu}}\approx10^{-7.5} M_{\odot}$ per event \citep{Argast2004} .
+While this may not be a particularly significant amount, core-collapse supernovae occur frequently $44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$ \citep{Li2011}, and so it isn't unreasonable to suggest that, with very little mixing occurring, that much if not all r-process material could have been formed by these and recycled in the stars we present in this letter.
+
+	\subsection{Neutron star mergers}
+	\label{NSmerg}
+	Neutron star mergers are another possible site of r-process element nucleosynthesis \citep{Kasen2017,Hotok2013,Drout2017}.
+They are easily able to meet the conditions for a high neutron density as interacting tidal forces between the stars rip away neutron dense material allowing r-process element synthesis to occur easily.
+In this interaction they produce considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}, however the direct interaction and merger of a binary neutron star pair occurs very infrequently with only one ever having been directly observed, and with an upper frequency estimate of $1000\ \rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016}.
+The massive amount of material that these mergers release could more than make up for the low frequency and so, similar to core-collapse supernovae, it is not unreasonable to suggest that they are responsible for most if not all known r-process material.
+
+	The recent discovery of the UFD Reticulum II \citep{Ji2016} is evidence against the case for a single r-process site.
+Of nine stars observed in Reticulum II, 7 of them were shown to be highly enriched in r-process elements ($\rm{[Eu/Fe]\approx1.7}$) which suggests a single prolific event having occurred in close proximity to the galaxy early in it's formation, such as a neutron star merger.
+However, two of the stars observed were only weakly enhanced in r-process elements which suggests that there must have been a second, less efficient, form of r-process enhancement present.
+
+	\subsection{The rates of r-process events and what they imply}
+	\label{rates}
+	From the recent advanced LIGO data \citep{LIGO2016}, we are able to find an estimate for a plausible frequency at which neutron star mergers occur, as mentioned in section \ref{NSmerg}.
+As well as a reliable estimate of core-collapse supernovae rates from \citet{Li2011}.
+
+	From these two rates we can, for the first time to our knowledge, estimate the amount of r-process stars that should be present in the Milky Way, enhanced both by purely neutron star mergers and core-collapse supernovae.
+We do this assuming instant recycling, and that no r-process matter pollutes stars by any other means than these.
+
+	From these rates we can find an estimate of how many r-process enhanced giants should be present from an estimate number of the Milky Way's total stars.
+As well as an estimate of how many stars, giants or otherwise, should be present in the Milky Way.
+
+	In preparing these calculations we assumed a constant star formation rate, 2 M$_\odot yr^{-1}$, in the disk of the Milky Way, $\rm{r=15kpc}$, with a typical IMF and giant star birth rate of approximately $0.3\ $stars per year.
+We also assumed the lifetime between $\log{g} = 3.2$ and the end of the core-helium burning phase is about $250\,{\rm Myr}$.
+Therefore if we assume a steady-state system, the number of giant stars in the Milky Way comes to approximately $7.53\times10^7$.
+This allowed us to find the percentage of the Milky Ways stars that our sample represents.
+
+	We also state that a star is said to be enhanced if [Eu/Fe] $\geq$ 0.7, and performed the lower-bound estimate that all of our 47 stars exhibited this abundance.
+The amount of r-process material expelled is the same as previously discussed, using Europium as our identifier, of $M_{Eu}\approx10^{-4.5} M_{\odot}$.
+
+    It was found that in the Milky Way alone there should be present 9,896 r-process enhanced stars.
+Considering this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the now updated known amount of r-process enhanced stars which comes to 60.
+
+    Scaling down from the amount of stars in the Milky Way to our sample size of $\approx450000$ giants, the amount of r-process enhanced stars we should find comes to less than one (0.0178).
+If we are to extend our sample from the 450000 giants, and instead use the entire LAMOST data release 2 (a survey of $\approx2.2$ million stars), we predict that we should still have found less than a single star (0.087)  enhanced in r-process elements.
+While again this should be considered a lower bound, it is still a startling difference from the 47 that were found.
+
+    We can do a similar calculation with our rate of core-collapse supernovae.
+Taking the same assumptions with minimal mixing, as well as both the ejecta ($M_{Eu}\approx10^{-4.5} M_{\odot}$) and rate ($44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$) previously discussed, we find that in the Milky Way there should be present 442 r-process enhanced stars made from core-collapse supernovae.
+
+    Were we to scale this down to our sample size of $\approx450000$ giants we arrive at a figure of $8.0\times10^{-4}$ stars that should have been observed.
+Scaling again to the full LAMOST sample we would then expect to find $3.9\times10^{-3}$ enhanced stars.
+
+    From these estimates we can find an approximation for whether or not either neutron star mergers or core-collapse supernovae by themselves are sufficient to enrich our entire r-process enhanced catalogue.
+
+    We find that, by using the assumptions listed, neutron star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for all 60 known r-process enhanced stars within $13.87\times10^9$ years, very close to the age of the universe.
+From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $3.1\times10^{11}$ years, not within the age of the universe.
+This means with our current knowledge of core-collapse supernovae frequency and the amount of r-process material they eject, there is no way that only core-collapse supernovae could enrich the entire Milky Way.
+
+    This is reinforced by the enhanced stars found in the LAMOST sample.
+47 is greater than 10\% of all enhanced stars that should be present in the Milky Way according to the solely core-collapse supernovae rate.
+However, the LAMOST data release 2 only surveyed 0.00088\% of the Milky Way.
+The idea that over 10\% of all r-process stars were found in this small a percentage is improbable, and so we can say that core-collapse supernovae can not be the only source of r-process material.
+
+    \todo{For Andy (haven't written this bit nicely this was a thought dump): Let us consider that both of these estimates are correct, and the rates they are based on have been roughly accurate over the age of the universe (although they should have increased with time, which is actually a bit worse for us).
+Then we are left with our previous prediction of 9,896 stars enhanced purely by neutron star mergers, and another 442 stars enhanced purely by core-collapse supernovae.
+This leaves us with a new sample of r-process enhanced stars that should exist in the Milky Way of 10,338.
+    At a rough estimate, the LAMOST data release 2 took spectra for 0.00088\% of the Milky Way's stars (assuming an average amount of stars in the Milky Way of 250 billion).
+In this very small percentage, 47 r-process enhanced stars were found.
+Then, if we are able to assume that there is nothing particularly special about the area of the sky that LAMOST surveyed, scaling this size to that of the Milky Way we should find 5,340,892 r-process enhanced stars.
+Clearly there is something wrong.}
 
 	\section{Conclusions}
+	We present the largest to date sample of r-process element enhanced stars.
+These stars are found at a wide range of metallicities, contrary to previous discoveries that focussed on metal-poor r-process enhanced stars.
+Similarly they are not clumped in either temperatures, $log(g)$, or radial velocity.
+They don't cluster to any one end of the H-R diagram, so it is likely there is no correlation between type of star.
+They are found both in the disk and halo, and are not clustered anywhere in the sky.
+In addition to this we also present the first ever estimate to our knowledge, from information provided by advanced LIGO, that neutron star mergers possess the ability to synthesise all currently known r-process material in a feasible time-scale.
+We also provide evidence that we are confident to say means that core-collapse supernovae can not possibly be the only progenitors of r-process material in the Milky Way Galaxy.
 
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
-
-\section*{Acknowledgements}
-
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
+	We recommend follow-up high resolution spectra be obtained for each of the 47 stars to ascertain how enhanced they are.
+To find the origin of these stars and to show whether or not they may come from a similar progenitor site it is necessary to find orbits for them.
 
@@
 	\bibliographystyle{mnras}
-\bibliography{paper} % if your bibtex file is called example.bib
+	%\bibliography{paper} % if your bibtex file is called example.bib
 	\begin{thebibliography}{99}
-	\bibitem[\protect\citeauthoryear{Sneden, Christopher; Cowan, John J; Gallino, Roberto}{2008}]{Sneden2008}
+		\bibitem[\protect\citeauthoryear{Sneden, C. et al.}{2008}]{Sneden2008}
 		Sneden C., Cowan J.J., \& Gallino R. 2013, Annual review of Astronomy \& Astrophysics, 46, 1
-	\bibitem[\protect\citeauthoryear{Ji, Alexander P.; Frebel, Anna; Chiti, Anirudh; Simon, Joshua D.}{2016}]{Ji2016}
+		\bibitem[\protect\citeauthoryear{Ji, A. P. et al.}{2016}]{Ji2016}
 		Ji A. P., Frebel A., Chiti A., \& Simon J. D. 2016, Nature, 531
@@
 		Ho A. Y. Q., Ness M. K., Hogg David W., Rix H-W., Liu C., Yang F., Zhang Y., Hou Y.,\& Wang Y. 2017, ApJ, 836, 1
-	\bibitem[\protect\citeauthoryear{Burbidge, E. Margaret; Burbidge, G.R.; Fowler, William A.; Hoyle, F}{1957}]{Burbidge1957}
+		\bibitem[\protect\citeauthoryear{Burbidge, E. et al.}{1957}]{Burbidge1957}
 		Burbidge E. M., Burbidge G. R., Fowler W. A., \& Hoyle F. 1957, Review of Modern Physics, 29, 4
+		\bibitem[\protect\citeauthoryear{Goriely, S. et al.}{2011}]{Goriely2011}
+		Goriely S., Bauswein A. \& Janka H-T. 2011, , 738, L32
+		\bibitem[\protect\citeauthoryear{Abbott, B.P. et al.}{2016}]{LIGO2016}
+		Abbot B.P. et al. 2016, Living Reviews in Relativity, 19, 1
+		\bibitem[\protect\citeauthoryear{Argast, D. et al.}{2004}]{Argast2004}
+		Argast D., Samland M., Thielmann F-K. \& Qian Y-Z. 2004, Astronomy and Astrophysics, 416
+		\bibitem[\protect\citeauthoryear{Woosley, S.E. et al.}{1992}]{Woosley1992}
+		Woosley S.E, \& Hoffman R.D. 1992, ApJ, 395, 1
+		\bibitem[\protect\citeauthoryear{Burrows, A. et al.}{1995}]{Burrows1995}
+		Burrows, A., Hayes, J., \& Fryxell, Bruce A. 1992, ApJ, 450, 830
+		\bibitem[\protect\citeauthoryear{Li, W. et al.}{2011}]{Li2011}
+		Li, W., Chornock, R., Leaman, J., Filippenko, A. V., Poznanski, D., Wang, X., Ganshalingam, M., \& Mannucci, F. 2011, Royal Astronomical Society, 412, 1473
+		\bibitem[\protect\citeauthoryear{Drout, M. R. et al.}{2017}]{Drout2017}
+		Drout, M. R. et al. 2017, Science
+		\bibitem[\protect\citeauthoryear{Kasen, D. et al.}{2017}]{Kasen2017}
+		Kasen, D., Metzger, B., Barnes, J., Quataert, E., \& Ramirez-Ruiz, E. 2017, Nature, 551, 7678
+		\bibitem[\protect\citeauthoryear{Hotokezaka, K. et al.}{2013}]{Hotok2013}
+		Hotokezaka, K., Kiuchi, K., Kyutoku, K., Okawa, H., Skiguchi, Y., Shibata, M., \& Taniguchi, K. 2013, APS
 	\end{thebibliography}
 
-\appendix
-\newpage
-
-\section{Some extra material}
-
-If you want to present additional material which would interrupt the flow of the main paper,
-it can be placed in an Appendix which appears after the list of references.
-
-\begin{table}
+	% Please add the following required packages to your document preamble:
+	% \usepackage{booktabs}
+	% Please add the following required packages to your document preamble:
+	% \usepackage{booktabs}
+	\begin{table*}
 		\centering
-	\resizebox{\textwidth}{!}{%
-		\begin{tabular}{@{}llllllllllllll@{}}
+		\label{Data for the 47}
+		\begin{tabular}{@{}cccccccccccc@{}}
 			\toprule
-			\textbf{2MASS ID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{\begin{tabular}[c]{@{}l@{}}Vr\\ (km/s)\end{tabular}} & \textbf{Teff} & \textbf{Logg} & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\chi^{2}$} & \textbf{\begin{tabular}[c]{@{}l@{}}{[}Eu/Fe{]}\\ at 4129\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}{[}Eu/Fe{]}\\ at 4129 error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}{[}Eu/Fe{]}\\ at 4205\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}{[}Eu/Fe{]}\\ at 4205 error\end{tabular}} \\ \midrule
-			J063400.95+420904.3 & 34:01.0 & +42:09:04.4 & 34.09 & 9.89 & 4315.56 & 1.62 & -0.50 & 0.10 & 0.43 & 1.02 & 3.09 & 1.35 & 0.22 \\ \midrule
-			J220118.66+033558.6 & 01:18.7 & +03:35:58.6 & 35.11 & -108.23 & 4790.06 & 2.51 & -1.36 & 0.33 & 0.37 & 1.51 & 0.03 & 1.38 & 0.16 \\ \midrule
-			J060021.29+384840.6 & 00:21.3 & +38:48:40.6 & 30.03 & 32.68 & 4305.08 & 2.10 & 0.15 & -0.01 & 0.54 & 1.48 & 0.29 & 1.51 & 0.04 \\ \midrule
-			J025225.88+324308.1 & 52:25.9 & +32:43:08.2 & 34.79 & 24.88 & 4797.58 & 2.52 & -0.23 & 0.05 & 0.24 & 1.32 & 0.16 & 1.31 & 0.14 \\ \midrule
-			J163116.81+002349.5 & 31:16.8 & +00:23:49.5 & 32.63 & -35.98 & 4628.92 & 2.53 & 0.01 & 0.18 & 0.29 & 1.37 & 0.25 & 1.51 & 0.03 \\ \midrule
-			J153333.12+510621.8 & 33:33.1 & +51:06:21.9 & 49.45 & -17.99 & 4861.78 & 2.51 & -0.49 & 0.22 & 0.46 & 1.33 & 0.16 & 1.29 & 0.12 \\ \midrule
-			J075116.55+220137.8 & 51:16.6 & +22:01:37.9 & 32.87 & 90.24 & 4810.60 & 2.70 & -0.33 & 0.02 & 0.30 & 1.38 & 0.18 & 1.32 & 0.15 \\ \midrule
-			J003929.43+430039.5 & 39:29.4 & +43:00:39.6 & 33.14 & -104.33 & 4190.26 & 1.87 & -0.01 & 0.07 & 0.41 & 1.37 & 0.19 & 1.33 & 0.19 \\ \midrule
-			J071206.83+213038.0 & 12:06.8 & +21:30:38.1 & 32.66 & 29.08 & 4432.03 & 1.75 & -0.38 & 0.11 & 0.40 & 1.51 & 0.03 & 1.43 & 0.19 \\ \midrule
-			J222820.22+340750.3 & 28:20.2 & +34:07:50.3 & 34.52 & -45.27 & 4419.96 & 2.06 & -0.07 & 0.11 & 0.49 & 1.36 & 0.17 & 1.38 & 0.17 \\ \midrule
-			J222310.49+344357.4 & 23:10.5 & +34:43:57.5 & 54.06 & -20.09 & 4232.66 & 1.87 & -0.01 & 0.03 & 0.86 & 1.27 & 0.09 & 1.18 & 0.21 \\ \midrule
-			J222101.61+365923.6 & 21:01.6 & +36:59:23.7 & 30.81 & -27.88 & 4360.28 & 2.23 & 0.20 & 0.04 & 0.45 & 1.51 & 0.03 & 1.42 & 0.21 \\ \midrule
-			J074102.63+130520.3 & 41:02.6 & +13:05:20.4 & 40.83 & 49.17 & 5000.84 & 3.00 & -0.38 & -0.02 & 0.30 & 1.27 & 0.15 & 1.42 & 0.12 \\ \midrule
-			J061559.10+470344.9 & 15:59.1 & +47:03:44.9 & 36.84 & -18.29 & 4811.98 & 2.82 & -0.59 & 0.07 & 0.44 & 0.63 & 1.30 & 1.37 & 0.13 \\ \midrule
-			J054704.12+600827.1 & 47:04.1 & +60:08:27.1 & 33.19 & -23.33 & 4770.80 & 2.64 & -0.10 & 0.06 & 0.40 & 1.51 & 0.03 & 1.40 & 0.16 \\ \midrule
-			J042723.73+271546.8 & 27:23.7 & +27:15:46.9 & 45.73 & -40.17 & 4211.91 & 1.72 & -0.04 & 0.05 & 0.79 & 1.36 & 0.20 & 1.30 & 0.18 \\ \midrule
-			J035702.05+281335.2 & 57:02.1 & +28:13:35.3 & 31.82 & -44.67 & 4712.89 & 2.44 & 0.01 & 0.16 & 0.46 & 1.35 & 0.14 & 1.22 & 0.29 \\ \midrule
-			J091256.32+353008.3 & 12:56.3 & +35:30:08.3 & 73.39 & 20.39 & 4441.95 & 2.33 & 0.41 & 0.02 & 0.76 & 0.61 & 0.30 & 1.24 & 0.14 \\ \midrule
-			J071534.00+211353.8 & 15:34.0 & +21:13:53.9 & 31.68 & 42.27 & 4892.00 & 2.57 & -0.72 & 0.11 & 0.34 & -0.20 & 0.00 & 1.38 & 0.21 \\ \midrule
-			J101317.14+122928.8 & 13:17.1 & +12:29:28.8 & 45.54 & 300.69 & 5055.95 & 2.24 & -1.34 & 0.33 & 0.38 & 1.51 & 0.03 & 1.41 & 0.14 \\ \midrule
-			J161326.00+073218.1 & 13:26.0 & +07:32:18.2 & 48.45 & -50.07 & 5086.79 & 3.40 & -0.68 & 0.29 & 0.93 & 1.44 & 0.11 & 1.32 & 0.08 \\ \midrule
-			J173711.85+101126.6 & 37:11.9 & +10:11:26.7 & 30.01 & -33.58 & 4991.07 & 3.49 & -0.05 & 0.17 & 0.41 & 1.40 & 0.15 & 1.50 & 0.13 \\ \bottomrule
-		\end{tabular}%
-	}
-	\caption{My caption}
-	\label{my-label}
-\end{table}
+			\textbf{2MASS ID}   & \textbf{RA} & \textbf{DEC} & \textbf{S/N}        	& \textbf{$\boldsymbol{V_{\rm{r}}}$}   & \textbf{$\boldsymbol{T_{\rm{eff}}}$} & \textbf{Log(g)}	& \textbf{$\boldsymbol{[\rm{Fe/H}]}$} & \textbf{$\boldsymbol{[\alpha/\rm{H}]}$} & \textbf{$\boldsymbol{\chi_{\rm{r}}^{2}}$} & \textbf{{[}Eu/Fe{]}} & \textbf{Error} \\
+			-               	& {[}deg{]}   & {[}deg{]}	& {[}$\rm{pixel}^{-1}${]} & {[}$\rm{km\ s}^{-1}${]} & {[}K{]}             	& {[}$cm\ s^{-2}${]} & {[}dex{]}          	& {[}dex{]}              	& -                        	& {[}dex{]}        	& {[}dex{]}  	\\ \midrule
+			J130303.65+260837.0 & 13:03:03.65 & +26:08:37.0  & 36.48               	& -37.77              	& 4851.24             	& 2.98           	& -0.54              	& 0.19                   	& 0.42                     	& 1.39             	& 0.31       	\\
+			J062733.76+280814.1 & 06:27:33.77 & +28:08:14.2  & 39.08               	& 38.67               	& 4502.58             	& 1.92           	& -0.15              	& 0.00                   	& 0.35                     	& 1.43             	& 0.35       	\\
+			J070035.19+103443.5 & 07:00:35.19 & +10:34:43.5  & 41.77               	& 17.69               	& 4752.08             	& 2.44           	& -0.43              	& 0.06                   	& 0.33                     	& 1.09             	& 0.63       	\\
+			J070107.18+125948.2 & 07:01:07.19 & +12:59:48.2  & 33.72               	& 46.17               	& 4452.61             	& 2.51           	& 0.47               	& 0.02                   	& 0.36                     	& 1.30             	& 0.31       	\\
+			J063400.95+420904.3 & 06:34:00.96 & +42:09:04.4  & 34.09               	& 9.89                	& 4315.56             	& 1.62           	& -0.50              	& 0.10                   	& 0.43                     	& 1.19             	& 3.10       	\\
+			J220118.66+033558.6 & 22:01:18.66 & +03:35:58.6  & 35.11               	& -108.23             	& 4790.06             	& 2.51           	& -1.36              	& 0.33                   	& 0.37                     	& 1.44             	& 0.26       	\\
+			J221220.27+032735.4 & 22:12:20.27 & +03:27:35.5  & 35.16               	& -12.89              	& 4867.34             	& 3.12           	& 0.11               	& 0.14                   	& 0.35                     	& 1.52             	& 0.20       	\\
+			J060021.29+384840.6 & 06:00:21.29 & +38:48:40.6  & 30.03               	& 32.68               	& 4305.08             	& 2.10           	& 0.15               	& -0.01                  	& 0.54                     	& 1.49             	& 0.35       	\\
+			J081632.10-053703.4 & 08:16:32.11 & -05:37:03.4  & 59.16               	& 44.67               	& 4541.14             	& 2.45           	& 0.57               	& 0.03                   	& 0.75                     	& 1.34             	& 0.26       	\\
+			J064641.14+235318.2 & 06:46:41.14 & +23:53:18.3  & 36.77               	& 25.78               	& 4325.56             	& 1.78           	& -0.10              	& 0.02                   	& 0.42                     	& 1.41             	& 0.27       	\\
+			J025225.88+324308.1 & 02:52:25.88 & +32:43:08.2  & 34.79               	& 24.88               	& 4797.58             	& 2.52           	& -0.23              	& 0.05                   	& 0.24                     	& 1.31             	& 0.29       	\\
+			J061822.02+015126.7 & 06:18:22.02 & +01:51:26.8  & 36.75               	& 45.27               	& 4617.95             	& 2.43           	& -0.12              	& 0.04                   	& 0.34                     	& 1.42             	& 0.30       	\\
+			J083049.21+304144.3 & 08:30:49.21 & +30:41:44.3  & 39.5                	& -125.31             	& 4859.92             	& 2.28           	& -1.63              	& 0.33                   	& 0.41                     	& 1.52             	& 0.20       	\\
+			J035949.12+302104.4 & 03:59:49.13 & +30:21:04.4  & 30.42               	& 26.98               	& 4164.41             	& 1.79           	& -0.12              	& 0.00                   	& 0.36                     	& 1.47             	& 0.32       	\\
+			J074852.24+075016.5 & 07:48:52.25 & +07:50:16.6  & 33.47               	& 36.87               	& 4405.84             	& 1.94           	& -0.48              	& 0.07                   	& 0.30                     	& 1.44             	& 0.30       	\\
+			J163116.81+002349.5 & 16:31:16.81 & +00:23:49.5  & 32.63               	& -35.98              	& 4628.92             	& 2.53           	& 0.01               	& 0.18                   	& 0.29                     	& 1.44             	& 0.32       	\\
+			J073532.54+215850.0 & 07:35:32.55 & +21:58:50.0  & 35.61               	& 35.98               	& 4859.66             	& 3.27           	& 0.19               	& 0.06                   	& 0.44                     	& 1.19             	& 0.79       	\\
+			J164023.01+164552.5 & 16:40:23.02 & +16:45:52.6  & 44.59               	& -34.18              	& 4964.91             	& 2.96           	& 0.36               	& 0.07                   	& 0.35                     	& 1.27             	& 0.32       	\\
+			J153333.12+510621.8 & 15:33:33.13 & +51:06:21.9  & 49.45               	& -17.99              	& 4861.78             	& 2.51           	& -0.49              	& 0.22                   	& 0.46                     	& 1.31             	& 0.28       	\\
+			J175737.71+521523.1 & 17:57:37.71 & +52:15:23.2  & 38.52               	& -40.47              	& 4861.38             	& 3.36           	& -0.34              	& 0.10                   	& 0.55                     	& 1.51             	& 0.24       	\\
+			J184125.86+432807.8 & 18:41:25.86 & +43:28:07.9  & 46.94               	& -93.84              	& 4703.92             	& 2.61           	& -0.26              	& 0.27                   	& 0.33                     	& 1.20             	& 0.34       	\\
+			J195234.41+470859.4 & 19:52:34.41 & +47:08:59.5  & 68.57               	& -24.28              	& 4596.44             	& 2.54           	& 0.55               	& 0.07                   	& 0.82                     	& 0.95             	& 0.48       	\\
+			J215146.68+304016.0 & 21:51:46.68 & +30:40:16.0  & 73.25               	& -28.78              	& 4566.21             	& 2.48           	& 0.64               	& 0.04                   	& 0.71                     	& 0.88             	& 0.45       	\\
+			J075116.55+220137.8 & 07:51:16.56 & +22:01:37.9  & 32.87               	& 90.24               	& 4810.60             	& 2.70           	& -0.33              	& 0.02                   	& 0.30                     	& 1.35             	& 0.31       	\\
+			J003929.43+430039.5 & 00:39:29.43 & +43:00:39.6  & 33.14               	& -104.33             	& 4190.26             	& 1.87           	& -0.01              	& 0.07                   	& 0.41                     	& 1.35             	& 0.33       	\\
+			J040122.07+461504.5 & 04:01:22.08 & +46:15:04.5  & 35.43               	& -95.03              	& 4305.88             	& 1.75           	& 0.02               	& 0.10                   	& 0.57                     	& 1.37             	& 0.35       	\\
+			J040815.45+464920.1 & 04:08:15.46 & +46:49:20.1  & 33.05               	& 16.19               	& 4855.16             	& 2.65           	& -0.11              	& 0.00                   	& 0.30                     	& 1.48             	& 0.30       	\\
+			J071206.83+213038.0 & 07:12:06.84 & +21:30:38.1  & 32.66               	& 29.08               	& 4432.03             	& 1.75           	& -0.38              	& 0.11                   	& 0.40                     	& 1.47             	& 0.28       	\\
+			J222820.22+340750.3 & 22:28:20.22 & +34:07:50.3  & 34.52               	& -45.27              	& 4419.96             	& 2.06           	& -0.07              	& 0.11                   	& 0.49                     	& 1.37             	& 0.31       	\\
+			J222310.49+344357.4 & 22:23:10.50 & +34:43:57.5  & 54.06               	& -20.09              	& 4232.66             	& 1.87           	& -0.01              	& 0.03                   	& 0.86                     	& 1.22             	& 0.31       	\\
+			J222101.61+365923.6 & 22:21:01.62 & +36:59:23.7  & 30.81               	& -27.88              	& 4360.28             	& 2.23           	& 0.20               	& 0.04                   	& 0.45                     	& 1.47             	& 0.29       	\\
+			J052327.44+571126.8 & 05:23:27.45 & +57:11:26.8  & 33.54               	& -24.88              	& 4806.24             	& 3.08           	& 0.24               	& 0.07                   	& 0.45                     	& 1.43             	& 0.25       	\\
+			J235212.27+492548.4 & 23:52:12.27 & +49:25:48.4  & 39.93               	& -95.03              	& 5047.36             	& 3.30           	& -0.43              	& 0.22                   	& 0.29                     	& 1.28             	& 0.26       	\\
+			J074102.63+130520.3 & 07:41:02.64 & +13:05:20.4  & 40.83               	& 49.17               	& 5000.84             	& 3.00           	& -0.38              	& -0.02                  	& 0.30                     	& 1.35             	& 0.27       	\\
+			J061559.10+470344.9 & 06:15:59.11 & +47:03:44.9  & 36.84               	& -18.29              	& 4811.98             	& 2.82           	& -0.59              	& 0.07                   	& 0.44                     	& 1.00             	& 1.33       	\\
+			J054704.12+600827.1 & 05:47:04.13 & +60:08:27.1  & 33.19               	& -23.33              	& 4770.80             	& 2.64           	& -0.10              	& 0.06                   	& 0.40                     	& 1.46             	& 0.26       	\\
+			J055548.33+611537.1 & 05:55:48.33 & +61:15:37.1  & 33.6                	& -40.88              	& 4850.39             	& 2.57           	& -0.46              	& 0.13                   	& 0.22                     	& 1.42             	& 0.26       	\\
+			J042723.73+271546.8 & 04:27:23.73 & +27:15:46.9  & 45.73               	& -40.17              	& 4211.91             	& 1.72           	& -0.04              	& 0.05                   	& 0.79                     	& 1.33             	& 0.34       	\\
+			J035702.05+281335.2 & 03:57:02.06 & +28:13:35.3  & 31.82               	& -44.67              	& 4712.89             	& 2.44           	& 0.01               	& 0.16                   	& 0.46                     	& 1.28             	& 0.38       	\\
+			J031030.13+531759.9 & 03:10:30.13 & +53:17:59.9  & 35.34               	& -16.79              	& 4699.75             	& 2.34           	& 0.21               	& 0.00                   	& 0.89                     	& 1.51             	& 0.21       	\\
+			J091256.32+353008.3 & 09:12:56.32 & +35:30:08.3  & 73.39               	& 20.39               	& 4441.95             	& 2.33           	& 0.41               	& 0.02                   	& 0.76                     	& 0.92             	& 0.39       	\\
+			J071534.00+211353.8 & 07:15:34.00 & +21:13:53.9  & 31.68               	& 42.27               	& 4892.00             	& 2.57           	& -0.72              	& 0.11                   	& 0.34                     	& 0.59             	& 0.29       	\\
+			J101317.14+122928.8 & 10:13:17.14 & +12:29:28.8  & 45.54               	& 300.69              	& 5055.95             	& 2.24           	& -1.34              	& 0.33                   	& 0.38                     	& 1.46             	& 0.24       	\\
+			J161326.00+073218.1 & 16:13:26.00 & +07:32:18.2  & 48.45               	& -50.07              	& 5086.79             	& 3.40           	& -0.68              	& 0.29                   	& 0.93                     	& 1.38             	& 0.24       	\\
+			J173711.85+101126.6 & 17:37:11.85 & +10:11:26.7  & 30.01               	& -33.58              	& 4991.07             	& 3.49           	& -0.05              	& 0.17                   	& 0.41                     	& 1.45             	& 0.28       	\\
+			J173041.92+125640.5 & 17:30:41.92 & +12:56:40.5  & 52.67               	& 20.39               	& 4986.98             	& 3.42           	& -0.45              	& 0.22                   	& 0.30                     	& 1.09             	& 0.43       	\\
+			J172929.42+120133.3 & 17:29:29.43 & +12:01:33.3  & 39.91               	& 14.39               	& 4597.08             	& 2.67           	& 0.24               	& 0.05                   	& 0.67                     	& 1.02             	& 0.80       	\\ \bottomrule
+		\end{tabular}
+		\caption{Abundances and additional information of the 47 enhanced stars.}
+	\end{table*}
 

### 2018-02-02 article/ms.tex
newest draft for Andy

@@
 
-	At the two main absorption lines for Europium (4129\,\AA\ and 4205\,\AA) \todo{citation needed} we fitted Gaussian profiles to each star in the 454,180 giants from LAMOST DR2, and we recorded the amplitude and the wavelength of each, as well as their corresponding errors.
+	At two absorption lines for Europium (4129\,\AA\ and 4205\,\AA) we fitted Gaussian profiles to each star in the 454,180 giants from LAMOST DR2, and we recorded the amplitude and the wavelength of each, as well as their corresponding errors.
 Candidate Europium enhanced stars were selected by identifying stars that met the following criteria:

### 2018-02-05 article/ms.tex
Final Draft, what a cracker, great read

@@
 % Keep the title short and informative.
-\title[Discovery of 47 r-process stars from the LAMOST survey]{Discovery of 47 $r$-process stars from the LAMOST survey}
+\title[On the Galactic nucleosynthesis of $r$-process material.]{On the Galactic nucleosynthesis of $r$-process material.}
 
@@
 Here we report the discovery of 47 r-process enhanced stars from the LAMOST survey, more than doubling the known number in our Galaxy.
-Additionally, we provide the first estimate, to our knowledge, of whether neutron star mergers are able to account for the r-process element abundances in all known r-process enhanced stars in the Milky Way.
-The discovery of these stars implies multiple r-process sites, contrary to previous conclusions in the literature including all r-process material being produced in small amounts in common events such as core-collapse supernovae, or the material only being produced in very large amounts in very rare events, such as neutron star mergers.
+Additionally, we provide the first estimation, to our knowledge, of whether neutron star mergers are able to act as the sole site for r-process nucleosynthesis with regards to all known r-process enhanced stars in the Milky Way.
+The discovery of these stars implies multiple r-process sites, contrary to previous conclusions in the literature including all r-process material being produced in small amounts in common events such as core-collapse supernovae, or the material exclusively being produced in very large amounts in very rare events, such as neutron star mergers.
 	\end{abstract}
@@
 	For over 60 years theorists have argued about the potential sites of the r-process.
-The r-process occurs when the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the isotope undergoes a $\beta$-decay.
-The sites where this phenomena can occur are very specific, with the most favoured being core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae.
+Rapid neutron capture occurs when the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the isotope undergoes a $\beta$-decay.
+The rapid capture sites are very specific, with the most favoured being core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae.
 Core-collapse supernovae are relatively common throughout the Galaxy, but they only produce small amounts of r-process material.
@@
 However analysis of several of Reticulum II's stars show they are greatly enriched, 2-3 orders of magnitude higher than stars found in any other UFD galaxy \citep{Ji2016}.
-This degree of enrichment supports the theory that a single rare event must have occurred in the galaxies formative years to enrich it, as (for Europium especially) the heavy element yields are found to be 1000 times higher than are achieved from core-collapse supernovae ejecta.
-As the idea that 1000 supernovae could have contributed to Reticulum II is extremely improbable, then the fact that Reticulum II is so heavily enriched is evidence that at least some r-process material must be produced by a rare astrophysical event such as a neutron star-neutron star merger.
+This degree of enrichment supports the theory that a single rare event must have occurred in the galaxies formative years.
+This is supported by the observed heavy element yields (Europium especially) which are found to be 1000 times higher than are achieved from core-collapse supernovae ejecta.
+It is highly improbable that 1000 supernovae could have contributed to Reticulum II, then the enrichment of this UFD galaxy suggests that some r-process material must be produced by a rare astrophysical event such as a neutron star-neutron star merger.
 
-	While neutron star mergers or magnetorotationally driven supernovae are likely to produce significant amounts of r-process material, that is not to say that all r-process material stems from these sources.
-Rather, the rarity of these events might serve as an indication of the rarity of stars found to be heavily enhanced in these elements.
+	While neutron star mergers or magnetorotationally driven supernovae are likely to produce significant amounts of r-process material.
+However, this is not to suggest that all r-process material stems from these sources, rather, the rarity of these events possibly indicates the rarity of stars found to be heavily enhanced in these elements.
 What we then have to ask is can these rare events be responsible for all r-process stars found in the Milky Way, regardless of the relative strength of their abundance?
@@
 	In this letter we report the probable discovery of 47 of these LAMOST giants that show enhanced r-process peaks for Europium at both 4129 and 4205 Angstroms.
-	In Section 2 we outline the methods used to attain our results and the analysis done. In Section 3 we discuss what our results imply about the r-process. We conclude in section 4.
+	In Section 2 we outline the methods used to attain our results and the analysis done. In Section 3 we discuss what our results imply about the r-process. We conclude in Section 4.
 
@@
 		\item The deviation from the required wavelength in question must be less than 2 \AA;
-		\item The reduced $\chi_{\rm{r}}^{2}$ value (where the $\chi_{\rm{r}}^{2}$ value represents how well the model fit the spectrum) must be less than 3, $\chi_{\rm{r}}^{2}<3$.
+		\item The $\chi_{\rm{r}}^{2}$ value (where the $\chi_{\rm{r}}^{2}$ value represents how well the model fit the spectrum) must be less than 3, $\chi_{\rm{r}}^{2}<3$.
 		\item All of these conditions must be met for both 4129 \AA\ and 4205 \AA\ for us to consider them sufficiently Eu enhanced.
@@
 Over half the current known r-process stars come from a very metal poor ultra faint dwarf galaxy, Reticulum II.
-However, Europium we know to be totally made from the r-process, therefore even at metallicities where the s-process contributes, Europium is a valuable indication of r-process synthesis.
+However, Europium we know to be totally made from the r-process, therefore even at metallicities where the s-process contributes, Europium is a valuable indicator of r-process synthesis.
 
 	\subsection{Multiple r-process sites?}
-	While it is possible that all currently known r-process enhancements can be made by neutron star mergers, we still have cases of stars in the galaxy which show particularly weak enrichment from r-process elements ([Eu/Fe] < 0.7).
-These enhancements imply that another site of r-process element synthesis is likely to be active.
-As we show in \ref{rates}  neutron star merger rates may show that all heavily enriched stars can be enhanced by these phenomena within an adequate time-scale, but we are not able to assume that as a consequence of the merger some stars are greatly enhanced, while others are only very slightly enhanced.
+	While it is possible that all currently known r-process enhancements can be made by neutron star mergers, we still observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ([Eu/Fe] < 0.7).
+These enhancements imply that an additional site of r-process element synthesis is likely to be active.
+As we show in \ref{rates}  neutron star merger rates may show that all heavily enriched stars can be enhanced by these phenomena within an adequate time-scale.
+However, we are not able to assume that as a consequence of the merger some stars are greatly enhanced, while others are only very slightly enhanced.
 It is more accurate to propose that at least two sites exist, with one (potentially mergers) producing a massive amount of enhanced material, and another only producing a small amount, such as supernovae.
@@
 	\subsection{Core-collapse supernovae (CCSN)}
-	Core-collapse supernova is one of the sites initially proposed to have a high enough neutron density to create elements synthesised by the r-process \citep{Burbidge1957}.
+	Core-collapse supernova are one of the sites initially proposed to have a high enough neutron density to create elements synthesised by the r-process \citep{Burbidge1957}.
 
@@
 
-	Core-collapse supernovae seem to release $M_{\rm{Eu}}\approx10^{-7.5} M_{\odot}$ per event \citep{Argast2004} .
+	Regardless of the exact mechanism, core-collapse supernovae seem to release $M_{\rm{Eu}}\approx10^{-7.5} M_{\odot}$ per event \citep{Argast2004} .
 While this may not be a particularly significant amount, core-collapse supernovae occur frequently $44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$ \citep{Li2011}, and so it isn't unreasonable to suggest that, with very little mixing occurring, that much if not all r-process material could have been formed by these and recycled in the stars we present in this letter.
@@
 	Neutron star mergers are another possible site of r-process element nucleosynthesis \citep{Kasen2017,Hotok2013,Drout2017}.
-They are easily able to meet the conditions for a high neutron density as interacting tidal forces between the stars rip away neutron dense material allowing r-process element synthesis to occur easily.
-In this interaction they produce considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}, however the direct interaction and merger of a binary neutron star pair occurs very infrequently with only one ever having been directly observed, and with an upper frequency estimate of $1000\ \rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016}.
-The massive amount of material that these mergers release could more than make up for the low frequency and so, similar to core-collapse supernovae, it is not unreasonable to suggest that they are responsible for most if not all known r-process material.
+They satisfy the conditions necessary to create a high neutron density by means of interacting tidal forces between the stars, neutron dense material is accreted off the stars, allowing r-process element synthesis to occur.
+This specific process produces considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}.
+However, the direct interaction and merger of a binary neutron star pair occurs very infrequently, with currently only one direct observation, and with a frequency estimate of $1000\ \rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016}.
+The significant amount of material that these mergers release can compensate for their low frequency and so, synonymous with core-collapse supernovae, it is not unreasonable to suggest that they are responsible for most if not all known r-process material.
 
-	The recent discovery of the UFD Reticulum II \citep{Ji2016} is evidence against the case for a single r-process site.
+	The recent discovery of the UFD Reticulum II \citep{Ji2016} is evidence against the case of a single r-process site.
 Of nine stars observed in Reticulum II, 7 of them were shown to be highly enriched in r-process elements ($\rm{[Eu/Fe]\approx1.7}$) which suggests a single prolific event having occurred in close proximity to the galaxy early in it's formation, such as a neutron star merger.
@@
 
-	From these two rates we can, for the first time to our knowledge, estimate the amount of r-process stars that should be present in the Milky Way, enhanced both by purely neutron star mergers and core-collapse supernovae.
+	From these two rates, we can for the first time to our knowledge, estimate the amount of r-process stars that should be present in the Milky Way, enhanced both by purely neutron star mergers and purely core-collapse supernovae.
 We do this assuming instant recycling, and that no r-process matter pollutes stars by any other means than these.
 
-	From these rates we can find an estimate of how many r-process enhanced giants should be present from an estimate number of the Milky Way's total stars.
-As well as an estimate of how many stars, giants or otherwise, should be present in the Milky Way.
+	From these rates we can find an estimate of how many r-process enhanced giants should be present from an approximate number of the Milky Way's total stars.
+As well as an estimate of how many enhanced stars, giants or otherwise, that should be present in the Milky Way.
 
-	In preparing these calculations we assumed a constant star formation rate, 2 M$_\odot yr^{-1}$, in the disk of the Milky Way, $\rm{r=15kpc}$, with a typical IMF and giant star birth rate of approximately $0.3\ $stars per year.
+	In preparing these calculations we assumed a constant star formation rate, 2 M$_\odot yr^{-1}$, in the disk of the Milky Way, $\rm{r=15kpc}$, with a typical IMF and giant star birth rate of approximately $0.3\ $ stars per year.
 We also assumed the lifetime between $\log{g} = 3.2$ and the end of the core-helium burning phase is about $250\,{\rm Myr}$.
 Therefore if we assume a steady-state system, the number of giant stars in the Milky Way comes to approximately $7.53\times10^7$.
-This allowed us to find the percentage of the Milky Ways stars that our sample represents.
+This allows us to find the percentage of the Milky Ways stars that our sample represents.
 
-	We also state that a star is said to be enhanced if [Eu/Fe] $\geq$ 0.7, and performed the lower-bound estimate that all of our 47 stars exhibited this abundance.
-The amount of r-process material expelled is the same as previously discussed, using Europium as our identifier, of $M_{Eu}\approx10^{-4.5} M_{\odot}$.
+	We also state that a star is said to be enhanced if [Eu/Fe] $\geq$ 0.7, and performed the lower-bound estimate that all of our 47 stars exhibit this abundance.
+The amount of r-process material expelled by neutron star mergers is the same as previously discussed, using Europium as our identifier, of $M_{Eu}\approx10^{-4.5} M_{\odot}$.
 
-    It was found that in the Milky Way alone there should be present 9,896 r-process enhanced stars.
-Considering this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the now updated known amount of r-process enhanced stars which comes to 60.
+    It was found that in the Milky Way there should be present 9,896 r-process enhanced stars from solely neutron star mergers.
+Taking into account that this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the known 60 r-process stars in the Milky Way.
 
-    Scaling down from the amount of stars in the Milky Way to our sample size of $\approx450000$ giants, the amount of r-process enhanced stars we should find comes to less than one (0.0178).
+    Scaling down from the 250 billion stars in the Milky Way to our sample size of $\approx450000$ giants, the amount of enhanced stars we expect to find comes to less than one (0.0178).
 If we are to extend our sample from the 450000 giants, and instead use the entire LAMOST data release 2 (a survey of $\approx2.2$ million stars), we predict that we should still have found less than a single star (0.087) enhanced in r-process elements.
-While again this should be considered a lower bound, it is still a startling difference from the 47 that were found.
+While again this should be considered a lower bound, it is nonetheless a startling difference from the 47 that were found.
 
     We can do a similar calculation with our rate of core-collapse supernovae.
-Taking the same assumptions with minimal mixing, as well as both the ejecta ($M_{Eu}\approx10^{-4.5} M_{\odot}$) and rate ($44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$) previously discussed, we find that in the Milky Way there should be present 442 r-process enhanced stars made from core-collapse supernovae.
+Taking the same assumptions with minimal mixing, as well as both the ejecta ($M_{Eu}\approx10^{-4.5} M_{\odot}$) and rate ($44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$) previously discussed, we find that in the Milky Way there should be present 442 r-process enhanced stars made solely from core-collapse supernovae.
 
@@
     We find that, by using the assumptions listed, neutron star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for all 60 known r-process enhanced stars within $13.87\times10^9$ years, very close to the age of the universe.
-From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $3.1\times10^{11}$ years, not within the age of the universe.
-This means with our current knowledge of core-collapse supernovae frequency and the amount of r-process material they eject, there is no way that only core-collapse supernovae could enrich the entire Milky Way.
+From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $3.1\times10^{11}$ years, not at all within the age of the universe.
+This illustrates, with our current knowledge of core-collapse supernovae frequency, and the amount of r-process material they eject, core-collapse supernovae cannot be the sole source of r-process enrichment in the Milky Way.
 
-    This is reinforced by the enhanced stars found in the LAMOST sample.
-47 is greater than 10\% of all enhanced stars that should be present in the Milky Way according to the solely core-collapse supernovae rate.
+    This is reinforced by our r-process enhanced stars found in the LAMOST sample.
+Our 47 stars represent greater then 10\% of all enhanced stars present in the Milky Way if core-collapse supernovae is considered to be the singular source of r-process enhanced stars.
 However, the LAMOST data release 2 only surveyed 0.00088\% of the Milky Way.
-The idea that over 10\% of all r-process stars were found in this small a percentage is improbable, and so we can say that core-collapse supernovae can not be the only source of r-process material.
+It is highly unlikely that 10\% of the entire r-process enhanced population of the Milky Way exists within our stellar sample, it is then concluded that core-collapse supernovae can not be the only source of r-process material.
 
@@
 	\section{Conclusions}
-	We present the largest to date sample of r-process element enhanced stars.
-These stars are found at a wide range of metallicities, contrary to previous discoveries that focussed on metal-poor r-process enhanced stars.
+	We present the largest to date sample of r-process element enhanced stars to date.
+Our sample is found at a wide range of metallicities, contrary to previous discoveries that focussed on metal-poor r-process enhanced stars.
 Similarly they are not clumped in either temperatures, $log(g)$, or radial velocity.
-They don't cluster to any one end of the H-R diagram, so it is likely there is no correlation between type of star.
-They are found both in the disk and halo, and are not clustered anywhere in the sky.
+They don't cluster to any one end of the H-R diagram, highlighting no correlation between type of star, they are observed both in the disk and halo, and are not clustered anywhere in the sky.
 In addition to this we also present the first ever estimate to our knowledge, from information provided by advanced LIGO, that neutron star mergers possess the ability to synthesise all currently known r-process material in a feasible time-scale.
-We also provide evidence that we are confident to say means that core-collapse supernovae can not possibly be the only progenitors of r-process material in the Milky Way Galaxy.
+We also provide evidence that we can confidently conclude core-collapse supernovae can not possibly be the only progenitors of r-process material in the Milky Way Galaxy.
 

### 2018-02-06 article/ms.tex
Final final draft
intro + abstract comments

@@
 % Keep the title short and informative.
-\title[On the Galactic nucleosynthesis of $r$-process material.]{On the Galactic nucleosynthesis of $r$-process material.}
+\title[Discovery and origin of $r$-process stars]{On the discovery and origin of $r$-process stars in the Milky Way}
 
@@
 	Alexander P. Ji,$^{4}$
-	Anna Y. Q. Ho,$^{5}$
+	Anna Y. Q. Ho$^{5}$
 	\\
@@
 		The production of heavy elements occurs through the slow and rapid neutron capture process.
-Numerous sites satisfy the conditions needed to synthesise r-process elements, but the frequency and abundance of these sites is unclear.
-The lack of a large number of stars with strong r-process signatures limits us.
-Here we report the discovery of 47 r-process enhanced stars from the LAMOST survey, more than doubling the known number in our Galaxy.
-Additionally, we provide the first estimation, to our knowledge, of whether neutron star mergers are able to act as the sole site for r-process nucleosynthesis with regards to all known r-process enhanced stars in the Milky Way.
-The discovery of these stars implies multiple r-process sites, contrary to previous conclusions in the literature including all r-process material being produced in small amounts in common events such as core-collapse supernovae, or the material exclusively being produced in very large amounts in very rare events, such as neutron star mergers.
+Numerous sites satisfy the conditions needed for the r-process to occur, but the relative frequency of these sites is unknown largely due to the lack of a large number of stars with strong r-process signatures.
+Here we report the discovery of 47 r-process enhanced stars discovered in the LAMOST survey, more than doubling the known number in our Galaxy.
+To our knowledge, we provide the first estimate on whether neutron star mergers are frequent enough to account for all known r-process stars in the Milky Way.
+\todo{We conclude....}.
+\todo{The discovery of these stars implies multiple r-process sites.}
+		% contrary to previous conclusions in the literature including all r-process material being produced in small amounts in common events such as core-collapse supernovae, or the material exclusively being produced in very large amounts in very rare events, such as neutron star mergers.
 	\end{abstract}
@@
 
-	For over 60 years theorists have argued about the potential sites of the r-process.
+	Potential sites of the r-process have been discussed for over sixty years.
 Rapid neutron capture occurs when the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the isotope undergoes a $\beta$-decay.
-The rapid capture sites are very specific, with the most favoured being core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae.
+The rapid neutron capture sites are very specific, with the most favoured being core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae.
 Core-collapse supernovae are relatively common throughout the Galaxy, but they only produce small amounts of r-process material.
-Neutron star mergers or magnetorotationally driven supernovae, however, occur much more infrequently than core-collapse supernovae, but produce far more r-process material.
+Neutron star mergers or magnetorotationally driven supernovae, however, occur much less frequently than core-collapse supernovae, but produce far more r-process material.
 Events such as these are theorised to account for the case of the highly r-process enhanced ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}.
-Neutron star mergers may have a stronger argument to be the parent site of this level of r-process enhancement in such a small volume.
+%Neutron star mergers may have a stronger argument to be the parent site of this level of r-process enhancement in such a small volume.
 However, magnetorotationally driven supernovae are also a possible solution.
+Magnetorotationally driven supernovae may not produce as much r-process material as neutron star mergers (although still more than core-collapse supernovae), they are thought to occur more frequently than neutron-star mergers \todo{[citation needed]}, and the predicted abundance patterns make them observationally indistinguishable from neutron star mergers \citep{Ji2016}.
 
-	While magnetorotationally driven supernovae may not produce as much r-process material as neutron star mergers (although still more than core-collapse supernovae), they occur more frequently, and enough material is produced that it is currently impossible to distinguish between them through abundance signatures.
+	Europium ($Z=63$), is entirely produced through the r-process.
+This makes it a very useful signature for identifying stars that show evidence of excess pollution by r-process material.
+%\todo{CLUMSY, lose the first half-sentence:The recent discovery of the UFD Reticulum II used Europium as evidence of its r-process enhancement, and found the particularly interesting result that the UFD's level of r-process enrichment was too high to have occurred through a core-collapse supernovae event.}
+	Historically, UFD galaxies have demonstrated some of the lowest abundance ratios of r-process elements seen in the Milky Way or its satellite systems.
+However, the analysis of several of Reticulum II's stars show they are greatly enriched, 2-3 orders of magnitude higher than stars found in any other UFD galaxy \citep{Ji2016}.
+This degree of enrichment supports the theory that a single rare event must have occurred early on.
+This is supported by the observed heavy element yields which are found to be some 1000 times higher than what is achievable on average from core-collapse supernovae ejecta.
+It is highly improbable that 1000 supernovae could have contributed to Reticulum II, suggesting that the r-process material must be produced by a rarer astrophysical event such as a binary neutron star merger.
 
-	Europium (Z=63), is entirely produced through the r-process.
-This makes it a very useful signature when detecting stars that show evidence of pollution by r-process material.
-The recent discovery of the UFD Reticulum II used Europium as evidence of its r-process enhancement, and found the particularly interesting result that the UFD's level of r-process enrichment was too high to have occurred through a core-collapse supernovae event.
+	While neutron star mergers or magnetorotationally driven supernovae are likely to produce significant amounts of r-process material, it does not suggest that all r-process material stems from these sources either.
+Rather, the rarity of these events possibly indicates the rarity of stars found to be heavily enhanced in these elements.
+One could ask if neutron-star mergers could be responsible for all r-process stars known in the Milky Way?
+On the other hand, if we assume very little gas mixing, could could core-collapse supernovae create enough material to explain a single r-process star?
+If neither of these prove to be true then we can confirm that there must be multiple sties to the r-process, providing a step forward in understanding the relative fraction of these mechanisms in the Milky Way.
 
-	Historically UFD's have had some of the lowest abundance of r-process elements of any celestial body.
-However analysis of several of Reticulum II's stars show they are greatly enriched, 2-3 orders of magnitude higher than stars found in any other UFD galaxy \citep{Ji2016}.
-This degree of enrichment supports the theory that a single rare event must have occurred in the galaxies formative years.
-This is supported by the observed heavy element yields (Europium especially) which are found to be 1000 times higher than are achieved from core-collapse supernovae ejecta.
-It is highly improbable that 1000 supernovae could have contributed to Reticulum II, then the enrichment of this UFD galaxy suggests that some r-process material must be produced by a rare astrophysical event such as a neutron star-neutron star merger.
-
-	While neutron star mergers or magnetorotationally driven supernovae are likely to produce significant amounts of r-process material.
-However, this is not to suggest that all r-process material stems from these sources, rather, the rarity of these events possibly indicates the rarity of stars found to be heavily enhanced in these elements.
-What we then have to ask is can these rare events be responsible for all r-process stars found in the Milky Way, regardless of the relative strength of their abundance?
-Or perhaps, assuming very little mixing, could core-collapse supernovae create enough material to pollute the stars we've found?
+%	 stars we've found?
 And if neither of these prove to be the case, can we then conclude that there must be multiple sites of r-process element creation throughout the Milky Way, that create these elements to different extents?
 
-	To answer this question it is necessary to find and catalogue more r-process stars to find some relative fraction of enhanced stars that are either very enhanced, and so must come from a rare event.
-Or only slightly enhanced, and so must come from a more common event that produces less material.
-However, r-process stars are very rare, which makes finding this fraction difficult.
+	To answer these questions it is necessary to identify a large sample of r-process stars.
+	 However, r-process stars are very rare, which makes finding this stars difficult.
 For this reason we must look to massive data sets, such as the LAMOST sky survey.
-
-	In this letter we report the probable discovery of 47 of these LAMOST giants that show enhanced r-process peaks for Europium at both 4129 and 4205 Angstroms.
-	In Section 2 we outline the methods used to attain our results and the analysis done. In Section 3 we discuss what our results imply about the r-process. We conclude in Section 4.
+In this letter we report the  discovery of 47 r-process enhanced stars identified from LAMOST.
+	In Section 2 we outline the methods used to identify r-process enhanced candidates, and our analysis methods.
+In Section 3 we discuss what our results imply about the sites of r-process.
+We provide concluding remarks in Section 4.
 
@@
 	\begin{thebibliography}{99}
-		\bibitem[\protect\citeauthoryear{Sneden, C. et al.}{2008}]{Sneden2008}
-		Sneden C., Cowan J.J., \& Gallino R. 2013, Annual review of Astronomy \& Astrophysics, 46, 1
-		\bibitem[\protect\citeauthoryear{Ji, A. P. et al.}{2016}]{Ji2016}
-		Ji A. P., Frebel A., Chiti A., \& Simon J. D. 2016, Nature, 531
-		\bibitem[\protect\citeauthoryear{Ho et al.}{2017}]{AnnaHo2017}
-		Ho A. Y. Q., Ness M. K., Hogg David W., Rix H-W., Liu C., Yang F., Zhang Y., Hou Y.,\& Wang Y. 2017, ApJ, 836, 1
-		\bibitem[\protect\citeauthoryear{Burbidge, E. et al.}{1957}]{Burbidge1957}
-		Burbidge E. M., Burbidge G. R., Fowler W. A., \& Hoyle F. 1957, Review of Modern Physics, 29, 4
-		\bibitem[\protect\citeauthoryear{Goriely, S. et al.}{2011}]{Goriely2011}
-		Goriely S., Bauswein A. \& Janka H-T. 2011, , 738, L32
 		\bibitem[\protect\citeauthoryear{Abbott, B.P. et al.}{2016}]{LIGO2016}
@@
 		Argast D., Samland M., Thielmann F-K. \& Qian Y-Z. 2004, Astronomy and Astrophysics, 416
+		\bibitem[\protect\citeauthoryear{Burbidge, E. et al.}{1957}]{Burbidge1957}
+		Burbidge E. M., Burbidge G. R., Fowler W. A., \& Hoyle F. 1957, Review of Modern Physics, 29, 4
+		\bibitem[\protect\citeauthoryear{Burrows, A. et al.}{1995}]{Burrows1995}
+		Burrows, A., Hayes, J., \& Fryxell, Bruce A. 1992, ApJ, 450, 830
+		\bibitem[\protect\citeauthoryear{Drout, M. R. et al.}{2017}]{Drout2017}
+		Drout, M. R. et al. 2017, Science
+		\bibitem[\protect\citeauthoryear{Goriely, S. et al.}{2011}]{Goriely2011}
+		Goriely S., Bauswein A. \& Janka H-T. 2011, , 738, L32
+		\bibitem[\protect\citeauthoryear{Ho et al.}{2017}]{AnnaHo2017}
+		Ho A. Y. Q., Ness M. K., Hogg David W., Rix H-W., Liu C., Yang F., Zhang Y., Hou Y.,\& Wang Y. 2017, ApJ, 836, 1
+		\bibitem[\protect\citeauthoryear{Hotokezaka, K. et al.}{2013}]{Hotok2013}
+		Hotokezaka, K., Kiuchi, K., Kyutoku, K., Okawa, H., Skiguchi, Y., Shibata, M., \& Taniguchi, K. 2013, APS
+		\bibitem[\protect\citeauthoryear{Ji, A. P. et al.}{2016}]{Ji2016}
+		Ji A. P., Frebel A., Chiti A., \& Simon J. D. 2016, Nature, 531
+		\bibitem[\protect\citeauthoryear{Kasen, D. et al.}{2017}]{Kasen2017}
+		Kasen, D., Metzger, B., Barnes, J., Quataert, E., \& Ramirez-Ruiz, E. 2017, Nature, 551, 7678
+		\bibitem[\protect\citeauthoryear{Li, W. et al.}{2011}]{Li2011}
+		Li, W., Chornock, R., Leaman, J., Filippenko, A. V., Poznanski, D., Wang, X., Ganshalingam, M., \& Mannucci, F. 2011, Royal Astronomical Society, 412, 1473
+		\bibitem[\protect\citeauthoryear{Sneden, C. et al.}{2008}]{Sneden2008}
+		Sneden C., Cowan J.J., \& Gallino R. 2013, Annual review of Astronomy \& Astrophysics, 46, 1
 		\bibitem[\protect\citeauthoryear{Woosley, S.E. et al.}{1992}]{Woosley1992}
 		Woosley S.E, \& Hoffman R.D. 1992, ApJ, 395, 1
-		\bibitem[\protect\citeauthoryear{Burrows, A. et al.}{1995}]{Burrows1995}
-		Burrows, A., Hayes, J., \& Fryxell, Bruce A. 1992, ApJ, 450, 830
-		\bibitem[\protect\citeauthoryear{Li, W. et al.}{2011}]{Li2011}
-		Li, W., Chornock, R., Leaman, J., Filippenko, A. V., Poznanski, D., Wang, X., Ganshalingam, M., \& Mannucci, F. 2011, Royal Astronomical Society, 412, 1473
-		\bibitem[\protect\citeauthoryear{Drout, M. R. et al.}{2017}]{Drout2017}
-		Drout, M. R. et al. 2017, Science
-		\bibitem[\protect\citeauthoryear{Kasen, D. et al.}{2017}]{Kasen2017}
-		Kasen, D., Metzger, B., Barnes, J., Quataert, E., \& Ramirez-Ruiz, E. 2017, Nature, 551, 7678
-		\bibitem[\protect\citeauthoryear{Hotokezaka, K. et al.}{2013}]{Hotok2013}
-		Hotokezaka, K., Kiuchi, K., Kyutoku, K., Okawa, H., Skiguchi, Y., Shibata, M., \& Taniguchi, K. 2013, APS
 	\end{thebibliography}
@@
 			\textbf{2MASS ID}   & \textbf{RA} & \textbf{DEC} & \textbf{S/N}        	& \textbf{$\boldsymbol{V_{\rm{r}}}$}   & \textbf{$\boldsymbol{T_{\rm{eff}}}$} & \textbf{Log(g)}	& \textbf{$\boldsymbol{[\rm{Fe/H}]}$} & \textbf{$\boldsymbol{[\alpha/\rm{H}]}$} & \textbf{$\boldsymbol{\chi_{\rm{r}}^{2}}$} & \textbf{{[}Eu/Fe{]}} & \textbf{Error} \\
-			-               	& {[}deg{]}   & {[}deg{]}	& {[}$\rm{pixel}^{-1}${]} & {[}$\rm{km\ s}^{-1}${]} & {[}K{]}             	& {[}$cm\ s^{-2}${]} & {[}dex{]}          	& {[}dex{]}              	& -                        	& {[}dex{]}        	& {[}dex{]}  	\\ \midrule
+			-               	& {[}H:M:S{]}   & {[}H:M:S{]}	& {[}$\rm{pixel}^{-1}${]} & {[}$\rm{km\ s}^{-1}${]} & {[}K{]}             	& {[}$cm\ s^{-2}${]} & {[}dex{]}          	& {[}dex{]}              	& -                        	& {[}dex{]}        	& {[}dex{]}  	\\ \midrule
 			J130303.65+260837.0 & 13:03:03.65 & +26:08:37.0  & 36.48               	& -37.77              	& 4851.24             	& 2.98           	& -0.54              	& 0.19                   	& 0.42                     	& 1.39             	& 0.31       	\\

### 2018-02-07 article/ms.tex
Name change

--- 2018-02-05 article/ms.tex
@@
 % Keep the title short and informative.
-\title[On the Galactic nucleosynthesis of $r$-process material.]{On the Galactic nucleosynthesis of $r$-process material.}
+\title[On the discovery and origin of r-process stars in the Milky Way.]{On the discovery and origin of $r$-process stars in the Milky Way.}
 
@@
 		\caption{The metallicities of the 47 candidate stars.}
-		\label{fig:starindex_423451}
+		\label{fig:metallicity}
 	\end{figure}
@@
 After this process we were left with 47 potentially r-process enhanced candidates, 22 of which stand out as very strong candidates.
+An example of one of our candidates is shown in Figure \ref{fig:starindex_423451}.
 
@@
 	\subsection{Selection effects}
-	The LAMOST giants we analyse belong to a broad range of metallicity ($\rm{[Fe/H]} -1.6\ \rm{to}\ 0.6$), and don't cluster towards any position in the observed sky.
+	The LAMOST giants we analyse belong to a broad range of metallicity ($\rm{[Fe/H]} -1.6\ \rm{to}\ 0.6$) as seen in Figure \ref{fig:metallicity}, and don't cluster towards any position in the observed sky.
 These characteristics argue that the abundance we see could not have originated from a common era or site.
@@
 			\textbf{2MASS ID}   & \textbf{RA} & \textbf{DEC} & \textbf{S/N}        	& \textbf{$\boldsymbol{V_{\rm{r}}}$}   & \textbf{$\boldsymbol{T_{\rm{eff}}}$} & \textbf{Log(g)}	& \textbf{$\boldsymbol{[\rm{Fe/H}]}$} & \textbf{$\boldsymbol{[\alpha/\rm{H}]}$} & \textbf{$\boldsymbol{\chi_{\rm{r}}^{2}}$} & \textbf{{[}Eu/Fe{]}} & \textbf{Error} \\
-			-               	& {[}deg{]}   & {[}deg{]}	& {[}$\rm{pixel}^{-1}${]} & {[}$\rm{km\ s}^{-1}${]} & {[}K{]}             	& {[}$cm\ s^{-2}${]} & {[}dex{]}          	& {[}dex{]}              	& -                        	& {[}dex{]}        	& {[}dex{]}  	\\ \midrule
+			-               	& {[}H:M:S{]}   & {[}H:M:S{]}	& {[}$\rm{pixel}^{-1}${]} & {[}$\rm{km\ s}^{-1}${]} & {[}K{]}             	& {[}$\rm{cm\ s}^{-2}${]} & {[}dex{]}          	& {[}dex{]}              	& -                        	& {[}dex{]}        	& {[}dex{]}  	\\ \midrule
 			J130303.65+260837.0 & 13:03:03.65 & +26:08:37.0  & 36.48               	& -37.77              	& 4851.24             	& 2.98           	& -0.54              	& 0.19                   	& 0.42                     	& 1.39             	& 0.31       	\\

### 2018-02-07 article/ms.tex
minor

--- 2018-02-06 article/ms.tex
@@
 
-	The LAMOST survey is a low resolution ($R\approx1800$) optical survey that took spectra of stars between 3650-9000 \AA.
-The second data release from the LAMOST telescope catalogued $\approx$ 2.2 million spectra (low resolution) of stars in the northern sky.
-Of these 2.2 million, 454,180 giants were fit against a normalised spectra from a sample of 9952 giants \citep{AnnaHo2017}, and from this it became possible to analyse which giants showed an abundance or depletion of particular heavy elements.
-A machine learning code \textit{The Cannon} was used to fit a predictive model using 9952 LAMOST giant stars that were also found in the higher resolution ($R\approx22500$) APOGEE survey.
-The labels \textit{The Cannon} predicted were $T_{\rm{eff}}$, $\rm{log_{10}[g]}$, $\rm{[Fe/H]}$, and $\rm{[\alpha/Fe]}$.
-Normalised spectra was then fit to 454,180 giants from the LAMOST survey and was restricted to between 3905\,\AA\ and 9000\,\AA.
-For reference, typical uncertainties for these labels are $70\rm{K}$ for $T_{\rm{eff}}$, $0.1$ in $\rm{log_{10}[g]}$, 0.1 in $\rm{[Fe/H]}$, and 0.04 in $\rm{[\alpha/H]}$.
+	The LAMOST survey is a low resolution optical spectroscopic survey ($R\approx1800$; 3650-9000\,\AA).
+The second data release from  LAMOST \citep{lamost} contains about 2.2 million stellar spectra in the northern sky.
+Of these 2.2 million, 454,180 were identified as giant stars through a data-driven analysis known as \textit{The Cannon}.
+An overlap sample of 9,952 giant stars common to LAMOST and the higher-resolution ($R\approx22500$) APOGEE survey \citep{apogee} were used as a training set.
+	The stellar labels used by \textit{The Cannon} included $T_{\rm{eff}}$, $\log{g}$, $\rm{[Fe/H]}$, and $\rm{[\alpha/Fe]}$.
+For reference, typical uncertainties for these labels are about $70\rm{K}$ for $T_{\rm{eff}}$, $0.1$ in $\rm{log_{10}{g}}$, 0.1\,dex in $\rm{[Fe/H]}$, and 0.04\,dex in $\rm{[\alpha/Fe]}$.
 
-	We selected potential candidate stars with an over-abundance of Europium by searching for deviations from the normalized spectra supplied by \textit{The Cannon}.
+	We identified candidate r-process enhanced stars by searching for deviations surrounding between the pseudo-continuum-normalised flux and the best-fitting model spectrum surrounding
+
+	 flux and the pseudo-continuum-normalised spectra
+
+	 with an over-abundance of Europium by searching for deviations from the normalized spectra supplied by \textit{The Cannon}.
 A negative deviation implies an enhancement in a particular element while a positive deviation implies a depletion (compared to what the data-driven model predicted).

### 2018-02-07 article/ms.tex
edits up to early discussion; rest in person

@@
 		The production of heavy elements occurs through the slow and rapid neutron capture process.
-Numerous sites satisfy the conditions needed for the r-process to occur, but the relative frequency of these sites is unknown largely due to the lack of a large number of stars with strong r-process signatures.
+Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures.
 Here we report the discovery of 47 r-process enhanced stars discovered in the LAMOST survey, more than doubling the known number in our Galaxy.
@@
 
-	Heavy elements ($Z > 30$) are synthesised through the slow (s) and rapid (r) neutron capture processes \citep{Sneden2008}.
-The nucleosynthesis of these elements has been a key area in astrophysics research since it was first theorised  \citep{Burbidge1957}.
-
-	Potential sites of the r-process have been discussed for over sixty years.
+	Heavy elements ($Z > 30$) are synthesised through the slow (s) and rapid (r) neutron capture processes \citep[e.g.,][]{Burbidge1957,Sneden2008}. 
+	%Potential sites of the r-process have been discussed for over sixty years. 
 	Rapid neutron capture occurs when the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the isotope undergoes a $\beta$-decay.
-The rapid neutron capture sites are very specific, with the most favoured being core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae.
+Extremely high neutron densities (\todo{of how much}) are necessary for the r-process to occur.
+Sites meeting this criteria include core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae.
 Core-collapse supernovae are relatively common throughout the Galaxy, but they only produce small amounts of r-process material.
 Neutron star mergers or magnetorotationally driven supernovae, however, occur much less frequently than core-collapse supernovae, but produce far more r-process material.
-Events such as these are theorised to account for the case of the highly r-process enhanced ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}.
+Events such as these are theorised to account for the case of the highly r-process enhanced stars in the ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}.
 %Neutron star mergers may have a stronger argument to be the parent site of this level of r-process enhancement in such a small volume.
@@
 
-	Europium ($Z=63$), is entirely produced through the r-process.
+	Europium ($Z=63$) is entirely produced through the r-process.
 This makes it a very useful signature for identifying stars that show evidence of excess pollution by r-process material.
@@
 However, the analysis of several of Reticulum II's stars show they are greatly enriched, 2-3 orders of magnitude higher than stars found in any other UFD galaxy \citep{Ji2016}.
-This degree of enrichment supports the theory that a single rare event must have occurred early on.
-This is supported by the observed heavy element yields which are found to be some 1000 times higher than what is achievable on average from core-collapse supernovae ejecta.
+This degree of enrichment supports the theory that a single rare event must have occurred early on in the formation history of Reticulum II.
+This is supported by the observed heavy element yields, which are found to be some 1000 times higher than what is achievable on average from core-collapse supernovae ejecta.
 It is highly improbable that 1000 supernovae could have contributed to Reticulum II, suggesting that the r-process material must be produced by a rarer astrophysical event such as a binary neutron star merger.
@@
 	While neutron star mergers or magnetorotationally driven supernovae are likely to produce significant amounts of r-process material, it does not suggest that all r-process material stems from these sources either.
-Rather, the rarity of these events possibly indicates the rarity of stars found to be heavily enhanced in these elements.
+Rather, the rarity of these events might imply that they are also responsible for the rare numbers of stars  observed to have significant enhancements in r-process material.
 One could ask if neutron-star mergers could be responsible for all r-process stars known in the Milky Way?
@@
 And if neither of these prove to be the case, can we then conclude that there must be multiple sites of r-process element creation throughout the Milky Way, that create these elements to different extents?
-
-	To answer these questions it is necessary to identify a large sample of r-process stars.
+	In order to answer these questions it is necessary to identify a large sample of r-process stars.
 	 However, r-process stars are very rare, which makes finding this stars difficult.
@@
 
-	We identified candidate r-process enhanced stars by searching for deviations surrounding between the pseudo-continuum-normalised flux and the best-fitting model spectrum surrounding
-
-	 flux and the pseudo-continuum-normalised spectra
-
-	 with an over-abundance of Europium by searching for deviations from the normalized spectra supplied by \textit{The Cannon}.
-A negative deviation implies an enhancement in a particular element while a positive deviation implies a depletion (compared to what the data-driven model predicted).
-
-	At two absorption lines for Europium (4129\,\AA\ and 4205\,\AA) we fitted Gaussian profiles to each star in the 454,180 giants from LAMOST DR2, and we recorded the amplitude and the wavelength of each, as well as their corresponding errors.
-Candidate Europium enhanced stars were selected by identifying stars that met the following criteria:
+	We identified candidate r-process enhanced stars by searching for deviations surrounding between the pseudo-continuum-normalised flux and the best-fitting data-driven model spectrum.
+Specifically, we looked for deviations at the 4129\,\AA\ and 4205\,\AA\ europium absorption lines.
+At each transition we fitted a Gaussian profile to the flux residuals for all 454,180 giant stars.
+We recorded the amplitude, wavelength, and width of each profile, as well as the corresponding uncertainties on these quantities.
+	 Candidate r-process stars were identified as stars that met the following criteria:
 
 	\begin{itemize}
-		\item The amplitude of their deviation from the model needed to be less than $\rm{A}<-0.05$;
+		\item The amplitude of the gaussian profile must be less than $\rm{A}<-0.05$;
 		\item The signal to noise (S/N) must be greater than 30;
 		\item The deviation from the required wavelength in question must be less than 2 \AA;
-		\item The $\chi_{\rm{r}}^{2}$ value (where the $\chi_{\rm{r}}^{2}$ value represents how well the model fit the spectrum) must be less than 3, $\chi_{\rm{r}}^{2}<3$.
+		\item The  $\chi_{\rm{r}}^{2}$ value must be less than 3, $\chi_{\rm{r}}^{2}<3$.
 		\item All of these conditions must be met for both 4129 \AA\ and 4205 \AA\ for us to consider them sufficiently Eu enhanced.
@@
 
-	We gathered an initial sample of 62 candidates out of the 454180 LAMOST giant sample.
-These were then visually scrutinised to identify those that lacked visual evidence that they were enhanced.
-After this process we were left with 47 potentially r-process enhanced candidates, 22 of which stand out as very strong candidates.
+	These filters produced an initial sample of 62 candidates from the total sample of 454,180.
+An example candidate is shown in Figure \ref{fig:starindex_423451}.
+We visually scrutinised each candidate to remove false positives.
+After this process we were left with 47 likely r-process enhanced candidates, 22 of which stand out as very strong candidates.
 
 	\section{The r-process}
-	For the r-process to occur there must be a very high neutron density, such that neutron capture must be able to occur before the nucleus undergoes a $\beta$-decay (assuming the nucleus is in an unstable state).
+	% Repeating the introduction:
+	%For the r-process to occur there must be a very high neutron density, such that neutron capture must be able to occur before the nucleus undergoes a $\beta$-decay (assuming the nucleus is in an unstable state).
 The conditions that can create this are rare.
@@
 
-	\subsection{Selection effects}
-	The LAMOST giants we analyse belong to a broad range of metallicity ($\rm{[Fe/H]} -1.6\ \rm{to}\ 0.6$), and don't cluster towards any position in the observed sky.
-These characteristics argue that the abundance we see could not have originated from a common era or site.
+	The LAMOST giants we analyse belong to a broad range of metallicity ($-1.6 < \rm{[Fe/H]} < 0.6$), and don't cluster in any part of the sky, suggesting they do not belong to a single stellar system.
 
-	The previous sample of r-process stars, before the release of this letter, almost exclusively consists of metal-poor stars.
+	The previous sample of r-process stars, before the release of this letter, almost exclusively consists of metal-poor stars \todo{[OMG CITATIONS NEEDED DUDE]}.
 This fact is not to be confused with saying that most r-process stars found should be metal-poor stars, rather that at low metallicities we know that the s-process will not contribute, so neutron capture elements formed from these stars would be only from the r-process.
-Over half the current known r-process stars come from a very metal poor ultra faint dwarf galaxy, Reticulum II.
+Over half the current known r-process stars are members of the ultra faint dwarf galaxy, Reticulum II.
 However, Europium we know to be totally made from the r-process, therefore even at metallicities where the s-process contributes, Europium is a valuable indicator of r-process synthesis.
@@
 	While it is possible that all currently known r-process enhancements can be made by neutron star mergers, we still observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ([Eu/Fe] < 0.7).
-These enhancements imply that an additional site of r-process element synthesis is likely to be active.
-As we show in \ref{rates}  neutron star merger rates may show that all heavily enriched stars can be enhanced by these phenomena within an adequate time-scale.
+These enhancements imply that an additional site of r-process element synthesis is likely to be active \todo{or there is very efficient mixing??
+I think here you just want to say that either there is $>1$ r-process site, or there is extremely heterogeneous levels of mixing from neutron-star mergers in order to produce stars with [Eu/Fe] abundances that range many orders of magnitude...}.
+
+	%As we show in \ref{rates}  neutron star merger rates may show that all heavily enriched stars can be enhanced by these phenomena within an adequate time-scale.
 However, we are not able to assume that as a consequence of the merger some stars are greatly enhanced, while others are only very slightly enhanced.
@@
 	Regardless of the exact mechanism, core-collapse supernovae seem to release $M_{\rm{Eu}}\approx10^{-7.5} M_{\odot}$ per event \citep{Argast2004} .
-While this may not be a particularly significant amount, core-collapse supernovae occur frequently $44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$ \citep{Li2011}, and so it isn't unreasonable to suggest that, with very little mixing occurring, that much if not all r-process material could have been formed by these and recycled in the stars we present in this letter.
+While this may not be a particularly significant amount, core-collapse supernovae occur frequently \citep[$44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$;][]{Li2011}, and so it isn't unreasonable to suggest that, with very little mixing occurring, that much if not all r-process material could have been formed by these and recycled in the stars we present in this letter.
 

### 2018-02-07 article/ms.tex
some abs

@@
 Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures.
-Here we report the discovery of 47 r-process enhanced stars discovered in the LAMOST survey, more than doubling the known number in our Galaxy.
-To our knowledge, we provide the first estimate on whether neutron star mergers are frequent enough to account for all known r-process stars in the Milky Way.
-\todo{We conclude....}.
-\todo{The discovery of these stars implies multiple r-process sites.}
+Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in our Galaxy.
+After taking expected rates of core-collapse supernovae and the average r-process material ejected in each event, we find the core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work.
+Current rate estimates of neutron-star mergers imply that should be about $\todo{X}$ r-process enhanced stars in the Milky Way, and about $\todo{Y}$ in LAMOST DR2.
+\todo{conclusions....}To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way.
 		% contrary to previous conclusions in the literature including all r-process material being produced in small amounts in common events such as core-collapse supernovae, or the material exclusively being produced in very large amounts in very rare events, such as neutron star mergers.

### 2018-02-09 article/ms.tex

@@
 % Keep the title short and informative.
+
 \title[Discovery and origin of $r$-process stars]{On the discovery and origin of $r$-process stars in the Milky Way}
@@
 
+	\subsection{Selection effects}
 	The LAMOST giants we analyse belong to a broad range of metallicity ($-1.6 < \rm{[Fe/H]} < 0.6$), and don't cluster in any part of the sky, suggesting they do not belong to a single stellar system.
@@
 			\textbf{2MASS ID}   & \textbf{RA} & \textbf{DEC} & \textbf{S/N}        	& \textbf{$\boldsymbol{V_{\rm{r}}}$}   & \textbf{$\boldsymbol{T_{\rm{eff}}}$} & \textbf{Log(g)}	& \textbf{$\boldsymbol{[\rm{Fe/H}]}$} & \textbf{$\boldsymbol{[\alpha/\rm{H}]}$} & \textbf{$\boldsymbol{\chi_{\rm{r}}^{2}}$} & \textbf{{[}Eu/Fe{]}} & \textbf{Error} \\
-			-               	& {[}H:M:S{]}   & {[}H:M:S{]}	& {[}$\rm{pixel}^{-1}${]} & {[}$\rm{km\ s}^{-1}${]} & {[}K{]}             	& {[}$cm\ s^{-2}${]} & {[}dex{]}          	& {[}dex{]}              	& -                        	& {[}dex{]}        	& {[}dex{]}  	\\ \midrule
+			-               	& {[}H:M:S{]}   & {[}H:M:S{]}	& {[}$\rm{pixel}^{-1}${]} & {[}$\rm{km\ s}^{-1}${]} & {[}K{]}             	& {[}$\rm{cm\ s}^{-2}${]} & {[}dex{]}          	& {[}dex{]}              	& -                        	& {[}dex{]}        	& {[}dex{]}  	\\ \midrule
 			J130303.65+260837.0 & 13:03:03.65 & +26:08:37.0  & 36.48               	& -37.77              	& 4851.24             	& 2.98           	& -0.54              	& 0.19                   	& 0.42                     	& 1.39             	& 0.31       	\\

### 2018-02-16 article/ms.tex
cant spell nobel prize without r-process enhancement

@@
 After taking expected rates of core-collapse supernovae and the average r-process material ejected in each event, we find the core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work.
-Current rate estimates of neutron-star mergers imply that should be about $\todo{X}$ r-process enhanced stars in the Milky Way, and about $\todo{Y}$ in LAMOST DR2.
-\todo{conclusions....}To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way.
-		% contrary to previous conclusions in the literature including all r-process material being produced in small amounts in common events such as core-collapse supernovae, or the material exclusively being produced in very large amounts in very rare events, such as neutron star mergers.
+Current rate estimates of neutron-star mergers imply that should be about $9896$ r-process enhanced stars in the Milky Way, and about $0.087$ in LAMOST DR2.
+We find that neutron star mergers are also able to create all currently known r-process enhanced stars within a reasonable timescale.
+Additionally these 47 stars show no correlation to poor metallicity, providing evidence against the relationship of poor metallicity environments and the action of the r-process.
+		To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way.
 	\end{abstract}
@@
 	Heavy elements ($Z > 30$) are synthesised through the slow (s) and rapid (r) neutron capture processes \citep[e.g.,][]{Burbidge1957,Sneden2008}.
-	%Potential sites of the r-process have been discussed for over sixty years. 
 	Rapid neutron capture occurs when the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the isotope undergoes a $\beta$-decay.
-Extremely high neutron densities (\todo{of how much}) are necessary for the r-process to occur.
+Extremely high neutron densities ($>10^{24}\ \rm{free\ neutrons\ per\ cm}^{3}$) \citep[e.g.,][]{Burbidge1957,Sneden2008} are necessary for the r-process to occur.
 Sites meeting this criteria include core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae.
@@
 Events such as these are theorised to account for the case of the highly r-process enhanced stars in the ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}.
-%Neutron star mergers may have a stronger argument to be the parent site of this level of r-process enhancement in such a small volume.
-However, magnetorotationally driven supernovae are also a possible solution.
-Magnetorotationally driven supernovae may not produce as much r-process material as neutron star mergers (although still more than core-collapse supernovae), they are thought to occur more frequently than neutron-star mergers \todo{[citation needed]}, and the predicted abundance patterns make them observationally indistinguishable from neutron star mergers \citep{Ji2016}.
+	Magnetorotationally driven supernovae may not produce as much r-process material as neutron star mergers (although still more than core-collapse supernovae), they are thought to occur more frequently than neutron-star mergers \citep[e.g.,][]{Li2011, LIGO2016}, and the predicted abundance patterns make them observationally indistinguishable from neutron star mergers \citep{Ji2016}.
 
@@
 This makes it a very useful signature for identifying stars that show evidence of excess pollution by r-process material.
-%\todo{CLUMSY, lose the first half-sentence:The recent discovery of the UFD Reticulum II used Europium as evidence of its r-process enhancement, and found the particularly interesting result that the UFD's level of r-process enrichment was too high to have occurred through a core-collapse supernovae event.}
+Using Europium, Reticulum II found the particularly interesting result that the UFD's level of r-process enrichment was too high to have occurred through a core-collapse supernovae event.
 	Historically, UFD galaxies have demonstrated some of the lowest abundance ratios of r-process elements seen in the Milky Way or its satellite systems.
@@
 One could ask if neutron-star mergers could be responsible for all r-process stars known in the Milky Way?
-On the other hand, if we assume very little gas mixing, could could core-collapse supernovae create enough material to explain a single r-process star?
+On the other hand, if we assume very little gas mixing, could core-collapse supernovae create enough material to explain a single r-process star?
 If neither of these prove to be true then we can confirm that there must be multiple sties to the r-process, providing a step forward in understanding the relative fraction of these mechanisms in the Milky Way.
 
-%	 stars we've found?
-And if neither of these prove to be the case, can we then conclude that there must be multiple sites of r-process element creation throughout the Milky Way, that create these elements to different extents?
 	In order to answer these questions it is necessary to identify a large sample of r-process stars.
@@
 For this reason we must look to massive data sets, such as the LAMOST sky survey.
-In this letter we report the discovery of 47 r-process enhanced stars identified from LAMOST.
+In this letter we report the discovery of 47 r-process enhanced stars identified from LAMOST, significantly building upon the previously known Milky Way sample of 14 \citep[e.g.,][]{masho2011,Honda2004,Hayek2009,Sneden2003,Ivans2006,Hill2002,Christlieb2004,Wako2010,placo2017}.
 	In Section 2 we outline the methods used to identify r-process enhanced candidates, and our analysis methods.
@@
 
-	\section{The r-process}
-	% Repeating the introduction:
-	%For the r-process to occur there must be a very high neutron density, such that neutron capture must be able to occur before the nucleus undergoes a $\beta$-decay (assuming the nucleus is in an unstable state).
-The conditions that can create this are rare.
-Events such as supernovae or neutron star mergers list among the most favoured sites.
+	\section{Identifying the r-process}
 
@@
 
-	The previous sample of r-process stars, before the release of this letter, almost exclusively consists of metal-poor stars \todo{[OMG CITATIONS NEEDED DUDE]}.
+	The previous sample of r-process stars, before the release of this letter, almost exclusively consists of metal-poor stars \citet{Barklem2005}.
 This fact is not to be confused with saying that most r-process stars found should be metal-poor stars, rather that at low metallicities we know that the s-process will not contribute, so neutron capture elements formed from these stars would be only from the r-process.
@@
 	\subsection{Multiple r-process sites?}
-	While it is possible that all currently known r-process enhancements can be made by neutron star mergers, we still observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ([Eu/Fe] < 0.7).
-These enhancements imply that an additional site of r-process element synthesis is likely to be active \todo{or there is very efficient mixing??
-I think here you just want to say that either there is $>1$ r-process site, or there is extremely heterogeneous levels of mixing from neutron-star mergers in order to produce stars with [Eu/Fe] abundances that range many orders of magnitude...}.
-
-	%As we show in \ref{rates}  neutron star merger rates may show that all heavily enriched stars can be enhanced by these phenomena within an adequate time-scale.
-However, we are not able to assume that as a consequence of the merger some stars are greatly enhanced, while others are only very slightly enhanced.
-It is more accurate to propose that at least two sites exist, with one (potentially mergers) producing a massive amount of enhanced material, and another only producing a small amount, such as supernovae.
+	While it is possible that all currently known r-process enhancements can be made by neutron star mergers (we show this in Section \ref{rates}), we still observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ([Eu/Fe] < 0.7).
+These enhancements imply either that there is more than $1$ active r-process site, or that there is present very heterogeneous levels of mixing, such that neutron-star mergers are able to enhance stars with [Eu/Fe] abundances that range many orders of magnitude.
 
@@
 
-	From these two rates, we can for the first time to our knowledge, estimate the amount of r-process stars that should be present in the Milky Way, enhanced both by purely neutron star mergers and purely core-collapse supernovae.
+	From these two rates, we can for the first time to our knowledge, estimate the amount of r-process giants that should be present in the Milky Way, enhanced both by purely neutron star mergers, and purely core-collapse supernovae.
+As well as an estimate of how many enhanced stars, giants or otherwise, that should be present in the Milky Way.
 We do this assuming instant recycling, and that no r-process matter pollutes stars by any other means than these.
-
-	From these rates we can find an estimate of how many r-process enhanced giants should be present from an approximate number of the Milky Way's total stars.
-As well as an estimate of how many enhanced stars, giants or otherwise, that should be present in the Milky Way.
 
@@
 	We also state that a star is said to be enhanced if [Eu/Fe] $\geq$ 0.7, and performed the lower-bound estimate that all of our 47 stars exhibit this abundance.
-The amount of r-process material expelled by neutron star mergers is the same as previously discussed, using Europium as our identifier, of $M_{Eu}\approx10^{-4.5} M_{\odot}$.
+The amount of r-process material expelled by neutron star mergers is the same as previously discussed, using Europium as our tracer, of $M_{Eu}\approx10^{-4.5} M_{\odot}$.
 
-    It was found that in the Milky Way there should be present 9,896 r-process enhanced stars from solely neutron star mergers.
-Taking into account that this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the known 60 r-process stars in the Milky Way.
+	These calculations were achieved by finding a density, $\rho$, such that:
+	\begin{center}
+	$\rho$ = $M_{Ejecta}*\rm{Rate}*13.8*10^{9}$
+	\end{center}
+	Where 'Rate' is defined as the number of neutron-star mergers that occur per parsec, per year.
+
+	The total known mass of Europium exhibited in these 47 stars was then calculated:
+	\begin{center}
+	$Eu_{\rm{Mass}} = 47*Eu_{\rm{Atomic\ mass}}*N_{\rm{Eu atoms}}$\\\\
+	\end{center}
+	Where:
+	\begin{center}
+	$Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}$ and;\\\\
+	$N_{\rm{Eu\ atoms}} = 10^{[Eu/H]-12} \times N_{\rm{Hydrogen\ atoms}}$\\
+	\end{center}
+	Where the number of Hydrogen atoms was approximated from the Hydrogen atomic mass and the assumption that a giant star will be composed of $\approx$75\% Hydrogen and will have a mass of $\approx 0.8\ M_{\odot}$
+
+    It was found that in the Milky Way there should be present 9,896 r-process stars enhanced solely from neutron star mergers.
+Taking into account that this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the known 61 r-process stars in the Milky Way.
 
@@
 
-    We find that, by using the assumptions listed, neutron star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for all 60 known r-process enhanced stars within $13.87\times10^9$ years, very close to the age of the universe.
-From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $3.1\times10^{11}$ years, not at all within the age of the universe.
+    We find that, by using the assumptions listed, neutron star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.87\times10^9$ years, very close to the age of the universe.
+From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $2.4\times10^{11}$ years, not at all within the age of the universe.
 This illustrates, with our current knowledge of core-collapse supernovae frequency, and the amount of r-process material they eject, core-collapse supernovae cannot be the sole source of r-process enrichment in the Milky Way.
@@
 
-    \todo{For Andy (haven't written this bit nicely this was a thought dump): Let us consider that both of these estimates are correct, and the rates they are based on have been roughly accurate over the age of the universe (although they should have increased with time, which is actually a bit worse for us).
-Then we are left with our previous prediction of 9,896 stars enhanced purely by neutron star mergers, and another 442 stars enhanced purely by core-collapse supernovae.
-This leaves us with a new sample of r-process enhanced stars that should exist in the Milky Way of 10,338.
-    At a rough estimate, the LAMOST data release 2 took spectra for 0.00088\% of the Milky Way's stars (assuming an average amount of stars in the Milky Way of 250 billion).
-In this very small percentage, 47 r-process enhanced stars were found.
-Then, if we are able to assume that there is nothing particularly special about the area of the sky that LAMOST surveyed, scaling this size to that of the Milky Way we should find 5,340,892 r-process enhanced stars.
-Clearly there is something wrong.}
+    In an effort to confirm this, we approached the calculation from a different direction.
+Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy (75,300,000), then we would expect to find 7849 enhanced giant stars, very close to 9896 stars from the previous calculation.
 
@@
 Our sample is found at a wide range of metallicities, contrary to previous discoveries that focussed on metal-poor r-process enhanced stars.
-Similarly they are not clumped in either temperatures, $log(g)$, or radial velocity.
+These 47 stars represent the first r-process enhanced stars found at [Eu/Fe] $>-2$.
+They are not clumped in either temperatures, log(g), or radial velocity.
 They don't cluster to any one end of the H-R diagram, highlighting no correlation between type of star, they are observed both in the disk and halo, and are not clustered anywhere in the sky.
@@
 		Argast D., Samland M., Thielmann F-K. \& Qian Y-Z. 2004, Astronomy and Astrophysics, 416
+		\bibitem[\protect\citeauthoryear{Barklem, P.S. et al.}{2005}]{Barklem2005}
+		Barklem, P.S., Christlieb, N., Beers, T.C., Hill, V., Besel, M.S., Holmberg, J., Marsteller, B., Rossi, S., Zickgraf, F.-J. \& Reimers, D. 2005, A\&A, 439, 1
 		\bibitem[\protect\citeauthoryear{Burbidge, E. et al.}{1957}]{Burbidge1957}
@@
 		Burrows, A., Hayes, J., \& Fryxell, Bruce A. 1992, ApJ, 450, 830
+		\bibitem[\protect\citeauthoryear{Cui, X.-Q. et al.}{2012}]{lamost}
+		Cui, X.-Q. et al., Research in Astronomy and Astrophysics, 12, 9
 		\bibitem[\protect\citeauthoryear{Drout, M. R. et al.}{2017}]{Drout2017}
 		Drout, M. R. et al. 2017, Science
+		\bibitem[\protect\citeauthoryear{Christlieb N. et al.}{2004}]{Christlieb2004}
+		Christlieb N. et al. 2004, Astronomy \& Astrophysics, 428, 1
 		\bibitem[\protect\citeauthoryear{Goriely, S. et al.}{2011}]{Goriely2011}
 		Goriely S., Bauswein A. \& Janka H-T. 2011, , 738, L32
+		\bibitem[\protect\citeauthoryear{Hayek, W. et al.}{2009}]{Hayek2009}
+		Hayek W., Wiesendahl U., Christlieb N., Eriksson K., Barklem P. S., Hill V., Beers T. C., Farouqi K., Pfeiffer B.,\& Kratz K.-L. 2009, Astronomy and Astrophysics, 504, 1
+		\bibitem[\protect\citeauthoryear{Hill, V. et al.}{2002}]{Hill2002}
+		Hill V. et al. Astronomy \& Astrophysics, 387, 1
 		\bibitem[\protect\citeauthoryear{Ho et al.}{2017}]{AnnaHo2017}
-		Ho A. Y. Q., Ness M. K., Hogg David W., Rix H-W., Liu C., Yang F., Zhang Y., Hou Y.,\& Wang Y. 2017, ApJ, 836, 1
+		Ho A. Y. Q., Ness M. K., Hogg D. W., Rix H-W., Liu C., Yang F., Zhang Y., Hou Y.,\& Wang Y. 2017, ApJ, 836, 1
+		\bibitem[\protect\citeauthoryear{Honda S. et al.}{2004}]{Honda2004}
+		Honda S., Aoki W., Kajino T., Ando H., Beers T. C., Izumiura H., Sadakane K. \& Takada-Hidai M. 2004, ApJ, 607, 1
 		\bibitem[\protect\citeauthoryear{Hotokezaka, K. et al.}{2013}]{Hotok2013}
-		Hotokezaka, K., Kiuchi, K., Kyutoku, K., Okawa, H., Skiguchi, Y., Shibata, M., \& Taniguchi, K. 2013, APS
+		Hotokezaka K., Kiuchi K., Kyutoku K., Okawa H., Skiguchi Y., Shibata M., \& Taniguchi K. 2013, APS
+		\bibitem[\protect\citeauthoryear{Ivans, I. I. et al.}{2006}]{Ivans2006}
+		Ivans I. I.,Simmerer J., Sneden C., Lawler J. E., Cowan J. J., Gallino R., \& Bisterzo S. 2006, ApJ, 645, 1
 		\bibitem[\protect\citeauthoryear{Ji, A. P. et al.}{2016}]{Ji2016}
@@
 		\bibitem[\protect\citeauthoryear{Kasen, D. et al.}{2017}]{Kasen2017}
-		Kasen, D., Metzger, B., Barnes, J., Quataert, E., \& Ramirez-Ruiz, E. 2017, Nature, 551, 7678
+		Kasen D., Metzger B., Barnes J., Quataert E., \& Ramirez-Ruiz E. 2017, Nature, 551, 7678
+		\bibitem[\protect\citeauthoryear{Lai, D. K. et al.}{2008}]{Lai2008}
+		Lai D. K., Bolte M., Johnson J. A., Lucatello S., Heger A., \& Woosley S. E. 2008, ApJ, 681,
 		\bibitem[\protect\citeauthoryear{Li, W. et al.}{2011}]{Li2011}
-		Li, W., Chornock, R., Leaman, J., Filippenko, A. V., Poznanski, D., Wang, X., Ganshalingam, M., \& Mannucci, F. 2011, Royal Astronomical Society, 412, 1473
+		Li W., Chornock R., Leaman J., Filippenko A. V., Poznanski D., Wang X., Ganshalingam M., \& Mannucci F. 2011, Royal Astronomical Society, 412, 1473
+		\bibitem[\protect\citeauthoryear{Majewski, S.R., et al.}{2017}]{apogee}
+		Majewski S.R., et al., The Astronomical Journal, 154, 3
+		\bibitem[\protect\citeauthoryear{Mashonkina, L., et al.}{2010}]{masho2011}
+		Mashonkina L., Christlieb N., Barklem P.S., Hill V., Beers T.C., \& Velichko A., Astronomy and Astrophysics, 516, 46
+		\bibitem[\protect\citeauthoryear{Placco, V.M., et al.}{2017}]{placo2017}
+		Placco V.M., Holmbeck E. M., Frebel A., Beers T. C., Surman R. A., Ji A. P., Ezzeddine R., Points S. D., Kaleida C. C. Hansen T. T., Sakari C. M, \& Casey A. R., ApJ, 844, 1
 		\bibitem[\protect\citeauthoryear{Sneden, C. et al.}{2008}]{Sneden2008}
-		Sneden C., Cowan J.J., \& Gallino R. 2013, Annual review of Astronomy \& Astrophysics, 46, 1
+		Sneden C., Cowan J.J., \& Gallino R. 2008, Annual review of Astronomy \& Astrophysics, 46, 1
+		\bibitem[\protect\citeauthoryear{Sneden, C. et al.}{2003}]{Sneden2003}
+		Sneden C. et al. 2003, ApJ, 591, 2
+		\bibitem[\protect\citeauthoryear{Wako, A. et al.}{2010}]{Wako2010}
+		Wako A., Beers T. C., Honda S. \& Carollo D. 2010, ApJ, 723, 1
 		\bibitem[\protect\citeauthoryear{Woosley, S.E. et al.}{1992}]{Woosley1992}

### 2018-02-17 Neutron_merger.py
some text edits etc

@@ -5,14 +5,14 @@ Created on Wed Jan 24 14:38:17 2018
 @author: Matt
 """
 
-import numpy as np 
+import numpy as np
 import os
 import matplotlib.pyplot as plt
 import math
 
 from astropy import units as u
 from astropy import constants as const
-import astropy as asp 
+import astropy as asp
 
 
 
@@ -23,8 +23,8 @@ LAMOSTstars = 454180
 
 Ejecta = 1.989*10**(30)*10**(-4.5)*u.kg #Typical Eu Neutron Star Ejecta in kg from Ji's Paper
 
-#Upper limit Merger rate from LIGO paper {Upper limits on the rates of binary neutron star 
-#and neutron-star--black-hole mergers from Advanced LIGO's 
+#Upper limit Merger rate from LIGO paper {Upper limits on the rates of binary neutron star
+#and neutron-star--black-hole mergers from Advanced LIGO's
 #first observing run}
 
 #Lower limit merger rate from 1991 paper; author: Phinney E.S. {The rate of neutron star binary mergers in the universe
@@ -58,7 +58,8 @@ N_Euatoms = 10**(Eu_H - 12)*N_Hatoms
 Euatom_mass = 2.5234214*10**(-25)*u.kg
 Eu_mass = Euatom_mass*N_Euatoms #Total mass of Eu in each enhanced star (assuming average of [Eu/Fe]=0.7)
 
-Eu60 = Eu_mass*60 #Total (average) mass of Eu in the 60 stars
+Eu60 = Eu_mass*61 #Total (average) mass of Eu in the 60 stars
+
 
 Eu_density = Eu60/ObsMW #kg*parsec^(-3)
 
@@ -75,13 +76,22 @@ N_starsinvol = Density/Eu_mass
 N_stars = N_starsinvol*MilkyWayVol
 
 
+# How many should there be in LAMOST?
+N_stars_in_LAMOST = N_stars * (float(LAMOSTstars)/N_MWgiants)
+
+print("Number of r-process stars within 15 kpc sphere of Milky  Way: {:.0f}".format(
+    N_stars.to(1)))
+
+print("Number of r-process giants expected in LAMOST from NSM: {:.0f}".format(
+    N_stars_in_LAMOST.to(1)))
+
 # ((N_stars.to(1))/(250*10**9))*2200000 Relevant code for below
 # ((N_stars.to(1))/(75300000))*450000
 # ((N_stars.to(1))/(250*10**9))*450000
 
[…]

### 2018-02-17 Neutron_merger.py
my code

@@ -58,7 +58,7 @@ N_Euatoms = 10**(Eu_H - 12)*N_Hatoms
 Euatom_mass = 2.5234214*10**(-25)*u.kg
 Eu_mass = Euatom_mass*N_Euatoms #Total mass of Eu in each enhanced star (assuming average of [Eu/Fe]=0.7)
 
-Eu60 = Eu_mass*60 #Total (average) mass of Eu in the 60 stars
+Eu60 = Eu_mass*61 #Total (average) mass of Eu in the 60 stars
 
 Eu_density = Eu60/ObsMW #kg*parsec^(-3)
 

### 2018-02-17 article/ms.tex

@@
 Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures.
-Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in our Galaxy.
-After taking expected rates of core-collapse supernovae and the average r-process material ejected in each event, we find the core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work.
-Current rate estimates of neutron-star mergers imply that should be about $9896$ r-process enhanced stars in the Milky Way, and about $0.087$ in LAMOST DR2.
-We find that neutron star mergers are also able to create all currently known r-process enhanced stars within a reasonable timescale.
-Additionally these 47 stars show no correlation to poor metallicity, providing evidence against the relationship of poor metallicity environments and the action of the r-process.
+Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in the Galaxy.
+Taking expected rates of core-collapse supernovae and the average r-process material ejected per event, we find that core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work within the lifetime of the universe.
+Current estimates of neutron-star merger rates imply that there should be about 10,000 r-process enhanced stars in the Milky Way, \todo{and about $0.087$ in LAMOST DR2}.
+We find that neutron star mergers are able to create all currently known r-process enhanced stars within \todo{X} years.
 To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way.
+All 47 r-process enhanced stars have $[{\rm Fe/H}] > -2$, providing the first evidence against the hypothesis that r-process signatures are only found in poor metallicity environments.
 	\end{abstract}
@@
 	Heavy elements ($Z > 30$) are synthesised through the slow (s) and rapid (r) neutron capture processes \citep[e.g.,][]{Burbidge1957,Sneden2008}.
-	Rapid neutron capture occurs when the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the isotope undergoes a $\beta$-decay.
-Extremely high neutron densities ($>10^{24}\ \rm{free\ neutrons\ per\ cm}^{3}$) \citep[e.g.,][]{Burbidge1957,Sneden2008} are necessary for the r-process to occur.
+	Rapid neutron capture occurs when the neutron density is high enough such that the rate of neutron capture will occur faster than the rate at which an isotope undergoes a $\beta$-decay.
+Extremely high neutron densities ($>$$10^{24}\ \rm{free\ neutrons\ per\ cm}^{3}$) are necessary for the r-process to occur \citep[e.g.,][]{Burbidge1957,Sneden2008}.
 Sites meeting this criteria include core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae.
-Core-collapse supernovae are relatively common throughout the Galaxy, but they only produce small amounts of r-process material.
+Core-collapse supernovae are believed to be relatively common throughout the history of the Milky Way, but they only produce small amounts of r-process material.
 Neutron star mergers or magnetorotationally driven supernovae, however, occur much less frequently than core-collapse supernovae, but produce far more r-process material.
 Events such as these are theorised to account for the case of the highly r-process enhanced stars in the ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}.
-	Magnetorotationally driven supernovae may not produce as much r-process material as neutron star mergers (although still more than core-collapse supernovae), they are thought to occur more frequently than neutron-star mergers \citep[e.g.,][]{Li2011, LIGO2016}, and the predicted abundance patterns make them observationally indistinguishable from neutron star mergers \citep{Ji2016}.
+	Magnetorotationally driven supernovae may not produce as much r-process material as neutron star mergers (although still more than core-collapse supernovae), are thought to occur more frequently than neutron-star mergers \citep[e.g.,][]{Li2011, LIGO2016}, but the predicted abundance patterns make them observationally indistinguishable from neutron star mergers \citep{Ji2016}.
 
 	Europium ($Z=63$) is entirely produced through the r-process.
-This makes it a very useful signature for identifying stars that show evidence of excess pollution by r-process material.
-Using Europium, Reticulum II found the particularly interesting result that the UFD's level of r-process enrichment was too high to have occurred through a core-collapse supernovae event.
+This makes it a very useful signature for identifying stars that show evidence of significant contribution by r-process material.
+Using europium as a tracer, \cite{Ji2016} found that the level of r-process enrichment in  Reticulum II was too high to have occurred through a core-collapse supernovae event.
 	Historically, UFD galaxies have demonstrated some of the lowest abundance ratios of r-process elements seen in the Milky Way or its satellite systems.
@@
 	In order to answer these questions it is necessary to identify a large sample of r-process stars.
-	However, r-process stars are very rare, which makes finding this stars difficult.
+	However, r-process stars are very rare.
 For this reason we must look to massive data sets, such as the LAMOST sky survey.
@@
 An overlap sample of 9,952 giant stars common to LAMOST and the higher-resolution ($R\approx22500$) APOGEE survey \citep{apogee} were used as a training set.
-	The stellar labels used by \textit{The Cannon} included $T_{\rm{eff}}$, $\log{g}$, $\rm{[Fe/H]}$, and $\rm{[\alpha/Fe]}$.
-For reference, typical uncertainties for these labels are about $70\rm{K}$ for $T_{\rm{eff}}$, $0.1$ in $\rm{log_{10}{g}}$, 0.1\,dex in $\rm{[Fe/H]}$, and 0.04\,dex in $\rm{[\alpha/Fe]}$.
+	The stellar labels included in \textit{The Cannon} model are stellar effective temperature $T_{\rm{eff}}$, surface gravity $\log{g}$, overall metallicity $\rm{[Fe/H]}$, and average relative abundance of elements produced via $\alpha$-particle capture $\rm{[\alpha/Fe]}$.
+For reference, typical uncertainties for these labels are about $70\,\rm{K}$ for $T_{\rm{eff}}$, $0.1$ in $\log{g}$, 0.1\,dex in $\rm{[Fe/H]}$, and 0.04\,dex in $\rm{[\alpha/Fe]}$.
 
@@
 	\begin{itemize}
-		\item The amplitude of the gaussian profile must be less than $\rm{A}<-0.05$;
+		\item The amplitude of the fitted gaussian profile must be less than ${A<-0.05}$;
 		\item The signal to noise (S/N) must be greater than 30;
-		\item The deviation from the required wavelength in question must be less than 2 \AA;
-		\item The  $\chi_{\rm{r}}^{2}$ value must be less than 3, $\chi_{\rm{r}}^{2}<3$.
-		\item All of these conditions must be met for both 4129 \AA\ and 4205 \AA\ for us to consider them sufficiently Eu enhanced.
+		\item The deviation from the required wavelength in question must be less than 2\,\AA;
+		\item The reduced $\chi^{2}$ value must be less than 3, $\chi_r^{2}<3$.
+		\item All of these conditions must be met for both 4129\,\AA\ and 4205\,\AA\ for us to consider them sufficiently Eu enhanced.
 	\end{itemize}
@@
 An example candidate is shown in Figure \ref{fig:starindex_423451}.
-We visually scrutinised each candidate to remove false positives.
+We visually scrutinised each candidate to remove false positives, typically due to data reduction artefacts.
 After this process we were left with 47 likely r-process enhanced candidates, 22 of which stand out as very strong candidates.
@@
 	The LAMOST giants we analyse belong to a broad range of metallicity ($-1.6 < \rm{[Fe/H]} < 0.6$), and don't cluster in any part of the sky, suggesting they do not belong to a single stellar system.
+The lowest metallicity among the 454,180 giant stars in our sample is $[{\rm Fe/H}] \approx -2.1$.
+The previous sample of known r-process stars, before this work, exclusively consists of very metal-poor stars with $[{\rm Fe/H}] < -2$ \citep{Barklem2005}.
+This fact is not to be confused with saying that most r-process stars found should be metal-poor stars, rather that at extremely low metallicities of $[{\rm Fe/H}] \lesssim -2.6$ \citep{Simmerer2004} there is a negligible contribution from the s-process
+	and all neutron-capture elements must be formed from the r-process.
+In other words, the primary reason why all r-process enhanced stars have $[{\rm Fe/H}] < -2$ is simply because searches for r-process stars have primarily focussed in the low metallicity regime.
 
-	The previous sample of r-process stars, before the release of this letter, almost exclusively consists of metal-poor stars \citet{Barklem2005}.
-This fact is not to be confused with saying that most r-process stars found should be metal-poor stars, rather that at low metallicities we know that the s-process will not contribute, so neutron capture elements formed from these stars would be only from the r-process.
-Over half the current known r-process stars are members of the ultra faint dwarf galaxy, Reticulum II.
-However, Europium we know to be totally made from the r-process, therefore even at metallicities where the s-process contributes, Europium is a valuable indicator of r-process synthesis.
+	%Over half the current known r-process stars are members of the ultra faint dwarf galaxy, Reticulum II.
+%However, europium we know to be totally made from the r-process, therefore even at metallicities where the s-process contributes, Europium is a valuable indicator of r-process synthesis.
 
 	\subsection{Multiple r-process sites?}
-	While it is possible that all currently known r-process enhancements can be made by neutron star mergers (we show this in Section \ref{rates}), we still observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ([Eu/Fe] < 0.7).
-These enhancements imply either that there is more than $1$ active r-process site, or that there is present very heterogeneous levels of mixing, such that neutron-star mergers are able to enhance stars with [Eu/Fe] abundances that range many orders of magnitude.
+	While it is possible that all known r-process enhanced stars could be made by neutron star mergers (we show this in Section \ref{rates}), we also observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ($[{\rm Eu/Fe}] < 0.7$).
+These enhancements imply either that there is more than one active r-process site, or that there is a very heterogeneous level of gas mixing, such that neutron-star mergers are able to enhance stars with [Eu/Fe] abundances that range many orders of magnitude.
 
-	\subsection{Core-collapse supernovae (CCSN)}
+	\subsection{Core-collapse supernovae}
 	Core-collapse supernova are one of the sites initially proposed to have a high enough neutron density to create elements synthesised by the r-process \citep{Burbidge1957}.
-
-	As of yet our knowledge is incomplete on the exact mechanism that allows material with a high enough neutron density to escape the supernovae event.
+Currently, the exact  mechanism that allows material with a high enough neutron density in order to produce  r-process material is unknown.
+%	As of yet our knowledge is incomplete on the exact mechanism that allows material with a high enough neutron density to escape the supernovae event.
 	One possible mechanism is the action of high-entropy neutrino winds being released from a proto-neutron star during core-collapse.
 In this stage of the collapse, this neutrino wind is driving mass loss and could be instrumental in the expulsion of the r-process material in supernovae conditions.
-However, how much enhanced material is released from the event is very dependant on the amount of material that is allowed to fall back onto the remnant at the arrival of the reverse shock, and so often the supernovae may not release a considerable amount of material \citep{Woosley1992, Burrows1995}.
+However, how much enhanced material is released from the event depends heavily on the amount of material that is allowed to fall back onto the remnant at the arrival of the reverse shock, and so often the supernovae may not release a considerable amount of material \citep{Woosley1992, Burrows1995}.
 
-	Regardless of the exact mechanism, core-collapse supernovae seem to release $M_{\rm{Eu}}\approx10^{-7.5} M_{\odot}$ per event \citep{Argast2004} .
-While this may not be a particularly significant amount, core-collapse supernovae occur frequently \citep[$44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$;][]{Li2011}, and so it isn't unreasonable to suggest that, with very little mixing occurring, that much if not all r-process material could have been formed by these and recycled in the stars we present in this letter.
+	Regardless of the exact mechanism, core-collapse supernovae seem to release $M_{\rm{Eu}}\approx10^{-7.5} M_{\odot}$ per event \citep{Argast2004}.
+While this may not be a particularly significant mass of europium, core-collapse supernovae occur reasonably frequently \citep[44,700$\,\ \rm{Gpc}^{-3} \rm{yr^{-1}}$;][]{Li2011}, and so it isn't unreasonable to suggest that, with very little mixing occurring, that much if not all r-process material could have been formed by these and recycled in the stars we present in this letter.
 
@@
 This specific process produces considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}.
-However, the direct interaction and merger of a binary neutron star pair occurs very infrequently, with currently only one direct observation, and with a frequency estimate of $1000\ \rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016}.
+However, the direct interaction and merger of a binary neutron star pair occurs very infrequently, with currently only one direct observation, and with a frequency estimate of 1,000$\,\rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016}.
 The significant amount of material that these mergers release can compensate for their low frequency and so, synonymous with core-collapse supernovae, it is not unreasonable to suggest that they are responsible for most if not all known r-process material.
@@
 	\label{rates}
-	From the recent advanced LIGO data \citep{LIGO2016}, we are able to find an estimate for a plausible frequency at which neutron star mergers occur, as mentioned in section \ref{NSmerg}.
-As well as a reliable estimate of core-collapse supernovae rates from \citet{Li2011}.
+	From the recent advanced LIGO data \citep{LIGO2016}, we are able to find an estimate for a plausible frequency at which neutron star mergers occur, as mentioned in Section \ref{NSmerg}.
+Reliable estimates of core-collapse supernovae are also available \citep{Li2011}.
+From these two rates we can estimate the amount of r-process enhanced giants that should be present in the Milky Way, either enhanced solely by purely neutron star mergers, or purely by core-collapse supernovae.
+As well as an estimate of how many r-process enhanced stars, giants or dwarfs, that are expected to be present in the Milky Way.
+We assuming instant recycling, and that no r-process matter pollutes stars by any other means than these two mechanisms.
 
-	From these two rates, we can for the first time to our knowledge, estimate the amount of r-process giants that should be present in the Milky Way, enhanced both by purely neutron star mergers, and purely core-collapse supernovae.
-As well as an estimate of how many enhanced stars, giants or otherwise, that should be present in the Milky Way.
-We do this assuming instant recycling, and that no r-process matter pollutes stars by any other means than these.
+	\todo{1.
+Calculate mass of Eu expected form NSM within 15 kpc sphere throughout age  of  universe.
+2.
+Calculate  mass of Eu in each 0.8 solar mass star.
+3.
+How many we expect in that 15 kpc sphere throughout universe?
+4.
+Multiply by fraction of LAMOST giants/number of giant stars in Milky Way, assuming star formation rate and typical IMF etc.
+5.
+Repeat for CCSN.
+6.
+Since estimated number from CCSN is only 4 giant stars in LAMOST, then state how long it would take to produce 60 r-process stars in LAMOST: orders of magnitude longer than the age of the universe.}
+	In preparing these calculations we assumed a constant star formation rate of 2 M$_\odot {\rm yr}^{-1}$ in the disk of the Milky Way, with a typical IMF and giant star birth rate of approximately 0.3\,stars per year.
+We considered a spherical volume out to $r_\textrm{GC} = 15\,{\rm kpc}$ from the  centre of the Galaxy.
+Therefore if we assume a steady-state system, the number of red giant stars in the Milky Way comes to approximately $7.53\times10^7$.
+This allows us to find the percentage of the Milky Ways stars that our sample of r-process  stars represents.
 
-	In preparing these calculations we assumed a constant star formation rate, 2 M$_\odot yr^{-1}$, in the disk of the Milky Way, $\rm{r=15kpc}$, with a typical IMF and giant star birth rate of approximately $0.3\ $ stars per year.
-We also assumed the lifetime between $\log{g} = 3.2$ and the end of the core-helium burning phase is about $250\,{\rm Myr}$.
-Therefore if we assume a steady-state system, the number of giant stars in the Milky Way comes to approximately $7.53\times10^7$.
-This allows us to find the percentage of the Milky Ways stars that our sample represents.
+	We assume that a star is said to be enhanced if $[{\rm Eu/Fe}] \geq 0.7$, and assert that all 47 stars here exhibit abundances exceeding this lower-bound.
+Taking the mass of europium ejected from a neutron star merger as $M_{\rm Eu}\approx10^{-4.5}\,M_{\odot}$, this allows us to calculate  a density of europium $\rho_{\rm Eu}$,
+\begin{equation}
+	\centering
+	\rho_{\rm Eu} = M_\textrm{Eu}\frac{dN}{dt}(13.87\times10^9\,{\rm yr})
+\end{equation}
 
-	We also state that a star is said to be enhanced if [Eu/Fe] $\geq$ 0.7, and performed the lower-bound estimate that all of our 47 stars exhibit this abundance.
-The amount of r-process material expelled by neutron star mergers is the same as previously discussed, using Europium as our tracer, of $M_{Eu}\approx10^{-4.5} M_{\odot}$.
-
-	These calculations were achieved by finding a density, $\rho$, such that:
-	\begin{center}
-	$\rho$ = $M_{Ejecta}*\rm{Rate}*13.8*10^{9}$
-	\end{center}
-	Where 'Rate' is defined as the number of neutron-star mergers that occur per parsec, per year.
+\noindent{}where ${dN}/{dt}$ is the estimated rate of neutron star mergers (1,000$\,{\rm Gpc}^{-3}{\rm yr}^{-1}$).
 
 	The total known mass of Europium exhibited in these 47 stars was then calculated:
-	\begin{center}
-	$Eu_{\rm{Mass}} = 47*Eu_{\rm{Atomic\ mass}}*N_{\rm{Eu atoms}}$\\\\
-	\end{center}
+	\begin{equation}
+	Eu_{\rm{Mass}} = 47*Eu_{\textrm{Atomic\,\,mass}}*N_{\textrm{Eu}}
+	\end{equation}
 	Where:
-	\begin{center}
-	$Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}$ and;\\\\
-	$N_{\rm{Eu\ atoms}} = 10^{[Eu/H]-12} \times N_{\rm{Hydrogen\ atoms}}$\\
-	\end{center}
+	\begin{equation}
+	Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}  \quad\textrm{and}\\
+	N_{\rm{Eu\ atoms}} = 10^{[Eu/H]-12} \times N_{\rm{Hydrogen\ atoms}}
+	\end{equation}
 	Where the number of Hydrogen atoms was approximated from the Hydrogen atomic mass and the assumption that a giant star will be composed of $\approx$75\% Hydrogen and will have a mass of $\approx 0.8\ M_{\odot}$
@@
 Our sample is found at a wide range of metallicities, contrary to previous discoveries that focussed on metal-poor r-process enhanced stars.
-These 47 stars represent the first r-process enhanced stars found at [Eu/Fe] $>-2$.
-They are not clumped in either temperatures, log(g), or radial velocity.
-They don't cluster to any one end of the H-R diagram, highlighting no correlation between type of star, they are observed both in the disk and halo, and are not clustered anywhere in the sky.
-In addition to this we also present the first ever estimate to our knowledge, from information provided by advanced LIGO, that neutron star mergers possess the ability to synthesise all currently known r-process material in a feasible time-scale.
+These 47 stars represent the first r-process enhanced stars found at [Fe/H] $>-2$.
+The sample is not grouped in effective temperatures, surface gravity, or radial velocity, and are not clustered in any  particular location on the sky.
+We present the first estimate, to our knowledge, that neutron star mergers could be synthesise all r-process material in the known r-process enhanced stars within the age of the universe.
 We also provide evidence that we can confidently conclude core-collapse supernovae can not possibly be the only progenitors of r-process material in the Milky Way Galaxy.
@@
 		Placco V.M., Holmbeck E. M., Frebel A., Beers T. C., Surman R. A., Ji A. P., Ezzeddine R., Points S. D., Kaleida C. C. Hansen T. T., Sakari C. M, \& Casey A. R., ApJ, 844, 1
+		\bibitem[Simmerer et al.(2004)]{Simmerer2004} Simmerer, J., Sneden, C., Cowan, J.~J., et al.\ 2004, \apj, 617, 1091 
 		\bibitem[\protect\citeauthoryear{Sneden, C. et al.}{2008}]{Sneden2008}

### 2018-02-17 Neutron_merger.py
math is hard

@@ -7,7 +7,7 @@ Created on Wed Jan 24 14:38:17 2018
 
 import numpy as np
 import os
-import matplotlib.pyplot as plt
+#import matplotlib.pyplot as plt
 import math
 
 from astropy import units as u
@@ -16,10 +16,10 @@ import astropy as asp
 
 
 
-MilkyWayVol = 4/3*math.pi*(15000*u.pc)**3 #radius of MW=15000 pc; Vol in pc^3
-N_MWstars = 250*10^(9) # Average number of stars in MW (+/- 150 billion error)
-N_MWgiants = 75300000
-LAMOSTstars = 454180
+MilkyWayVol = 4.0/3.0*math.pi*(15000.0*u.pc)**3 #radius of MW=15000 pc; Vol in pc^3
+N_MWstars = 250.0*10**9 # Average number of stars in MW (+/- 150 billion error)
+N_MWgiants = 75300000.0
+LAMOSTstars = 454180.0
 
 Ejecta = 1.989*10**(30)*10**(-4.5)*u.kg #Typical Eu Neutron Star Ejecta in kg from Ji's Paper
 
@@ -59,6 +59,7 @@ Euatom_mass = 2.5234214*10**(-25)*u.kg
 Eu_mass = Euatom_mass*N_Euatoms #Total mass of Eu in each enhanced star (assuming average of [Eu/Fe]=0.7)
 
 Eu60 = Eu_mass*61 #Total (average) mass of Eu in the 60 stars
+
 
 Eu_density = Eu60/ObsMW #kg*parsec^(-3)
 

### 2018-02-18 article/ms.tex
proof read

@@
 Taking expected rates of core-collapse supernovae and the average r-process material ejected per event, we find that core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work within the lifetime of the universe.
-Current estimates of neutron-star merger rates imply that there should be about 10,000 r-process enhanced stars in the Milky Way, \todo{and about $0.087$ in LAMOST DR2}.
-We find that neutron star mergers are able to create all currently known r-process enhanced stars within \todo{X} years.
+Current estimates of neutron-star merger rates imply that there should be about 13,000 r-process enhanced stars in the Milky Way, and about $80$ in LAMOST DR2.
+We find that neutron-star mergers are able to create all currently known r-process enhanced stars within $10.57 \times 10^{9}$ years.
 To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way.
@@
 	\begin{keywords}
-		nucleosynthesis -- r-process -- neutron star mergers -- core-collapse supernovae
+		nucleosynthesis -- r-process -- neutron-star mergers -- core-collapse supernovae
 	\end{keywords}
@@
 Extremely high neutron densities ($>$$10^{24}\ \rm{free\ neutrons\ per\ cm}^{3}$) are necessary for the r-process to occur \citep[e.g.,][]{Burbidge1957,Sneden2008}.
-Sites meeting this criteria include core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae.
+Sites meeting this criteria include core-collapse supernovae, neutron-star mergers, or magnetorotationally driven supernovae.
 Core-collapse supernovae are believed to be relatively common throughout the history of the Milky Way, but they only produce small amounts of r-process material.
-Neutron star mergers or magnetorotationally driven supernovae, however, occur much less frequently than core-collapse supernovae, but produce far more r-process material.
+Neutron-star mergers or magnetorotationally driven supernovae, however, occur much less frequently than core-collapse supernovae, but produce far more r-process material.
 Events such as these are theorised to account for the case of the highly r-process enhanced stars in the ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}.
-	Magnetorotationally driven supernovae may not produce as much r-process material as neutron star mergers (although still more than core-collapse supernovae), are thought to occur more frequently than neutron-star mergers \citep[e.g.,][]{Li2011, LIGO2016}, but the predicted abundance patterns make them observationally indistinguishable from neutron star mergers \citep{Ji2016}.
+	Magnetorotationally driven supernovae may not produce as much r-process material as neutron-star mergers (although still more than core-collapse supernovae), are thought to occur more frequently than neutron-star mergers \citep[e.g.,][]{Li2011, LIGO2016}, but the predicted abundance patterns make them observationally indistinguishable from neutron-star mergers \citep{Ji2016}.
 
@@
 This is supported by the observed heavy element yields, which are found to be some 1000 times higher than what is achievable on average from core-collapse supernovae ejecta.
-It is highly improbable that 1000 supernovae could have contributed to Reticulum II, suggesting that the r-process material must be produced by a rarer astrophysical event such as a binary neutron star merger.
+It is highly improbable that 1000 supernovae could have contributed to Reticulum II, suggesting that the r-process material must be produced by a rarer astrophysical event such as a binary neutron-star merger.
 
-	While neutron star mergers or magnetorotationally driven supernovae are likely to produce significant amounts of r-process material, it does not suggest that all r-process material stems from these sources either.
+	While neutron-star mergers or magnetorotationally driven supernovae are likely to produce significant amounts of r-process material, it does not suggest that all r-process material stems from these sources either.
 Rather, the rarity of these events might imply that they are also responsible for the rare numbers of stars  observed to have significant enhancements in r-process material.
@@
 	\subsection{Multiple r-process sites?}
-	While it is possible that all known r-process enhanced stars could be made by neutron star mergers (we show this in Section \ref{rates}), we also observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ($[{\rm Eu/Fe}] < 0.7$).
+	While it is possible that all known r-process enhanced stars could be made by neutron-star mergers (we show this in Section \ref{rates}), we also observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ($[{\rm Eu/Fe}] < 0.7$).
 These enhancements imply either that there is more than one active r-process site, or that there is a very heterogeneous level of gas mixing, such that neutron-star mergers are able to enhance stars with [Eu/Fe] abundances that range many orders of magnitude.
@@
 %	As of yet our knowledge is incomplete on the exact mechanism that allows material with a high enough neutron density to escape the supernovae event.
-	One possible mechanism is the action of high-entropy neutrino winds being released from a proto-neutron star during core-collapse.
+	One possible mechanism is the action of high-entropy neutrino winds being released from a proto-neutron-star during core-collapse.
 In this stage of the collapse, this neutrino wind is driving mass loss and could be instrumental in the expulsion of the r-process material in supernovae conditions.
@@
 
-	\subsection{Neutron star mergers}
+	\subsection{Neutron-star mergers}
 	\label{NSmerg}
-	Neutron star mergers are another possible site of r-process element nucleosynthesis \citep{Kasen2017,Hotok2013,Drout2017}.
+	Neutron-star mergers are another possible site of r-process element nucleosynthesis \citep{Kasen2017,Hotok2013,Drout2017}.
 They satisfy the conditions necessary to create a high neutron density by means of interacting tidal forces between the stars, neutron dense material is accreted off the stars, allowing r-process element synthesis to occur.
 This specific process produces considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}.
-However, the direct interaction and merger of a binary neutron star pair occurs very infrequently, with currently only one direct observation, and with a frequency estimate of 1,000$\,\rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016}.
+However, the direct interaction and merger of a binary neutron-star pair occurs very infrequently, with currently only one direct observation, and with a frequency estimate of 1,000$\,\rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016}.
 The significant amount of material that these mergers release can compensate for their low frequency and so, synonymous with core-collapse supernovae, it is not unreasonable to suggest that they are responsible for most if not all known r-process material.
@@
 	The recent discovery of the UFD Reticulum II \citep{Ji2016} is evidence against the case of a single r-process site.
-Of nine stars observed in Reticulum II, 7 of them were shown to be highly enriched in r-process elements ($\rm{[Eu/Fe]\approx1.7}$) which suggests a single prolific event having occurred in close proximity to the galaxy early in it's formation, such as a neutron star merger.
+Of nine stars observed in Reticulum II, 7 of them were shown to be highly enriched in r-process elements ($\rm{[Eu/Fe]\approx1.7}$) which suggests a single prolific event having occurred in close proximity to the galaxy early in it's formation, such as a neutron-star merger.
 However, two of the stars observed were only weakly enhanced in r-process elements which suggests that there must have been a second, less efficient, form of r-process enhancement present.
@@
 	\label{rates}
-	From the recent advanced LIGO data \citep{LIGO2016}, we are able to find an estimate for a plausible frequency at which neutron star mergers occur, as mentioned in Section \ref{NSmerg}.
+	From the recent advanced LIGO data \citep{LIGO2016}, we are able to find an estimate for a plausible frequency at which neutron-star mergers occur, as mentioned in Section \ref{NSmerg}.
 Reliable estimates of core-collapse supernovae are also available \citep{Li2011}.
-From these two rates we can estimate the amount of r-process enhanced giants that should be present in the Milky Way, either enhanced solely by purely neutron star mergers, or purely by core-collapse supernovae.
+From these two rates we can estimate the amount of r-process enhanced giants that should be present in the Milky Way, either enhanced solely by purely neutron-star mergers, or purely by core-collapse supernovae.
 As well as an estimate of how many r-process enhanced stars, giants or dwarfs, that are expected to be present in the Milky Way.
 We assuming instant recycling, and that no r-process matter pollutes stars by any other means than these two mechanisms.
+In these calculations a star is deemed to be 'enhanced' where $[{\rm Eu/Fe}] \geq 0.7$.
 
@@
 Calculate mass of Eu expected form NSM within 15 kpc sphere throughout age of universe.
-2.
-Calculate  mass of Eu in each 0.8 solar mass star.
+DONE 2.
+Calculate  mass of Eu in each 0.8 solar mass star DONE.
 3.
@@
 Since estimated number from CCSN is only 4 giant stars in LAMOST, then state how long it would take to produce 60 r-process stars in LAMOST: orders of magnitude longer than the age of the universe.}
-	In preparing these calculations we assumed a constant star formation rate of 2 M$_\odot {\rm yr}^{-1}$ in the disk of the Milky Way, with a typical IMF and giant star birth rate of approximately 0.3\,stars per year.
-We considered a spherical volume out to $r_\textrm{GC} = 15\,{\rm kpc}$ from the  centre of the Galaxy.
-Therefore if we assume a steady-state system, the number of red giant stars in the Milky Way comes to approximately $7.53\times10^7$.
-This allows us to find the percentage of the Milky Ways stars that our sample of r-process  stars represents.
 
-	We assume that a star is said to be enhanced if $[{\rm Eu/Fe}] \geq 0.7$, and assert that all 47 stars here exhibit abundances exceeding this lower-bound.
-Taking the mass of europium ejected from a neutron star merger as $M_{\rm Eu}\approx10^{-4.5}\,M_{\odot}$, this allows us to calculate  a density of europium $\rho_{\rm Eu}$,
+	Taking the mass of europium ejected from a neutron-star merger as $M_{\rm Eu}\approx10^{-4.5}\,M_{\odot}$, we can calculate a density of Europium $\rho_{\rm Eu}$,
 \begin{equation}
@@
 
-\noindent{}where ${dN}/{dt}$ is the estimated rate of neutron star mergers (1,000$\,{\rm Gpc}^{-3}{\rm yr}^{-1}$).
+\noindent{}where ${dN}/{dt}$ is the estimated rate of neutron-star mergers (1,000$\,{\rm Gpc}^{-3}{\rm yr}^{-1}$).
+From this calculation we expect there to be present $\approx1.23 \times 10^{25}$ kilograms of Europium within a 15 kpc radius sphere from the centre of the Milky Way.
 
@@
 	\begin{equation}
-	Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}  \quad\textrm{and}\\
+	Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}  \quad\textrm{and}\
+	\end{equation}
+	\begin{equation}
 	N_{\rm{Eu\ atoms}} = 10^{[Eu/H]-12} \times N_{\rm{Hydrogen\ atoms}}
 	\end{equation}
-	Where the number of Hydrogen atoms was approximated from the Hydrogen atomic mass and the assumption that a giant star will be composed of $\approx$75\% Hydrogen and will have a mass of $\approx 0.8\ M_{\odot}$
+	The number of Hydrogen atoms was approximated from the Hydrogen atomic mass, and the assumption was made that a giant star will be composed of $\approx$75\% Hydrogen and each star possesses an average mass of $\approx 0.8\ M_{\odot}$.
+These assumption mean that a Europium mass of $9.3 \times 10^{20}$ kilograms is required to be present in the star for it to be deemed 'enhanced'.
 
-    It was found that in the Milky Way there should be present 9,896 r-process stars enhanced solely from neutron star mergers.
+    It was found that in the Milky Way there should be present 13,194 r-process stars enhanced solely from neutron-star mergers.
 Taking into account that this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the known 61 r-process stars in the Milky Way.
 
-    Scaling down from the 250 billion stars in the Milky Way to our sample size of $\approx450000$ giants, the amount of enhanced stars we expect to find comes to less than one (0.0178).
+    In preparing these calculations we assumed a constant star formation rate of 2 M$_\odot {\rm yr}^{-1}$ in the disk of the Milky Way, with a typical IMF and giant star birth rate of approximately 0.3 stars per year.
+Therefore if we assume a steady-state system, the number of red giant stars in the Milky Way comes to approximately $7.53\times10^7$.
+This allows us to find the fraction of the Milky Ways giants that our sample of r-process stars represents.
+Multiplying this fraction by the 13,194 stars that should be present in the Milky Way, we expect to be present 80 enhanced stars in LAMOST DR2, a number consistent with the 61 we now know of.
+
+    %Scaling down from the 250 billion stars in the Milky Way to our sample size of $\approx450000$ giants, the amount of enhanced stars we expect to find comes to less than one (0.0178).
 If we are to extend our sample from the 450000 giants, and instead use the entire LAMOST data release 2 (a survey of $\approx2.2$ million stars), we predict that we should still have found less than a single star (0.087) enhanced in r-process elements.
@@
     We can do a similar calculation with our rate of core-collapse supernovae.
-Taking the same assumptions with minimal mixing, as well as both the ejecta ($M_{Eu}\approx10^{-4.5} M_{\odot}$) and rate ($44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$) previously discussed, we find that in the Milky Way there should be present 442 r-process enhanced stars made solely from core-collapse supernovae.
+Taking the same assumptions with minimal mixing, as well as both the ejecta ($M_{Eu}\approx10^{-4.5} M_{\odot}$) and rate ($44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$) previously discussed, we find that in the Milky Way there should be present 590 r-process enhanced stars made solely from core-collapse supernovae.
+Applying the same method as utilised in the neutron-star merger calculations, we expect there to be present only 4 r-process enhanced stars in LAMOST DR2 enhanced entirely by core-collapse supernovae.
 
-    Were we to scale this down to our sample size of $\approx450000$ giants we arrive at a figure of $8.0\times10^{-4}$ stars that should have been observed.
+    %Were we to scale this down to our sample size of $\approx450000$ giants we arrive at a figure of $8.0\times10^{-4}$ stars that should have been observed.
 Scaling again to the full LAMOST sample we would then expect to find $3.9\times10^{-3}$ enhanced stars.
 
-    From these estimates we can find an approximation for whether or not either neutron star mergers or core-collapse supernovae by themselves are sufficient to enrich our entire r-process enhanced catalogue.
+    From these estimates we find an approximation for whether or not either neutron-star mergers or core-collapse supernovae by themselves are sufficient to enrich our entire r-process enhanced catalogue.
 
-    We find that, by using the assumptions listed, neutron star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.87\times10^9$ years, very close to the age of the universe.
-From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $2.4\times10^{11}$ years, not at all within the age of the universe.
-This illustrates, with our current knowledge of core-collapse supernovae frequency, and the amount of r-process material they eject, core-collapse supernovae cannot be the sole source of r-process enrichment in the Milky Way.
+    By using the assumptions listed, neutron-star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.87\times10^{9}$ years, very close to the age of the universe.
+From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $2.4\times10^{11}$ years, orders of magnitude longer than the age of the universe.
+This illustrates, with our current knowledge of core-collapse supernovae frequency, and the amount of r-process material they eject, that core-collapse supernovae cannot be the sole source of r-process enrichment in the Milky Way.
 
-    This is reinforced by our r-process enhanced stars found in the LAMOST sample.
-Our 47 stars represent greater then 10\% of all enhanced stars present in the Milky Way if core-collapse supernovae is considered to be the singular source of r-process enhanced stars.
+    This is reinforced by the r-process enhanced stars found in the LAMOST sample.
+Our 47 stars represent almost 10\% of all enhanced stars present in the Milky Way if core-collapse supernovae is considered to be the singular source of r-process enhanced stars.
 However, the LAMOST data release 2 only surveyed 0.00088\% of the Milky Way.
-It is highly unlikely that 10\% of the entire r-process enhanced population of the Milky Way exists within our stellar sample, it is then concluded that core-collapse supernovae can not be the only source of r-process material.
+It is highly unlikely that close to 10\% of the entire r-process enhanced population of the Milky Way exists within our stellar sample, it is then concluded that core-collapse supernovae can not be the only source of r-process material.
 
-    In an effort to confirm this, we approached the calculation from a different direction.
-Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy (75,300,000), then we would expect to find 7849 enhanced giant stars, very close to 9896 stars from the previous calculation.
+    In an effort to confirm these numbers, we approached the calculation from a different direction.
+Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy (75,300,000), then we would expect to find 7849 enhanced giant stars, very close to the 13,194 stars from the previous calculation.
 
@@
 The sample is not grouped in effective temperatures, surface gravity, or radial velocity, and are not clustered in any  particular location on the sky.
-We present the first estimate, to our knowledge, that neutron star mergers could be synthesise all r-process material in the known r-process enhanced stars within the age of the universe.
-We also provide evidence that we can confidently conclude core-collapse supernovae can not possibly be the only progenitors of r-process material in the Milky Way Galaxy.
+We present the first estimate, to our knowledge, that neutron-star mergers could be synthesise all r-process material in the known r-process enhanced stars within the age of the universe.
+We also provide evidence to confidently conclude core-collapse supernovae can not possibly be the only progenitors of r-process material in the Milky Way Galaxy.
 

### 2018-02-23 article/ms.tex
The best damn paper ever written

@@
 
-	\todo{1.
-Calculate mass of Eu expected form NSM within 15 kpc sphere throughout age of universe.
-DONE 2.
-Calculate  mass of Eu in each 0.8 solar mass star DONE.
-3.
-How many we expect in that 15 kpc sphere throughout universe?
-4.
-Multiply by fraction of LAMOST giants/number of giant stars in Milky Way, assuming star formation rate and typical IMF etc.
-5.
-Repeat for CCSN.
-6.
-Since estimated number from CCSN is only 4 giant stars in LAMOST, then state how long it would take to produce 60 r-process stars in LAMOST: orders of magnitude longer than the age of the universe.}
-
 	Taking the mass of europium ejected from a neutron-star merger as $M_{\rm Eu}\approx10^{-4.5}\,M_{\odot}$, we can calculate a density of Europium $\rho_{\rm Eu}$,
@@
 	\begin{equation}
-	Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}  \quad\textrm{and}\
+	Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}  \quad\textrm{and}
 	\end{equation}

### 2018-02-27 article/ms.tex
I got 96 for this subject which is just primo get around me

@@
 Taking expected rates of core-collapse supernovae and the average r-process material ejected per event, we find that core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work within the lifetime of the universe.
-Current estimates of neutron-star merger rates imply that there should be about 13,000 r-process enhanced stars in the Milky Way, and about $80$ in LAMOST DR2.
+Current estimates of neutron-star merger rates imply that there should be about 13,000 r-process enhanced stars in the Milky Way, and about $79$ in LAMOST DR2.
 We find that neutron-star mergers are able to create all currently known r-process enhanced stars within $10.57 \times 10^{9}$ years.
@@
 	\begin{figure}
-		\includegraphics[width=\columnwidth]{423451}
+		\includegraphics[width=\columnwidth]{229257}
 		\caption{The spectral region around two Europium absorption lines at 4129 and 4205 Angstroms.
 This particular star's spectra (black) shows clear absorption at these wavelengths, as compared to the data-driven model (red).}
-		\label{fig:starindex_423451}
+		\label{fig:starindex_229257}
 	\end{figure}
@@
 
-    It was found that in the Milky Way there should be present 13,194 r-process stars enhanced solely from neutron-star mergers.
+    It was found that in the Milky Way there should be present 13,060 r-process stars enhanced solely from neutron-star mergers.
 Taking into account that this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the known 61 r-process stars in the Milky Way.
@@
 This allows us to find the fraction of the Milky Ways giants that our sample of r-process stars represents.
-Multiplying this fraction by the 13,194 stars that should be present in the Milky Way, we expect to be present 80 enhanced stars in LAMOST DR2, a number consistent with the 61 we now know of.
+Multiplying this fraction by the 13,060 stars that should be present in the Milky Way, we expect to be present 79 enhanced stars in LAMOST DR2, a number consistent with the 61 we now know of.
 
@@
     In an effort to confirm these numbers, we approached the calculation from a different direction.
-Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy (75,300,000), then we would expect to find 7849 enhanced giant stars, very close to the 13,194 stars from the previous calculation.
+Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy (75,300,000), then we would expect to find 7849 enhanced giant stars, very close to the 13,060 stars from the previous calculation.
 

### 2018-02-28 article/ms.tex
minor

@@
 Current estimates of neutron-star merger rates imply that there should be about 13,000 r-process enhanced stars in the Milky Way, and about $79$ in LAMOST DR2.
-We find that neutron-star mergers are able to create all currently known r-process enhanced stars within $10.57 \times 10^{9}$ years.
+We find that neutron-star mergers are able to create all currently known r-process enhanced stars within about 10\,Gyr.
 To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way.
@@
 
-    By using the assumptions listed, neutron-star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.87\times10^{9}$ years, very close to the age of the universe.
+    By using the assumptions listed, neutron-star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.9\times10^{9}$ years, very close to the age of the universe.
 From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $2.4\times10^{11}$ years, orders of magnitude longer than the age of the universe.
@@
 Our 47 stars represent almost 10\% of all enhanced stars present in the Milky Way if core-collapse supernovae is considered to be the singular source of r-process enhanced stars.
-However, the LAMOST data release 2 only surveyed 0.00088\% of the Milky Way.
+However, the LAMOST data release 2 only surveyed a small fraction of the Milky Way.
 It is highly unlikely that close to 10\% of the entire r-process enhanced population of the Milky Way exists within our stellar sample, it is then concluded that core-collapse supernovae can not be the only source of r-process material.
@@
     In an effort to confirm these numbers, we approached the calculation from a different direction.
-Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy (75,300,000), then we would expect to find 7849 enhanced giant stars, very close to the 13,060 stars from the previous calculation.
+Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy, then we would expect to find about 7,849 r-process enhanced giant stars, very close to the 13,060 stars from the previous calculation.
 

### 2018-03-01 article/ms.tex
arrange other co-auths alphabetically and add JBH

@@
 	Alex J. Kemp,$^{1}$\newauthor
-	John C. Lattanzio,$^{1}$
-	Kevin C. Schlaufman,$^{3}$
-	Alexander P. Ji,$^{4}$
-	Anna Y. Q. Ho$^{5}$
+    Joss Bland-Hawthorn?,$^3$
+    Anna Y. Q. Ho?,$^4$
+    Alexander P. Ji?,$^5$
+	John C. Lattanzio?,$^{1}$
+	Kevin C. Schlaufman?,$^{6}$
 	\\
@@
 	$^{2}$Faculty of Information Technology, Monash University, Clayton Campus, Victoria 3800, Australia\\
-	$^{3}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA\\
-	$^{4}$Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA\\
-	$^{5}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, CA, 91125, USA
+    $^{3}$Sifa, University of Sydney\\
+	$^{4}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, CA, 91125, USA\\
+    $^{5}$Carnegie Observatories\\
+    $^{6}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA
 }

### 2018-04-03 article/ms.tex
whoops
author comments WOO

@@
     Alexander P. Ji?,$^5$
-	John C. Lattanzio?,$^{1}$
+	John C. Lattanzio?,$^{1}$\newauthor
 	Kevin C. Schlaufman?,$^{6}$
@@
 	Rapid neutron capture occurs when the neutron density is high enough such that the rate of neutron capture will occur faster than the rate at which an isotope undergoes a $\beta$-decay.
-Extremely high neutron densities ($>$$10^{24}\ \rm{free\ neutrons\ per\ cm}^{3}$) are necessary for the r-process to occur \citep[e.g.,][]{Burbidge1957,Sneden2008}.
-Sites meeting this criteria include core-collapse supernovae, neutron-star mergers, or magnetorotationally driven supernovae.
+Extremely high neutron densities ($>$$10^{24}\ \rm{free\ neutrons\ per\ cm}^{3}$) are necessary for the r-process to occur.
+Sites meeting this criteria include core-collapse supernovae (especially those that are magnetorotationally driven), neutron-star mergers.
 Core-collapse supernovae are believed to be relatively common throughout the history of the Milky Way, but they only produce small amounts of r-process material.
-Neutron-star mergers or magnetorotationally driven supernovae, however, occur much less frequently than core-collapse supernovae, but produce far more r-process material.
+Neutron-star mergers or magnetorotationally driven supernovae, however, occur much less frequently than ordinary core-collapse supernovae, but produce far more r-process material.
 Events such as these are theorised to account for the case of the highly r-process enhanced stars in the ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}.
-	Magnetorotationally driven supernovae may not produce as much r-process material as neutron-star mergers (although still more than core-collapse supernovae), are thought to occur more frequently than neutron-star mergers \citep[e.g.,][]{Li2011, LIGO2016}, but the predicted abundance patterns make them observationally indistinguishable from neutron-star mergers \citep{Ji2016}.
+	Magnetorotationally driven supernovae may not produce as much r-process material as neutron-star mergers (although still more than ordinary core-collapse supernovae), but are thought to occur more frequently than neutron-star mergers \citep[e.g.,][]{Li2011, LIGO2016}, and the predicted abundance patterns make them observationally indistinguishable from neutron-star mergers \citep{Ji2016}.
 
-	Europium ($Z=63$) is entirely produced through the r-process.
-This makes it a very useful signature for identifying stars that show evidence of significant contribution by r-process material.
-Using europium as a tracer, \cite{Ji2016} found that the level of r-process enrichment in  Reticulum II was too high to have occurred through a core-collapse supernovae event.
-	Historically, UFD galaxies have demonstrated some of the lowest abundance ratios of r-process elements seen in the Milky Way or its satellite systems.
-However, the analysis of several of Reticulum II's stars show they are greatly enriched, 2-3 orders of magnitude higher than stars found in any other UFD galaxy \citep{Ji2016}.
+	Europium ($Z=63$) is almost entirely produced through the r-process.
+This makes it a very useful signature for identifying stars that show evidence of a significant contribution from r-process material.
+Using europium as a tracer, \cite{Ji2016} found that the level of r-process enrichment in  Reticulum II was too high to have occurred through a single core-collapse supernovae event.
+	Historically, UFD galaxies have demonstrated some of the lowest abundance ratios of r-process elements with respect to Fe seen in the Milky Way or its satellite systems.
+However, the analysis of several of Reticulum II's stars show they are greatly enriched in r-process elements, 2-3 orders of magnitude higher than stars found in any other UFD galaxy \citep{Ji2016}.
 This degree of enrichment supports the theory that a single rare event must have occurred early on in the formation history of Reticulum II.
@@
 One could ask if neutron-star mergers could be responsible for all r-process stars known in the Milky Way?
-On the other hand, if we assume very little gas mixing, could core-collapse supernovae create enough material to explain a single r-process star?
-If neither of these prove to be true then we can confirm that there must be multiple sties to the r-process, providing a step forward in understanding the relative fraction of these mechanisms in the Milky Way.
+On the other hand, if we assume very little gas mixing, could core-collapse supernovae create enough material to explain a single r-process enriched star?
+If neither of these prove to be true then we can confirm that there must be multiple sites to the r-process, providing a step forward in understanding the relative fraction of these mechanisms in the Milky Way.
 
@@
 For this reason we must look to massive data sets, such as the LAMOST sky survey.
-In this letter we report the discovery of 47 r-process enhanced stars identified from LAMOST, significantly building upon the previously known Milky Way sample of 14 \citep[e.g.,][]{masho2011,Honda2004,Hayek2009,Sneden2003,Ivans2006,Hill2002,Christlieb2004,Wako2010,placo2017}.
+In this letter we report the discovery of 47 r-process enhanced stars identified from LAMOST, significantly building upon the previously known Milky Way sample of 26 \citep[e.g.,][]{masho2011,Honda2004,Hayek2009,Sneden2003,Ivans2006,Hill2002,Christlieb2004,Wako2010,placo2017,Sakari2018}.
 	In Section 2 we outline the methods used to identify r-process enhanced candidates, and our analysis methods.
-In Section 3 we discuss what our results imply about the sites of r-process.
+In Section 3 we discuss what our results imply about the sites of the r-process.
 We provide concluding remarks in Section 4.
 
-	\begin{figure}
-		\includegraphics[width=\columnwidth]{229257}
+	\begin{figure*}
+		\includegraphics[width=\textwidth]{229257}
 		\caption{The spectral region around two Europium absorption lines at 4129 and 4205 Angstroms.
@@
 		\label{fig:starindex_229257}
-	\end{figure}
+	\end{figure*}
 
@@
 The second data release from LAMOST \citep{lamost} contains about 2.2 million stellar spectra in the northern sky.
-Of these 2.2 million, 454,180 were identified as giant stars through a data-driven analysis known as \textit{The Cannon}.
+Of these 2.2 million, 454,180 were identified as giant stars through a data-driven analysis known as \textit{The Cannon} \citep{AnnaHo2017}.
 An overlap sample of 9,952 giant stars common to LAMOST and the higher-resolution ($R\approx22500$) APOGEE survey \citep{apogee} were used as a training set.
-	The stellar labels included in \textit{The Cannon} model are stellar effective temperature $T_{\rm{eff}}$, surface gravity $\log{g}$, overall metallicity $\rm{[Fe/H]}$, and average relative abundance of elements produced via $\alpha$-particle capture $\rm{[\alpha/Fe]}$.
-For reference, typical uncertainties for these labels are about $70\,\rm{K}$ for $T_{\rm{eff}}$, $0.1$ in $\log{g}$, 0.1\,dex in $\rm{[Fe/H]}$, and 0.04\,dex in $\rm{[\alpha/Fe]}$.
+	The stellar labels included in \textit{The Cannon} model are stellar effective temperature $T_{\rm{eff}}$, surface gravity $\log{g}$, overall metallicity $\rm{[Fe/H]}$, average relative abundance of elements produced via $\alpha$-particle capture $\rm{[\alpha/Fe]}$, and K-band extinction $\rm{A_{k}}$.
+For reference, typical uncertainties for these labels are about $70\,\rm{K}$ for $T_{\rm{eff}}$, $0.1$ in $\log{g}$, 0.1\, in $\rm{[Fe/H]}$, and 0.04\, in $\rm{[\alpha/Fe]}$.
 
-	We identified candidate r-process enhanced stars by searching for deviations surrounding between the pseudo-continuum-normalised flux and the best-fitting data-driven model spectrum.
+	We identified candidate r-process enhanced stars by searching for deviations between the pseudo-continuum-normalised flux and the best-fitting data-driven model spectrum.
 Specifically, we looked for deviations at the 4129\,\AA\ and 4205\,\AA\ europium absorption lines.
@@
 	\begin{itemize}
-		\item The amplitude of the fitted gaussian profile must be less than ${A<-0.05}$;
+		\item The amplitude $\rm{A}$ of the fitted gaussian profile must be ${A<-0.05}$;
 		\item The signal to noise (S/N) must be greater than 30;
 		\item The deviation from the required wavelength in question must be less than 2\,\AA;
-		\item The reduced $\chi^{2}$ value must be less than 3, $\chi_r^{2}<3$.
+		\item The reduced $\chi_r^{2}$ value must be less than 3, $\chi_r^{2}<3$.
 		\item All of these conditions must be met for both 4129\,\AA\ and 4205\,\AA\ for us to consider them sufficiently Eu enhanced.
@@
 	These filters produced an initial sample of 62 candidates from the total sample of 454,180.
-An example candidate is shown in Figure \ref{fig:starindex_423451}.
+An example candidate is shown in Figure \ref{fig:starindex_229257}.
 We visually scrutinised each candidate to remove false positives, typically due to data reduction artefacts.
 After this process we were left with 47 likely r-process enhanced candidates, 22 of which stand out as very strong candidates.
+In addition to this we searched these stars for enhancements of a similar degree in the s-process created elements Strontium and Barium and found none.
 
@@
 The lowest metallicity among the 454,180 giant stars in our sample is $[{\rm Fe/H}] \approx -2.1$.
-The previous sample of known r-process stars, before this work, exclusively consists of very metal-poor stars with $[{\rm Fe/H}] < -2$ \citep{Barklem2005}.
+The previous sample of known r-process stars, before this work, exclusively consists of very metal-poor stars with $[{\rm Fe/H}] < -1.5$ \citep{Barklem2005}.
 This fact is not to be confused with saying that most r-process stars found should be metal-poor stars, rather that at extremely low metallicities of $[{\rm Fe/H}] \lesssim -2.6$ \citep{Simmerer2004} there is a negligible contribution from the s-process
@@
 	\subsection{Multiple r-process sites?}
-	While it is possible that all known r-process enhanced stars could be made by neutron-star mergers (we show this in Section \ref{rates}), we also observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ($[{\rm Eu/Fe}] < 0.7$).
-These enhancements imply either that there is more than one active r-process site, or that there is a very heterogeneous level of gas mixing, such that neutron-star mergers are able to enhance stars with [Eu/Fe] abundances that range many orders of magnitude.
+	While it is possible that all known r-process enhanced stars could be made by neutron-star mergers (we show this in Section \ref{rates}), we also observe stellar populations in the galaxy which show relatively weak enrichment from r-process elements ($[{\rm Eu/Fe}] < 0.7$).
+These enhancements imply either that there is more than one active r-process site, or that there is a very heterogeneous level of gas mixing, such that neutron-star mergers are able to enhance stars with [Eu/Fe] abundances that cover  many orders of magnitude.
 
@@
 	Core-collapse supernova are one of the sites initially proposed to have a high enough neutron density to create elements synthesised by the r-process \citep{Burbidge1957}.
-Currently, the exact  mechanism that allows material with a high enough neutron density in order to produce  r-process material is unknown.
+Currently, the exact  mechanism that creates material with a high enough neutron density to synthesise r-process material is unknown.
 %	As of yet our knowledge is incomplete on the exact mechanism that allows material with a high enough neutron density to escape the supernovae event.
@@
 	Regardless of the exact mechanism, core-collapse supernovae seem to release $M_{\rm{Eu}}\approx10^{-7.5} M_{\odot}$ per event \citep{Argast2004}.
-While this may not be a particularly significant mass of europium, core-collapse supernovae occur reasonably frequently \citep[44,700$\,\ \rm{Gpc}^{-3} \rm{yr^{-1}}$;][]{Li2011}, and so it isn't unreasonable to suggest that, with very little mixing occurring, that much if not all r-process material could have been formed by these and recycled in the stars we present in this letter.
+While this may not be a particularly significant mass of europium, core-collapse supernovae occur reasonably frequently \citep[44,700$\,\ \rm{Gpc}^{-3} \rm{yr^{-1}}$;][]{Li2011}, and so with little mixing core-collapse supernovae are a candidate as the progenitor for some r-process enhancements under the conditions listed, but it can not be the sole source.
 
@@
 They satisfy the conditions necessary to create a high neutron density by means of interacting tidal forces between the stars, neutron dense material is accreted off the stars, allowing r-process element synthesis to occur.
-This specific process produces considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}.
-However, the direct interaction and merger of a binary neutron-star pair occurs very infrequently, with currently only one direct observation, and with a frequency estimate of 1,000$\,\rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016}.
-The significant amount of material that these mergers release can compensate for their low frequency and so, synonymous with core-collapse supernovae, it is not unreasonable to suggest that they are responsible for most if not all known r-process material.
+This specific process produces considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}, consistent with observed ejecta \citep{Kasliwal2017}.
+However, the direct interaction and merger of a binary neutron-star pair occurs very infrequently, with currently only one direct observation, and with a most plausible frequency estimate of 1,000$\,\rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016,Abadie2010} well within the the outer estimates of $320 and 4780\ \rm{Gpc^{-3}yr^{-1}}$.
+The significant amount of material that these mergers release can compensate for their low frequency and so it could be that they are responsible for most if not all r-process enhancements observed.
 
@@
 As well as an estimate of how many r-process enhanced stars, giants or dwarfs, that are expected to be present in the Milky Way.
-We assuming instant recycling, and that no r-process matter pollutes stars by any other means than these two mechanisms.
+We assume instant recycling, and that no r-process matter pollutes stars by any other means than these two mechanisms.
 In these calculations a star is deemed to be 'enhanced' where $[{\rm Eu/Fe}] \geq 0.7$.
@@
 	\begin{equation}
-	Eu_{\rm{Mass}} = 47*Eu_{\textrm{Atomic\,\,mass}}*N_{\textrm{Eu}}
+	M_{\rm{Eu}} = 47*A_{\textrm{Eu}}*N_{\textrm{Eu}}
 	\end{equation}
@@
 	\begin{equation}
-	Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}  \quad\textrm{and}
+	Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}
 	\end{equation}
@@
 	The number of Hydrogen atoms was approximated from the Hydrogen atomic mass, and the assumption was made that a giant star will be composed of $\approx$75\% Hydrogen and each star possesses an average mass of $\approx 0.8\ M_{\odot}$.
+[Eu/H] was found under the assumption the star would exhibit a [Eu/Fe] = 0.7, and using the [Fe/H] given in Table 1.
 These assumption mean that a Europium mass of $9.3 \times 10^{20}$ kilograms is required to be present in the star for it to be deemed 'enhanced'.
@@
     It was found that in the Milky Way there should be present 13,060 r-process stars enhanced solely from neutron-star mergers.
-Taking into account that this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the known 61 r-process stars in the Milky Way.
+Taking into account that this should be considered a upper-bound estimate this is still a startlingly large difference from the known 73 r-process stars in the Milky Way.
 
@@
 This allows us to find the fraction of the Milky Ways giants that our sample of r-process stars represents.
-Multiplying this fraction by the 13,060 stars that should be present in the Milky Way, we expect to be present 79 enhanced stars in LAMOST DR2, a number consistent with the 61 we now know of.
+Multiplying this fraction by the 13,060 stars that should be present in the Milky Way, we expect to be present 79 enhanced stars in LAMOST DR2, a number consistent with the 73 we now know of.
 
@@
     We can do a similar calculation with our rate of core-collapse supernovae.
-Taking the same assumptions with minimal mixing, as well as both the ejecta ($M_{Eu}\approx10^{-4.5} M_{\odot}$) and rate ($44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$) previously discussed, we find that in the Milky Way there should be present 590 r-process enhanced stars made solely from core-collapse supernovae.
+Taking the same assumptions with minimal mixing, as well as both the ejecta ($M_{Eu}\approx10^{-7.5} M_{\odot}$) and rate ($44700\ \rm{Gpc}^{-3} \rm{yr^{-1}}$) previously discussed, we find that in the Milky Way there should be present 584 r-process enhanced stars made solely from core-collapse supernovae.
 Applying the same method as utilised in the neutron-star merger calculations, we expect there to be present only 4 r-process enhanced stars in LAMOST DR2 enhanced entirely by core-collapse supernovae.
@@
 
-    By using the assumptions listed, neutron-star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.9\times10^{9}$ years, very close to the age of the universe.
+    Following from the assumptions listed and calculations above, neutron-star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.9\times10^{9}$ years, very close to the age of the universe.
 From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $2.4\times10^{11}$ years, orders of magnitude longer than the age of the universe.
@@
     This is reinforced by the r-process enhanced stars found in the LAMOST sample.
-Our 47 stars represent almost 10\% of all enhanced stars present in the Milky Way if core-collapse supernovae is considered to be the singular source of r-process enhanced stars.
+Our 47 stars represent almost 10\% of all r-process enhanced stars present in the Milky Way if core-collapse supernovae is considered to be the singular source of r-process enhanced stars.
 However, the LAMOST data release 2 only surveyed a small fraction of the Milky Way.
-It is highly unlikely that close to 10\% of the entire r-process enhanced population of the Milky Way exists within our stellar sample, it is then concluded that core-collapse supernovae can not be the only source of r-process material.
+It is highly unlikely that close to 10\% of the entire r-process enhanced population of the Milky Way exists within our stellar sample.
+It is then concluded that core-collapse supernovae can not be the only source of r-process material.
 
@@
 	\section{Conclusions}
-	We present the largest to date sample of r-process element enhanced stars to date.
-Our sample is found at a wide range of metallicities, contrary to previous discoveries that focussed on metal-poor r-process enhanced stars.
+	We present the largest sample of r-process element enhanced stars to date.
+Our sample is found to cover a wide range of metallicities, contrary to previous discoveries that focussed on metal-poor r-process enhanced stars.
 These 47 stars represent the first r-process enhanced stars found at [Fe/H] $>-2$.
 The sample is not grouped in effective temperatures, surface gravity, or radial velocity, and are not clustered in any  particular location on the sky.
-We present the first estimate, to our knowledge, that neutron-star mergers could be synthesise all r-process material in the known r-process enhanced stars within the age of the universe.
+We present the first estimate, to our knowledge, that neutron-star mergers could synthesise all r-process material in the known r-process enhanced stars within the age of the universe.
 We also provide evidence to confidently conclude core-collapse supernovae can not possibly be the only progenitors of r-process material in the Milky Way Galaxy.
@@
 	\begin{thebibliography}{99}
-		\bibitem[\protect\citeauthoryear{Abbott, B.P. et al.}{2016}]{LIGO2016}
+		\bibitem[\protect\citeauthoryear{Abadie et al.}{2010}]{Abadie2010}
+		Abadie J. et al. 2010, Classical and Quantum Gravity, 27, 17
+		\bibitem[\protect\citeauthoryear{Abbott et al.}{2016}]{LIGO2016}
 		Abbot B.P. et al. 2016, Living Reviews in Relativity, 19, 1
-		\bibitem[\protect\citeauthoryear{Argast, D. et al.}{2004}]{Argast2004}
+		\bibitem[\protect\citeauthoryear{Argast et al.}{2004}]{Argast2004}
 		Argast D., Samland M., Thielmann F-K. \& Qian Y-Z. 2004, Astronomy and Astrophysics, 416
-		\bibitem[\protect\citeauthoryear{Barklem, P.S. et al.}{2005}]{Barklem2005}
+		\bibitem[\protect\citeauthoryear{Barklem et al.}{2005}]{Barklem2005}
 		Barklem, P.S., Christlieb, N., Beers, T.C., Hill, V., Besel, M.S., Holmberg, J., Marsteller, B., Rossi, S., Zickgraf, F.-J. \& Reimers, D. 2005, A\&A, 439, 1
-		\bibitem[\protect\citeauthoryear{Burbidge, E. et al.}{1957}]{Burbidge1957}
+		\bibitem[\protect\citeauthoryear{Burbidge et al.}{1957}]{Burbidge1957}
 		Burbidge E. M., Burbidge G. R., Fowler W. A., \& Hoyle F. 1957, Review of Modern Physics, 29, 4
-		\bibitem[\protect\citeauthoryear{Burrows, A. et al.}{1995}]{Burrows1995}
+		\bibitem[\protect\citeauthoryear{Burrows et al.}{1995}]{Burrows1995}
 		Burrows, A., Hayes, J., \& Fryxell, Bruce A. 1992, ApJ, 450, 830
-		\bibitem[\protect\citeauthoryear{Cui, X.-Q. et al.}{2012}]{lamost}
+		\bibitem[\protect\citeauthoryear{Cui et al.}{2012}]{lamost}
 		Cui, X.-Q. et al., Research in Astronomy and Astrophysics, 12, 9
-		\bibitem[\protect\citeauthoryear{Drout, M. R. et al.}{2017}]{Drout2017}
+		\bibitem[\protect\citeauthoryear{Drout et al.}{2017}]{Drout2017}
 		Drout, M. R. et al. 2017, Science
-		\bibitem[\protect\citeauthoryear{Christlieb N. et al.}{2004}]{Christlieb2004}
+		\bibitem[\protect\citeauthoryear{Christlieb et al.}{2004}]{Christlieb2004}
 		Christlieb N. et al. 2004, Astronomy \& Astrophysics, 428, 1
-		\bibitem[\protect\citeauthoryear{Goriely, S. et al.}{2011}]{Goriely2011}
+		\bibitem[\protect\citeauthoryear{Goriely et al.}{2011}]{Goriely2011}
 		Goriely S., Bauswein A. \& Janka H-T. 2011, , 738, L32
-		\bibitem[\protect\citeauthoryear{Hayek, W. et al.}{2009}]{Hayek2009}
+		\bibitem[\protect\citeauthoryear{Hayek et al.}{2009}]{Hayek2009}
 		Hayek W., Wiesendahl U., Christlieb N., Eriksson K., Barklem P. S., Hill V., Beers T. C., Farouqi K., Pfeiffer B.,\& Kratz K.-L. 2009, Astronomy and Astrophysics, 504, 1
-		\bibitem[\protect\citeauthoryear{Hill, V. et al.}{2002}]{Hill2002}
+		\bibitem[\protect\citeauthoryear{Hill et al.}{2002}]{Hill2002}
 		Hill V. et al. Astronomy \& Astrophysics, 387, 1
@@
 		Ho A. Y. Q., Ness M. K., Hogg D. W., Rix H-W., Liu C., Yang F., Zhang Y., Hou Y.,\& Wang Y. 2017, ApJ, 836, 1
-		\bibitem[\protect\citeauthoryear{Honda S. et al.}{2004}]{Honda2004}
+		\bibitem[\protect\citeauthoryear{Honda et al.}{2004}]{Honda2004}
 		Honda S., Aoki W., Kajino T., Ando H., Beers T. C., Izumiura H., Sadakane K. \& Takada-Hidai M. 2004, ApJ, 607, 1
-		\bibitem[\protect\citeauthoryear{Hotokezaka, K. et al.}{2013}]{Hotok2013}
+		\bibitem[\protect\citeauthoryear{Hotokezaka et al.}{2013}]{Hotok2013}
 		Hotokezaka K., Kiuchi K., Kyutoku K., Okawa H., Skiguchi Y., Shibata M., \& Taniguchi K. 2013, APS
-		\bibitem[\protect\citeauthoryear{Ivans, I. I. et al.}{2006}]{Ivans2006}
+		\bibitem[\protect\citeauthoryear{Ivans et al.}{2006}]{Ivans2006}
 		Ivans I. I.,Simmerer J., Sneden C., Lawler J. E., Cowan J. J., Gallino R., \& Bisterzo S. 2006, ApJ, 645, 1
-		\bibitem[\protect\citeauthoryear{Ji, A. P. et al.}{2016}]{Ji2016}
+		\bibitem[\protect\citeauthoryear{Ji et al.}{2016}]{Ji2016}
 		Ji A. P., Frebel A., Chiti A., \& Simon J. D. 2016, Nature, 531
-		\bibitem[\protect\citeauthoryear{Kasen, D. et al.}{2017}]{Kasen2017}
+		\bibitem[\protect\citeauthoryear{Kasen et al.}{2017}]{Kasen2017}
 		Kasen D., Metzger B., Barnes J., Quataert E., \& Ramirez-Ruiz E. 2017, Nature, 551, 7678
-		\bibitem[\protect\citeauthoryear{Lai, D. K. et al.}{2008}]{Lai2008}
+		\bibitem[\protect\citeauthoryear{Kasliwal et al.}{2017}]{Kasliwal2017}
+		Kasliwal M. M., et al. 2017, Science,
+		\bibitem[\protect\citeauthoryear{Lai et al.}{2008}]{Lai2008}
 		Lai D. K., Bolte M., Johnson J. A., Lucatello S., Heger A., \& Woosley S. E. 2008, ApJ, 681,
-		\bibitem[\protect\citeauthoryear{Li, W. et al.}{2011}]{Li2011}
+		\bibitem[\protect\citeauthoryear{Li et al.}{2011}]{Li2011}
 		Li W., Chornock R., Leaman J., Filippenko A. V., Poznanski D., Wang X., Ganshalingam M., \& Mannucci F. 2011, Royal Astronomical Society, 412, 1473
-		\bibitem[\protect\citeauthoryear{Majewski, S.R., et al.}{2017}]{apogee}
+		\bibitem[\protect\citeauthoryear{Majewski et al.}{2017}]{apogee}
 		Majewski S.R., et al., The Astronomical Journal, 154, 3
-		\bibitem[\protect\citeauthoryear{Mashonkina, L., et al.}{2010}]{masho2011}
+		\bibitem[\protect\citeauthoryear{Mashonkina et al.}{2010}]{masho2011}
 		Mashonkina L., Christlieb N., Barklem P.S., Hill V., Beers T.C., \& Velichko A., Astronomy and Astrophysics, 516, 46
-		\bibitem[\protect\citeauthoryear{Placco, V.M., et al.}{2017}]{placo2017}
+		\bibitem[\protect\citeauthoryear{Placco et al.}{2017}]{placo2017}
 		Placco V.M., Holmbeck E. M., Frebel A., Beers T. C., Surman R. A., Ji A. P., Ezzeddine R., Points S. D., Kaleida C. C. Hansen T. T., Sakari C. M, \& Casey A. R., ApJ, 844, 1
-		\bibitem[Simmerer et al.(2004)]{Simmerer2004} Simmerer, J., Sneden, C., Cowan, J.~J., et al.\ 2004, \apj, 617, 1091 
-		\bibitem[\protect\citeauthoryear{Sneden, C. et al.}{2008}]{Sneden2008}
+		\bibitem[\protect\citeauthoryear{Simmerer et al.}{2004}]{Simmerer2004} Simmerer, J., Sneden, C., Cowan, J.~J., et al.\ 2004, \apj, 617, 1091 
+		\bibitem[\protect\citeauthoryear{Sakari et al.}{2018}]{Sakari2018} Sakari C.M., et al. 2004, \apj, 854, 2
+		\bibitem[\protect\citeauthoryear{Sneden et al.}{2008}]{Sneden2008}
 		Sneden C., Cowan J.J., \& Gallino R. 2008, Annual review of Astronomy \& Astrophysics, 46, 1
-		\bibitem[\protect\citeauthoryear{Sneden, C. et al.}{2003}]{Sneden2003}
+		\bibitem[\protect\citeauthoryear{Sneden  et al.}{2003}]{Sneden2003}
 		Sneden C. et al. 2003, ApJ, 591, 2
-		\bibitem[\protect\citeauthoryear{Wako, A. et al.}{2010}]{Wako2010}
+		\bibitem[\protect\citeauthoryear{Wako  et al.}{2010}]{Wako2010}
 		Wako A., Beers T. C., Honda S. \& Carollo D. 2010, ApJ, 723, 1
-		\bibitem[\protect\citeauthoryear{Woosley, S.E. et al.}{1992}]{Woosley1992}
+		\bibitem[\protect\citeauthoryear{Woosley  et al.}{1992}]{Woosley1992}
 		Woosley S.E, \& Hoffman R.D. 1992, ApJ, 395, 1

### 2018-04-13 betterprocess.py
Analysis code

@@ -1,0 +1,372 @@
+import numpy as np
+import os
+import matplotlib.pyplot as plt
+from astropy.table import Table
+
+import lamost
+import utils
+import pandas as pd
+
+plt.ioff()
+catalog = lamost.load_catalog()
+wavelengths = lamost.common_wavelengths
+N, P = (len(catalog), wavelengths.size)
+
+# Open the data arrays
+all_observed_flux = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "observed_flux.memmap"),
+    mode="r", dtype='float32', shape=(N, P))
+
+all_observed_ivar = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "observed_ivar.memmap"),
+    mode="r", dtype='float32', shape=(N, P))
+
+all_model_flux = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "model_flux.memmap"),
+    mode="r", dtype="float32", shape=(N, P))
+
+"""
+d = Table.read("mycatalog.fits")
+d.write("mycatalog.csv")
+"""
+data=pd.read_csv('mycatalog.csv')
+
+csv=np.array(data)
+
+Ba4554_wavelength = csv[:,41] #
+Ba4554_amp = csv[:,15]
+Ba4554_amperr = csv[:,16]
+Ba4934_wavelength = csv[:,43] #
+Ba4934_amp = csv[:,17]
+Ba4934_amperr = csv[:,18]
+Ba5853_wavelength = csv[:,45]
+Ba5853_amp = csv[:,19]
+Ba5853_amperr = csv[:,20]
+Ba6141_wavelength = csv[:,47]
+Ba6141_amp = csv[:,21]
+Ba6141_amperr = csv[:,22]
+Ba6496_wavelength = csv[:,49]
+Ba6496_amp = csv[:,23]
+Ba6496_amperr = csv[:,24]
+
+
+Eu4129_wavelength = csv[:,51]
+Eu4129_amp = csv[:,25]
+Eu4129_amperr = csv[:,26]
+Eu4205_wavelength = csv[:,53]
+Eu4205_amp = csv[:,27]
+Eu4205_amperr = csv[:,28]
+Eu4435_wavelength = csv[:,55]
+Eu4435_amp = csv[:,29]
+Eu4435_amperr = csv[:,30]
+Eu4522_wavelength = csv[:,57]
[…]

### 2018-04-13 article/ms.tex
updated things and all that

@@
 For this reason we must look to massive data sets, such as the LAMOST sky survey.
-In this letter we report the discovery of 47 r-process enhanced stars identified from LAMOST, significantly building upon the previously known Milky Way sample of 26 \citep[e.g.,][]{masho2011,Honda2004,Hayek2009,Sneden2003,Ivans2006,Hill2002,Christlieb2004,Wako2010,placo2017,Sakari2018}.
+In this letter we report the discovery of 47 r-process enhanced stars identified from LAMOST, significantly building upon the previously known Milky Way sample of 38 \citep[e.g.,][]{masho2011,Honda2004,Hayek2009,Sneden2003,Ivans2006,Hill2002,Christlieb2004,Wako2010,placo2017,Sakari2018,Hansen2018}.
 	In Section 2 we outline the methods used to identify r-process enhanced candidates, and our analysis methods.
@@
 This specific process produces considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}, consistent with observed ejecta \citep{Kasliwal2017}.
-However, the direct interaction and merger of a binary neutron-star pair occurs very infrequently, with currently only one direct observation, and with a most plausible frequency estimate of 1,000$\,\rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016,Abadie2010} well within the the outer estimates of $320 and 4780\ \rm{Gpc^{-3}yr^{-1}}$.
+However, the direct interaction and merger of a binary neutron-star pair occurs very infrequently, with currently only one direct observation, and with a most plausible frequency estimate of 1,000$\,\rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016,Abadie2010} well within the the outer estimates of $320\ \rm and 4780\ \rm{Gpc^{-3}yr^{-1}}$.
 The significant amount of material that these mergers release can compensate for their low frequency and so it could be that they are responsible for most if not all r-process enhancements observed.
@@
     It was found that in the Milky Way there should be present 13,060 r-process stars enhanced solely from neutron-star mergers.
-Taking into account that this should be considered a upper-bound estimate this is still a startlingly large difference from the known 73 r-process stars in the Milky Way.
+Taking into account that this should be considered a upper-bound estimate this is still a startlingly large difference from the known 85 r-process stars in the Milky Way.
 
@@
 This allows us to find the fraction of the Milky Ways giants that our sample of r-process stars represents.
-Multiplying this fraction by the 13,060 stars that should be present in the Milky Way, we expect to be present 79 enhanced stars in LAMOST DR2, a number consistent with the 73 we now know of.
+Multiplying this fraction by the 13,060 stars that should be present in the Milky Way, we expect to be present 79 enhanced stars in LAMOST DR2, a number consistent with the 85 we now know of.
+
+    For clarity we have also included the amount of stars expected should the rate of neutron star mergers be $320\ \rm{Gpc^{-3}yr^{-1}}$, in which case we expect there to be 4179 in Milky Way and 25 in LAMOST DR2.
+As well as what we expect should the rate be $4780\ \rm{Gpc^{-3}yr^{-1}}$, in which case in the Milky Way there would be 62426 and 377 expected in LAMOST DR2.
+
+    Should we use another more realistic estimation supplied by Galaxia \todo{CITATION NEEDED}, where we have a total amount of giants in the disk and the bulge to be $4.8\times10^8$, we then expect to find 12 stars enhanced in LAMOST DR2.
+A less consistent number from what we have observed, but still comparable in orders of magnitude.
 
@@
 
-    Following from the assumptions listed and calculations above, neutron-star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.9\times10^{9}$ years, very close to the age of the universe.
+    Following from the calculations above, neutron-star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.9\times10^{9}$ years, very close to the age of the universe as described in the calculation below:
+
+    \begin{equation}
+    	\rm Time = \frac{\rho_{\rm Eu}}{M_{\rm Eu,\ Ejecta}*Rate_{\rm NS\ star\ merger}}
+    \end{equation}
+
 	From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $2.4\times10^{11}$ years, orders of magnitude longer than the age of the universe.
@@
 		Goriely S., Bauswein A. \& Janka H-T. 2011, , 738, L32
+		\bibitem[\protect\citeauthoryear{Hansen et al.}{2018}]{Hansen2018}
+		Hansen T. T., Holmbeck E. M., Beers T. C., Placco V. M., Roederer I. U., Frebel A., Sakari C. M., Simon J. D.,\& Thompson I. B. 2018, The Astrophysical Journal
 		\bibitem[\protect\citeauthoryear{Hayek et al.}{2009}]{Hayek2009}
@@
 	% Don't change these lines
-	%\bsp	% typesetting comment
+	\bsp	% typesetting comment
 	\label{lastpage}
